---
title: "Dust Events at SBB"
author: "Danielle Reimanis"
date: "1/29/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(tidyverse)
library(tidyr)
library(lubridate)
library(ggthemes)
library(ggpubr)
library(ggplot2)
library(stringr)
library(purrr)
library(xts)
library(dygraphs)

```

### Reading in Dust Data
```{r}

dust_files <- list.files('data/Dust_Events', full.names = TRUE)

dust_read_in <- function(file){
  data_names = str_sub(file, -8,-5)
  name = paste("WY", data_names, sep = "")
 df <- read_delim(file = file, delim = " ", col_names=TRUE)%>%
  mutate(date = mdy(date))%>%
  mutate_if(is.character, as.numeric)%>%
  mutate(WY = name)%>%
  rename("date" =1, "doy"=2,"dust_event"=3)
return(df)
}

dust_06_14 <- map_dfr(dust_files, dust_read_in)

```

## Dust Events by Year
```{r}

events_yearly <- dust_06_14%>%
  filter(!is.na(dust_event))%>%
  mutate(DE_1 = ifelse(dust_event >0,1,NA))
  
ggplot(events_yearly, aes(x=date))+
  geom_col(aes(y=DE_1), width = 1)+
  facet_wrap(~WY, scales="free_x")+
  theme_bw()

```

## Connecting DE to SASP Radiation Data
```{r}

load("data/sasp_final_05_14.Rdata")

sasp_alb_dust <- dust_06_14%>%
  select(1,3)%>%
  rename("dust_raw" =2)%>%
  merge(., sasp_final_05_14, by = 'date', all = TRUE)%>%
  mutate(dust_event_num = ifelse(is.na(dust_raw), 0, dust_raw),
         dust_event = ifelse(is.na(dust_raw), 0 ,1))%>%
  select(1,3:23)

```


```{r}

ggplot(sasp_alb_dust%>%filter(!is.na(SY)), aes(x=DOSY))+
  geom_bar(aes(x = DOSY, y = dust_event), stat = 'unique', fill="red")+
  geom_bar(aes(x = DOSY, y = correct_m/4), stat = 'unique', fill="dodgerblue3")+
  geom_line(aes(y=alb_final))+
  facet_wrap(~SY, nrow = 5)+
  theme_bw()+
  scale_y_continuous(name = "Broadband Albedo",
                     sec.axis = sec_axis(~.*4, name = "Depth (m)"))+
  labs(x= "Day of Snow Year")

ggplot(sasp_alb_dust%>%filter(SY == "SY2013"), aes(x=DOSY))+
  geom_bar(aes(x = DOSY, y = dust_event), stat = 'unique', fill="red")+
  geom_bar(aes(x = DOSY, y = correct_m/4), stat = 'unique', fill="dodgerblue3")+
  geom_line(aes(y=alb_obs), color = "yellow3")+
  geom_line(aes(y=alb_final))+
  facet_wrap(~SY, nrow = 5)+
  theme_bw()+
  scale_y_continuous(name = "Broadband Albedo",
                     sec.axis = sec_axis(~.*4, name = "Depth (m)"))+
  labs(x= "Day of Snow Year", title = "SASP Albedo, Depth, and Dust Events",
       subtitle = "Black = corrected albedo, yellow = observed albedo, red = dust event")
```

### Random Hk DyGraph 
```{r}
sasp_incoming_xts <- sasp_alb_dust%>%
  select(1,10,13)%>%
  xts(., order.by = .$date)

sasp_outgoing_xts <- sasp_alb_dust%>%
  select(1,11,14)%>%
  xts(., order.by = .$date)
  
dygraph(sasp_incoming_xts)
dygraph(sasp_outgoing_xts)

```

### Final Data Depth/Albedo Graphs
```{r}

sasp_alb_dust_filter <- sasp_alb_dust%>%
  filter(!is.na(SY))

ggplot(sasp_alb_dust_filter, aes(x=correct_m, y=alb_final))+
  geom_point(aes(color = DOSY))+
  facet_wrap(~SY, nrow = 5)+
  theme_bw()+
  labs(x="Depth (m)", y="Broadband Albedo", title = "SASP Depth vs. Albedo with Day of Snow Year")

ggplot(sasp_alb_dust_filter%>%filter(correct_m < 0.5), aes(x=correct_m, y=alb_final))+
  geom_path(aes(color = DOSY))+
  geom_point(aes(color = DOSY))+
  facet_wrap(~SY, nrow = 5)+
  theme_bw()+
  labs(x="Depth (m)", y="Broadband Albedo", title = "SASP Depth vs. Albedo with Day of Snow Year, filtered to depths <0.5")

ggplot(sasp_alb_dust_filter, aes(x=depth_diff, y=alb_final))+
  geom_point(aes(color = correct_m))+
  facet_wrap(~SY, nrow = 5)+
  theme_bw()+
  labs(x=expression(Delta*"Depth (m)"), y="Broadband Albedo", title = "SASP Depth vs. Albedo with Day of Snow Year")+
  geom_vline(xintercept = 0)

ggplot(sasp_alb_dust_filter, aes(x=depth_diff, y=alb_diff))+
  geom_hline(yintercept = 0)+
  geom_vline(xintercept = 0)+
  geom_point(aes(color = correct_m))+
  facet_wrap(~SY, nrow = 5)+
  theme_bw()+
  labs(x=expression(Delta*"Depth (m)"), y=expression(Delta*"Broadband Albedo"), title = "SASP Depth vs. Albedo with Actual Depth (m)")

ggplot(sasp_alb_dust_filter, aes(x=correct_m, y=alb_diff))+
  geom_hline(yintercept = 0)+
  geom_vline(xintercept = 0)+
  geom_point(aes(color = alb_final))+
  facet_wrap(~SY, nrow = 5)+
  theme_bw()+
  labs(x="Depth (m)", y=expression(Delta*"Broadband Albedo"), title = "SASP Depth vs. Albedo with Actual Depth (m)")



```

### Max Depth
```{r}
peak_depth <- sasp_alb_dust_filter %>%
  group_by(SY)%>%
  mutate(max_depth = max(correct_m),
         SAG = ifelse(lag(correct_m) >0 & correct_m == 0, 1,0))%>%
  ungroup()%>%
  mutate(max_no_depth = ifelse(max_depth == correct_m, 1,0),
         max_no_depth = ifelse(SY == "SY2006" & 
                              lag(max_no_depth) == 1, 1, max_no_depth),
         max_no_depth = ifelse(SY == "SY2010" & 
                              lag(max_no_depth) == 1, 1, max_no_depth),
         SAG = ifelse(DOSY <100, 0, SAG))

```


### Radiation Absorbed
```{r}

hk_absorbed <- peak_depth%>%
  mutate(hk_absorbed = hkin_comb - hkout_comb)

ggplot(hk_absorbed%>%filter(correct_m > 0), aes(x=correct_m, y=hk_absorbed))+
  geom_point(aes(color = DOSY))+
  facet_wrap(~SY, nrow = 5)+
  theme_bw()+
  labs(x="Depth (m)", y = "Absorbed Shortwave Radiation")

ggplot(hk_absorbed%>%filter(correct_m > 0), aes(x=DOSY))+
  geom_col(aes(y = max_no_depth*800))+
  geom_point(aes(y = hk_absorbed, color = correct_m))+
  facet_wrap(~SY, nrow = 5)+
  theme_bw()+
  labs(x="DOSY", y = "Absorbed Shortwave Radiation")

```

### Visible Light Albedo
```{r}
load("data/sasp_05_14_skiles.Rdata")

visible_sasp <- sasp_05_14_skiles%>%
  filter(hour == 12)%>%
  filter(date > "2005-01-24")%>%
  mutate(hvis_in = hkin_unfilt - hkin_filt,
         hvis_out = hkout_unfilt - hkout_filt,
         alb_vis = hvis_out/hvis_in)%>%
  select(1,17:19)%>%
  merge(., hk_absorbed, all = TRUE)%>%
  filter(!is.na(SY))%>%
  mutate(SAG = ifelse(is.na(SAG), 0, SAG))%>%
  filter(alb_vis < 1)%>%
  select(1, 5:29, 2:4)%>%
  mutate(hkin_filt = hkin_comb - hvis_in,
         hkout_filt = hkout_comb - hvis_out,
         alb_filt = hkout_filt/hkin_filt)
  
```

### Vis vs Broadband & Filtered for graphing
```{r}
alb_long<- visible_sasp%>%
  filter(DOSY<300)%>%
  select(1,5:7, 29,8,22,25,24)%>%
  rename("Depth_meters" = correct_m,
         "Broadband" = alb_final,
         "Visible" = alb_vis)%>%
  mutate(dust_event = dust_event*0.5,
         max_no_depth = max_no_depth*0.5)%>%
  gather(key = "type", value = "albedo", 
         -date, -Depth_meters, -max_no_depth,-dust_event,-SY,-DOSY,-SAG)

alb_long_nir_swir <- visible_sasp%>%
  filter(DOSY<300)%>%
  select(1,5:6, 32, 29,8,22,24,25)%>%
  rename("Depth_meters" = correct_m,
         "NIR_SWIR" = alb_filt,
         "Visible" = alb_vis)%>%
  mutate(dust_event = dust_event*0.5,
         max_no_depth = max_no_depth*0.5)%>%
  gather(key = "type", value = "albedo", 
         -date, -Depth_meters, -max_no_depth,-dust_event,-SY,-DOSY,-SAG)

alb_long_all <- visible_sasp%>%
  filter(DOSY<300)%>%
  select(1,5:7, 32, 29,8,22,24,25)%>%
  rename("Depth_meters" = correct_m,
         "NIR_SWIR" = alb_filt,
         "Visible" = alb_vis,
         "Broadband" = alb_final)%>%
  mutate(dust_event = dust_event*0.35,
         max_no_depth = max_no_depth*0.35)%>%
  gather(key = "type", value = "albedo", 
         -date, -Depth_meters, -max_no_depth,-dust_event,-SY,-DOSY, -SAG)

alb_long_pos_all <- visible_sasp%>%
  filter(DOSY<300)%>%
  select(1,5:7, 32, 29,8,9, 22,24,25)%>%
  rename("Depth_meters" = correct_m,
         "NIR_SWIR" = alb_filt,
         "Visible" = alb_vis,
         "Broadband" = alb_final)%>%
  mutate(dust_event = dust_event*(1/3),
         max_no_depth = max_no_depth*(1/3),
         depth_positive = ifelse(depth_diff >0, depth_diff*(1/3), 0),
         depth_diff = depth_diff*(1/3))%>%
  gather(key = "type", value = "albedo", 
         -date, -Depth_meters, -max_no_depth,-dust_event,
         -SY,-DOSY, -depth_diff, -depth_positive, -SAG)
  
```

Visible vs Broadband Graphing
```{r}
ggplot(alb_long_pos_all, aes(x=DOSY))+
  geom_col(aes(y=dust_event), color = "salmon3", width = 0.25)+
  geom_col(aes(y=max_no_depth), width = 2, color = "darkslateblue")+
  geom_col(aes(y=SAG/3), width =2, color = "darkgreen")+
  geom_line(aes(y=albedo, color = type, linetype = type))+
  facet_wrap(~SY, nrow=5)+
  scale_color_manual(values=c("grey22","maroon4","cyan3"))+
  theme_bw()+
  labs(x="Day of Snow Year", y= "Albedo", title = "SASP Albedo and Dust Events", subtitle = "Brown Lines = Dust Event, Black Line = Peak Snow Depth")+
  theme(legend.title = element_blank())

ggplot(alb_long_pos_all%>%filter(DOSY>175), aes(x=DOSY))+
  geom_col(aes(y=dust_event), color = "salmon3", width = 0.25)+
  geom_col(aes(y=max_no_depth), width = 1, fill = "darkslateblue")+
  geom_col(aes(y=SAG/3), width =1, fill = "darkgreen")+
  geom_line(aes(y=albedo, color = type, linetype = type))+
  facet_wrap(~SY, nrow=5)+
  scale_color_manual(values=c("grey22","maroon4","cyan3"))+
  theme_bw()+
  labs(x="Day of Snow Year", y= "Albedo", title = "SASP Albedo and Dust Events", subtitle = "Brown Lines = Dust Event, Purple Line = Peak Snow Depth, Green Line = SAG")+
  theme(legend.title = element_blank())

ggplot(alb_long%>%filter(DOSY>175), aes(x=DOSY))+
  geom_bar(aes(y=Depth_meters/4), stat = 'unique', fill = "steelblue2", width = 0.5)+
  geom_col(aes(y=dust_event), fill = "salmon3", width = 0.5)+
  geom_col(aes(y=max_no_depth), fill = "purple4", width = 0.6)+
  geom_line(aes(y=albedo, color = type))+
  facet_wrap(~SY, nrow=5)+
  scale_color_manual(values=c("grey22","cyan3"))+
  scale_y_continuous(name = "Albedo",
                     sec.axis = sec_axis(~.*4, name = "Depth (m)"))+
  theme_bw()+
  labs(x="Day of Snow Year", title = "SASP Albedo and Dust Events", subtitle = "Brown Lines = Dust Event, Purple Line = Peak Snow Depth")+
  theme(legend.title = element_blank())
  

```

Visible vs NIR/SWIR Plot
```{r}
ggplot(alb_long_nir_swir%>%filter(DOSY>175), aes(x=DOSY))+
  geom_col(aes(y=dust_event/4), color = "salmon3", width = 0.25)+
  geom_col(aes(y=max_no_depth), width = 1, fill = "darkslateblue")+
  geom_line(aes(y=albedo, color = type))+
  geom_col(aes(y=SAG/2), width =1, fill = "darkgreen")+
  facet_wrap(~SY, nrow=5)+
  scale_color_manual(values=c("plum4","cyan3"))+
  theme_bw()+
  labs(x="Day of Snow Year", y= "Albedo", title = "SASP Albedo and Dust Events", subtitle = "Brown Lines = Dust Event, Purple Line = Peak Snow Depth, Green Line = SAG")+
  theme(legend.title = element_blank())

```

All Albedos
```{r}
ggplot(alb_long_all%>%filter(DOSY>175), aes(x=date))+
  geom_col(aes(y=dust_event/4), color = "salmon3", width = 0.25)+
  geom_col(aes(y=max_no_depth), width = 1, fill = "darkslateblue")+
  geom_col(aes(y=SAG/3), width =1, fill = "darkgreen")+
  geom_line(aes(y=albedo, color = type, linetype = type))+
  facet_wrap(~SY, nrow=5, scales = "free_x")+
  scale_color_manual(values=c("grey22","plum4", "cyan3"))+
  theme_bw()+
  labs(x="", y= "Albedo", title = "SASP Albedo and Dust Events", subtitle = "Brown Lines = Dust Event, Purple = Peak Snow Depth, Green = SAG")+
  theme(legend.title = element_blank())

alb_long_all_2 <- alb_long_all%>%
  group_by(type)%>%
  mutate(depth_diff = Depth_meters-lag(Depth_meters),
         depth_diff_pos = ifelse(depth_diff >0,depth_diff,0))%>%
  ungroup()

ggplot(alb_long_all_2%>%filter(DOSY>175), aes(x=date))+
  geom_col(aes(y=dust_event/4), color = "salmon3", width = 0.25)+
  geom_col(aes(y=max_no_depth), width = 1, fill = "darkslateblue")+
  geom_col(aes(y=depth_diff_pos/3), width = 1, fill = "steelblue4")+
  geom_col(aes(y=SAG/3), width =1, fill = "darkgreen")+
  geom_line(aes(y=albedo, color = type, linetype = type))+
  facet_wrap(~SY, nrow=5, scales = "free_x")+
  scale_color_manual(values=c("grey22","plum4", "cyan3"))+
  theme_bw()+
  labs(x="", y= "Albedo", title = "SASP Albedo and Dust Events", subtitle = "Brown Lines = Dust Event, Purple = Peak Snow Depth, Green = SAG")+
  theme(legend.title = element_blank())

ggplot(alb_long_all_2%>%filter(DOSY>175), aes(x=date))+
  geom_col(aes(y=dust_event/4), color = "salmon3", width = 0.25)+
  geom_col(aes(y=depth_diff_pos/3), width = 1, fill = "steelblue4")+
  geom_col(aes(y=SAG/3), width =1, fill = "darkgreen")+
  geom_line(aes(y=albedo, color = type, linetype = type))+
  facet_wrap(~SY, nrow=5, scales = "free_x")+
  scale_color_manual(values=c("grey22","plum4", "cyan3"))+
  theme_bw()+
  labs(x="", y= "Albedo", title = "SASP Albedo and Dust Events", subtitle = "Brown Lines = Dust Event, Purple = Peak Snow Depth, Green = SAG")+
  theme(legend.title = element_blank())

ggplot(alb_long_all%>%filter(DOSY>175), aes(x=DOSY))+
  geom_bar(aes(y=Depth_meters/4), stat = 'unique', fill = "steelblue2", width = 0.5)+
  geom_col(aes(y=dust_event), color = "salmon3", width = 0.25)+
  geom_col(aes(y=max_no_depth), width = 1)+
  geom_line(aes(y=albedo, color = type))+
  facet_wrap(~SY, nrow=5)+
  scale_color_manual(values=c("grey22","plum4", "cyan3"))+
  theme_bw()+
  labs(x="Day of Snow Year", title = "SASP Albedo and Dust Events", subtitle = "Brown Lines = Dust Event, Black Line = Peak Snow Depth")+
  theme(legend.title = element_blank())+
  scale_y_continuous(name = "Albedo",
                     sec.axis = sec_axis(~.*4, name = "Depth (m)"))


```

More Albedo graphs
```{r}

# ggplot(alb_long_pos_all%>%filter(DOSY>175), aes(x=DOSY))+
#   geom_col(aes(y=dust_event), color = "salmon3", width = 0.25)+
#   geom_col(aes(y=max_no_depth), width = 1)+
#   geom_line(aes(y=1.25-depth_positive*4), color = "steelblue2", size = 1)+
#   geom_line(aes(y=albedo, color = type))+
#   facet_wrap(~SY, nrow=5)+
#   scale_color_manual(values=c("grey22","plum4", "cyan3"))+
#   theme_bw()+
#   labs(x="Day of Snow Year", title = "SASP Albedo and Dust Events", subtitle = "Brown Lines = Dust Event, Black Line = Peak Snow Depth")+
#   theme(legend.title = element_blank())+
#   scale_y_continuous(name = "Albedo",
#                      sec.axis = sec_axis(~(1.25-.)/4, name = expression(Delta*"Depth (m)")))


ggplot(alb_long_pos_all%>%filter(DOSY>175), aes(x=DOSY))+
  geom_col(aes(y=dust_event), fill = "salmon3", width = 0.25)+
  geom_col(aes(y=max_no_depth), width = 0.5)+
  geom_col(aes(y=depth_positive), fill = "steelblue2", width = 1)+
  scale_y_reverse(name = expression(Delta*" Depth (m)"),
                     sec.axis = sec_axis(~(1-.)/(3/4), name = "Albedo"))+
  theme_bw()+
  facet_wrap(~SY, nrow=5)+
  geom_line(aes(y=1-albedo*(3/4), color = type))+
  scale_color_manual(values=c("grey22","plum4", "cyan3"))+
  labs(x="Day of Snow Year", title = "SASP Albedo and Dust Events", subtitle = "Brown Lines = Dust Event, Black Line = Peak Snow Depth")+
  theme(legend.title = element_blank())

ggplot(alb_long_pos_all%>%filter(DOSY<100&DOSY>25), aes(x=DOSY))+
  geom_col(aes(y=dust_event), fill = "salmon3", width = 0.25)+
  geom_col(aes(y=max_no_depth), width = 0.5)+
  geom_col(aes(y=depth_positive), fill = "steelblue2", width = 1)+
  scale_y_reverse(name = expression(Delta*" Depth (m)"),
                     sec.axis = sec_axis(~(1-.)/(3/4), name = "Albedo"))+
  theme_bw()+
  facet_wrap(~SY, nrow=5)+
  geom_line(aes(y=1-albedo*(3/4), color = type))+
  scale_color_manual(values=c("grey22","plum4", "cyan3"))+
  labs(x="Day of Snow Year", title = "SASP Albedo and Dust Events", subtitle = "Brown Lines = Dust Event")+
  theme(legend.title = element_blank())

```

More Random Graphs
```{r}

ggplot(visible_sasp%>%filter(DOSY<300), aes(x=DOSY))+
  geom_col(aes(y=dust_event), color = "salmon3", width = 0.5)+
  geom_col(aes(y=max_no_depth), width = 1)+
  geom_line(aes(y=alb_final), color = "black", size = 0.5)+
  geom_line(aes(y=alb_vis, color = correct_m))+
  facet_wrap(~SY, nrow=5)+
  theme_bw()+
  labs(x="Day of Snow Year", y= "Visible Light Albedo", title = "SASP Visible Albedo and Dust Events", subtitle = "Red Lines = Dust Event, Black Line = Peak Snow Depth, Blue Gradient = Depth (m)")+
  theme(legend.title = element_blank())

ggplot(visible_sasp, aes(x=DOSY))+
  geom_col(aes(y=dust_event), color = "salmon3", width = 0.5)+
  geom_line(aes(y=alb_vis), color = "goldenrod")+
  geom_line(aes(y=alb_final), color = "purple4")+
  theme_bw()+
  facet_wrap(~SY, nrow =5)

ggplot(visible_sasp, aes(x=alb_vis, y=alb_final))+
  geom_point(aes(color = correct_m))+
  theme_bw()+
  geom_abline()+
  labs(x="Visible Albedo (305-780nm)", y= "Broadband Albedo (305-2800nm)")
  
ggplot(visible_sasp, aes(x=alb_vis, y=alb_filt))+
  geom_point(aes(color = correct_m))+
  theme_bw()+
  geom_abline()+
  labs(x="Visible Albedo (305-780nm)", y= "NIR/SWIR Albedo (780-2800nm)")


```

## Dust Event Focus

```{r}
pre_post_dust <- function(filter_sy){
    dust_event <- visible_sasp%>%
      filter(SY == filter_sy)%>%
      filter(dust_event == 1)
    
    dosy_dust_event = dust_event$DOSY
    
    startframe <- data.frame(DOSY = c(0), event = c(0), day_away = c(0))

    for(i in as.list(dosy_dust_event)){
      print(i)
      local <- c(i-3,i-2,i-1,i,i+1,i+2,i+3)
      event <- paste("DE", i, sep = "")
      day_away <- c(-3,-2,-1,0,1,2,3)
    midframe <- data.frame(DOSY = local)%>%
      mutate(event = event,
             day_away = day_away)
    startframe <- rbind(startframe, midframe)
    }
    
    endframe <- startframe%>%
      filter(DOSY != 0)%>%
      filter(!duplicated(DOSY))
    end_vector <- endframe$DOSY
    
    filtered_dust <- visible_sasp%>%
      filter(SY == filter_sy)%>%
      filter(DOSY %in% end_vector)%>%
      merge(endframe, by ="DOSY")

return(filtered_dust)
}

sy_unique <- visible_sasp$SY%>%
  unique()
sy_unique <- sy_unique[sy_unique!="SY2005"]

filtered_dust_all <- map_dfr(sy_unique,pre_post_dust)

filtered_dust_graphing <- filtered_dust_all%>%
  mutate(seq = NA)
filtered_dust_graphing$seq <- with(filtered_dust_graphing, ave(SY, SY, FUN = seq_along))
filtered_dust_graphing <- filtered_dust_graphing%>%
  mutate(seq = as.numeric(as.character(seq)))%>%
  mutate(group = ifelse(event != lag(event), 1,0))

```


```{r}

ggplot(filtered_dust_graphing, aes(x=seq, group = event))+
  geom_col(aes(y=correct_m/4), fill = "steelblue2", width = 0.5)+
  geom_col(aes(y=dust_event), fill = "salmon3", width = 0.2)+
  geom_line(aes(y=alb_vis), color = "goldenrod")+
  geom_point(aes(y=alb_vis), color = "goldenrod", size = 0.5)+
  geom_line(aes(y=alb_filt), color = "plum4")+
  geom_point(aes(y=alb_filt), color = "plum4", size = 0.5)+
  facet_wrap(~SY, scales = "free_x")+
  theme_bw()+
  labs(x="", title = "SASP Albedo and Dust", subtitle = "Golden = Visible Albedo, Plum = NIR & SWIR, Brown Lines = Dust Events" )+
  theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())+
  scale_y_continuous(name = "Albedo",
                     sec.axis = sec_axis(~.*4, name = "Depth (m)"))

```

### Zenith Exploration & Max Sunlight

```{r}
cos_zen <- read_csv(file = "data/cos_zenith_angle.csv", col_names=TRUE)%>%
  as.data.frame()

visible_sasp_zenith <- visible_sasp%>%
  merge(., cos_zen, by ="DOY")%>%
  mutate(zen_rad = acos(cos_zen),
         zen_deg = zen_rad*(180/pi))%>%
  distinct(.keep_all=T)%>%
  arrange(date, decreasing = FALSE)%>%
  mutate(max_hkin = cos_zen * 1367,
         max_hkabs_alb = max_hkin*(1-alb_final))

ggplot(visible_sasp_zenith, aes(x=Et, y=zen_deg))+
  geom_point(aes(color = DOY))+
  theme_minimal()+
  labs(x="Change in Time from Solar Noon",y= "Zenith Angle °")

```


```{r}
ggplot(visible_sasp_zenith, aes(x=DOSY))+
  geom_line(aes(y=max_hkin), size = 0.5)+
  geom_col(aes(y=correct_m*400), fill = "steelblue2", width = 0.75)+
  geom_col(aes(y=hk_absorbed), fill = "black")+
  scale_y_continuous(name = "Shortwave Radiation (W/m2)",
                     sec.axis = sec_axis(~./400, name = "Depth (m)"))+
  labs(title= "SASP Absorbed Shortwave vs Max Incoming Radiation from Zenith Angle")+
  facet_wrap(~SY, nrow=5)+
  theme_bw()

```

For this next graph I mulitpled the absorportion coefficent (1-albedo) by the max incoming solar radiation for the location (1367 w/m2 * zenith angle). There was no cloud cover calculation - but it turned out surprisingly close to to the real during snowpack

```{r}
ggplot(visible_sasp_zenith, aes(x=DOSY))+
  geom_col(aes(y=correct_m*400), fill = "steelblue2", width = 0.75)+
  geom_line(aes(y=max_hkabs_alb), size = 0.5, color = "cyan")+
  geom_col(aes(y=hk_absorbed), fill = "black")+
  scale_y_continuous(name = "Shortwave Radiation (W/m2)",
                     sec.axis = sec_axis(~./400, name = "Depth (m)"))+
  labs(title= "SASP Absorbed Shortwave vs Max Incoming Radiation from Zenith Angle")+
  facet_wrap(~SY, nrow=5)+
  theme_bw()

ggplot(visible_sasp_zenith %>% filter(correct_m >0), aes(x=DOSY))+
  geom_col(aes(y=correct_m*400), fill = "steelblue2", width = 0.75)+
  geom_line(aes(y=max_hkabs_alb), size = 0.5, color = "cyan")+
  geom_line(aes(y=hk_absorbed), size = 0.5, color = "black")+
  scale_y_continuous(name = "Abosrbed Shortwave Radiation (W/m2)",
                     sec.axis = sec_axis(~./400, name = "Depth (m)"))+
  labs(title= "SASP Absorbed Shortwave vs Max Incoming Radiation from Zenith Angle")+
  facet_wrap(~SY, nrow=5, scales = "free_x")+
  theme_bw()

ggplot(visible_sasp_zenith , aes(x=DOSY))+
  geom_line(aes(y=max_hkabs_alb), size = 0.5, color = "cyan")+
  geom_line(aes(y=hk_absorbed), size = 0.5, color = "black")+
  scale_y_continuous(name = "Abosrbed Shortwave Radiation (W/m2)")+
  labs(title= "SASP Absorbed Shortwave vs Max Incoming Radiation from Zenith Angle")+
  facet_wrap(~SY, nrow=5, scales = "free_x")+
  theme_bw()
```

### First 70 cm

```{r}
visible_sasp_early <- visible_sasp_zenith%>%
  filter(correct_m < 0.7)%>%
  filter(DOSY < 125)

ggplot(visible_sasp_early%>%filter(DOSY>25), aes(x=DOSY))+
  geom_line(aes(y=alb_final))+
  geom_col(aes(y=correct_m), fill = "steelblue2", width = 0.5)+
  facet_wrap(~SY, scales = "free_x")+
  scale_y_continuous(name = "Albedo",
                     sec.axis = sec_axis(~., name = "Depth (m)"), limits = c(0,1))+
  
  theme_bw()
```

### Last 70 cm

```{r}
visible_sasp_late <- visible_sasp_zenith%>%
  filter(correct_m < 0.9)%>%
  filter(DOSY > 150)%>%
  mutate(final_days = ifelse(lag(correct_m) >0, "keep", "delete"),
         final_days = ifelse(lag(final_days) == "keep", "keep", "delete"))%>%
  filter(final_days == "keep")%>%
  mutate(depth_diff_pos = ifelse(depth_diff >0, depth_diff, 0))

ggplot(visible_sasp_late, aes(x=DOSY))+
  geom_col(aes(y=correct_m/1), fill = "steelblue2", width = 0.5)+
  geom_line(aes(y=alb_final))+
  facet_wrap(~SY, scales = "free_x", nrow = 5)+
  scale_y_continuous(name = "Albedo",
                     sec.axis = sec_axis(~.*1, name = "Depth (m)"))+
  
  theme_bw()

```
Add on new depth via precip levels not depth?

```{r}
save(visible_sasp_zenith, file= "data/visible_sasp_zenith.Rdata")

```

