---
title: "Correct SASP Values"
author: "Danielle Reimanis"
date: "1/22/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(tidyverse)
library(tidyr)
library(lubridate)
library(ggthemes)
library(ggpubr)
library(ggplot2)
library(stringr)
library(purrr)
library(xts)
library(dygraphs)

```

Workable Data Sets

```{r}

# sasp_og <- read.csv('data/SASP_1hr.csv')
# sbsp_og <- read.csv('data/SBSP_1hr.csv')
# 
# sbsp <- sbsp_og   %>%
#   mutate(., Date = mdy(Date))%>%
#   mutate(., Hour0 = ifelse(nchar(Hour) < 4,
#                           paste0("0", Hour), Hour))%>%
#   rename("date" = Date)%>%
#   mutate(., datetime_test = paste(date, Hour0, sep = " "),
#          datetime = ymd_hm(datetime_test, tz = "MST"))%>%
#   filter(datetime >= "2005-01-20 12:00:00")%>%
#   select(51,4,3,2,5,6,8,10,14,20,23:27,29,35,44,46,48)
# 
# save(sbsp, file = "data/sbsp.Rdata")
# 
# sasp <- sasp_og   %>%
#   mutate(., Date = mdy(Date))%>%
#   mutate(., Hour0 = ifelse(nchar(Hour) < 4,
#                           paste0("0", Hour), Hour))%>%
#   rename("date" = Date)%>%
#   mutate(., datetime_test = paste(date, Hour0, sep = " "),
#          datetime = ymd_hm(datetime_test, tz = "MST"))%>%
#   filter(datetime >= "2005-01-25 12:00:00")%>%
#   select(37,4,3,2,5,6,8,10,14,17:21,29,32,33)
#   
# # 
# save(sasp, file = "data/sasp.Rdata")

load("data/sasp.Rdata")
load("data/sbsp.Rdata")

```


SBSP and SASP Changes in Hkin 
```{r}
hist(sasp_filtered$PyUp_Unfilt_W)
hist(sbsp_filtered$PyUp_Unfilt_W)
hist(sasp_filtered$PyUp_Filt_W)
hist(sbsp_filtered$PyUp_Filt_W)

sasp_filtered <- sasp%>%
  filter(PyUp_Unfilt_W > 0)%>%
  filter(Hour == 1200)

sbsp_filtered <- sbsp%>%
  filter(PyUp_Unfilt_W > 0)%>%
  filter(Hour == 1200)

sbsp_pyup_unfilt <- sbsp_filtered%>%
  select(1, 13:15)%>%
  rename("PyUp_Unfilt_SBSP" = 2,
         "PyUp_Filt_SBSP" = 3,
         "PyUp_Shad_SBSP" = 4)

sasp_sbsp_boxplot <- sasp_filtered%>%
  merge(., sbsp_pyup_unfilt, by = "datetime", all= TRUE)%>%
  filter(PyUp_Shad_W > 0)%>%
  select(1,12:14,18:20)

ggplot(sasp_sbsp_boxplot, aes(x=datetime))+
  geom_point(aes(y=PyUp_Unfilt_SBSP), color = "blue")+
  geom_point(aes(y=PyUp_Unfilt_W), color = "lightblue")

ggplot(sasp_sbsp_boxplot, aes(x=PyUp_Unfilt_SBSP, y=PyUp_Unfilt_W))+
  geom_point(color = "goldenrod")+
  theme_bw()+
  labs(x="PyUp Unfiltered SBSP (W)", y="PyUp Unfiltered SASP (W)")+
  geom_abline()

ggplot(sasp_sbsp_boxplot, aes(x=PyUp_Filt_SBSP, y=PyUp_Filt_W))+
  geom_point(color = "indianred4")+
  theme_bw()+
  labs(x="PyUp Filtered SBSP (W)", y="PyUp Filtered SASP (W)")+
  geom_abline()

ggplot(sasp_sbsp_boxplot, aes(x=PyUp_Shad_SBSP, y=PyUp_Shad_W))+
  geom_point(color = "olivedrab4")+
  theme_bw()+
  labs(x="PyUp Shade SBSP (W)", y="PyUp Shade SASP (W)")+
  geom_abline()

sasp_sbsp_boxplot_long <- sasp_sbsp_boxplot%>%
  rename("SASP_Unfilt" =2,
         "SASP_Filt" =3,
         "SASP_Shad" = 4,
         "SBSP_Unfilt" = 5,
         "SBSP_Filt" = 6,
         "SBSP_Shad" = 7)%>%
  gather(., key = "specific", value = "incoming_radiation", -datetime)

sasp_sbsp_boxplot_long$specific <- factor(sasp_sbsp_boxplot_long$specific, 
                                      levels = c("SASP_Unfilt","SASP_Filt","SASP_Shad",
                                                 "SBSP_Unfilt","SBSP_Filt","SBSP_Shad"))

sasp_sbsp_boxplot_long <- sasp_sbsp_boxplot_long%>%
  mutate(site = ifelse(substr(specific,1,4) == "SASP", "SASP", "SBSP"),
         type = str_sub(specific, 6, -1))

ggplot(sasp_sbsp_boxplot_long, aes(x=datetime, y=incoming_radiation, 
                                   group = site, color=site))+
  geom_point(aes(shape = type), size = 1)+
  scale_color_manual(values = c("burlywood", "olivedrab4"))

  
```

Correcting SASP Values
```{r}

unfilt_box <- sasp_sbsp_boxplot%>%
  select(1,2,5)%>%
  rename("SASP_Unfilt" = 2,
         "SBSP_Unfilt" = 3)%>%
  gather(., key = "site", value = "Hkin", -datetime)

boxplot(Hkin~site, data = unfilt_box)

```


### Importing Skiles data
```{r}


skiles_files <- list.files('data/Skiles_Data', full.names = TRUE)
  
skiles_reader <- function(file){
  
  data_names = str_sub(file, -8,-5)
  name = paste("WY", data_names, sep = "")
  df <- read_delim(file= file,
                        delim = " ", col_names = FALSE)%>%
  select(1:17)%>%
  rename("year" = 1, "month" = 2, "day" = 3, "hour" = 4, "doy" = 5,
         "hkin_unfilt" = 6, "hkout_unfilt" = 7, "hkabs_unfilt" = 8, "alb_unfilt" = 9,
         "hkin_filt" = 10, "hkout_filt" = 11, "hkabs_filt" = 12, "alb_filt" = 13,
         "hkin_shad" = 14, "hkout_shad" = 15, "hkabs_shad" = 16, "alb_shad" = 17)%>%
  mutate_if(is.character, as.numeric)%>%
  mutate(date = paste(month, day, year, sep = " "),
         date = mdy(date))%>%
  mutate(WY = name)%>%
  select(18:19, 4:17)%>%
  mutate_all(funs(replace(., .<0,NA)))
  
  return(df)
}

sasp_05_14_skiles <- map_dfr(skiles_files, skiles_reader)

  
```

Noon Values

```{r}

sasp_05_14_skiles_noon <- sasp_05_14_skiles%>%
  filter(hour == 12,
         date > "2005-01-24")
  
ggplot(sasp_05_14_skiles_noon, aes(x=date, y=alb_unfilt))+
  geom_line()
ggplot(sasp_05_14_skiles_noon, aes(x=date, y=hkin_unfilt))+
  geom_point()
ggplot(sasp_05_14_skiles_noon, aes(x=date, y=hkout_unfilt))+
  geom_point()

sasp_noon <- sasp%>%
  filter(Hour == 1200)%>%
  filter(date < "2014-09-30")%>%
  select(2,10,12)%>%
  rename("hkin_obs" = 3,
         "hkout_obs" = 2)%>%
  mutate_all(funs(replace(., .<0,NA)))

doy_factor <- 
  
sasp_Skiles_obs <- sasp_05_14_skiles_noon %>%
  select(1, 2, 4, 5, 6)%>%
  merge(., sasp_noon, by = "date")%>%
  mutate(wy_doy = ifelse(doy > 273, doy-273, doy+92))

ggplot(sasp_Skiles_obs, aes(x=hkin_obs, y=hkin_unfilt))+
  geom_point()+
  geom_abline()+
  theme_bw()+
  facet_wrap(~WY)
ggplot(sasp_Skiles_obs, aes(x=hkout_obs, y=hkout_unfilt))+
  geom_point()+
  geom_abline()+
  theme_bw()+
  facet_wrap(~WY)
ggplot(sasp_Skiles_obs, aes(x=doy))+
  geom_point(aes(y=hkout_unfilt), color = "lightblue3")+
  geom_point(aes(y=hkout_obs), color = "lightblue4")+
  facet_wrap(~WY)+
  theme_bw()
ggplot(sasp_Skiles_obs, aes(x=doy))+
  geom_point(aes(y=hkin_unfilt), color = "gray")+
  geom_point(aes(y=hkin_obs), color = "gray17")+
  facet_wrap(~WY)+
  theme_bw()

hkin_long <- sasp_Skiles_obs%>%
  select(1:4,7,8)%>%
  rename("calculated" = 4,
         "observed" = 5)%>%
  gather(., key = "type", value = "hkin", -date, -WY, -doy, -wy_doy)

ggplot(hkin_long, aes(x=wy_doy, y=hkin, color = type))+
  geom_line()+
  facet_wrap(~WY)+
  theme_bw()+
  scale_color_manual(values = c("gray17","gray"))

ggplot(hkin_long, aes(x=wy_doy, y=hkin, color = type))+
  geom_line()+
  facet_wrap(~WY)+
  theme_bw()+
  scale_color_manual(values = c("gray17","gray"))+
  geom_vline(xintercept = 274)

hkout_long <- sasp_Skiles_obs%>%
  select(1:3,5,6,8)%>%
  rename("calculated" = 4,
         "observed" = 5)%>%
  gather(., key = "type", value = "hkout", -date, -WY, -doy, -wy_doy)

ggplot(hkout_long, aes(x=wy_doy, y=hkout, color = type))+
  geom_line()+
  facet_wrap(~WY)+
  theme_bw()+
  scale_color_manual(values = c("blueviolet","lightblue4"))

boxplot(hkout~type, data = hkout_long)
boxplot(hkin~type, data = hkin_long)

```

### Skiles Depth Write In

```{r}
skiles_depth <- list.files('data/Skiles_Depth', full.names = TRUE)

depth_reader <- function(file){
  data_year = str_sub(file, -18, -15)
  name = paste("WY", data_year, sep = "")
  df <- read_delim(file = file,
                            delim = " ", col_names=FALSE)%>%
    rename("year" =1, "month" = 2, "day" = 3, 
           "hour" = 4, "doy" = 5, "depth_m" =6)%>%
    mutate_if(is.character, as.numeric)%>%
    mutate(date = paste(month, day, year, sep = " "),
         date = mdy(date))%>%
    mutate(WY = name)%>%
    select(7,8,4,5,6)%>%
    mutate_all(funs(replace(., .<0,NA)))%>%
    mutate(depth_m = ifelse(depth_m > 9000, NA, depth_m))
         
   return(df)
}
  
sasp_05_14_depth_skiles <- map_dfr(skiles_depth, depth_reader)

```

Observed Depth and Calculated Depth
```{r}

ggplot(sasp_05_14_depth_skiles, aes(x=date, y=depth_m))+
  geom_line()

sasp_depth_noon <- sasp%>%
  filter(Hour == 1200)%>%
  select(2,16)%>%
  rename(observed_m = 2)

sasp_05_14_depth_noon <- sasp_05_14_depth_skiles%>%
  filter(hour == 12)%>%
  rename(calculated_m = 5)%>%
  merge(., sasp_depth_noon, by = 'date')%>%
  mutate(diff = calculated_m - observed_m)%>%
  filter(diff > -0.25)%>%
  mutate(correct_m = ifelse(is.na(observed_m), calculated_m, observed_m),
         correct_m = ifelse(is.na(correct_m), observed_m, calculated_m))%>%
  mutate(diff_correct = correct_m - observed_m)%>%
  mutate(wy_doy = ifelse(doy > 273, doy-273, doy+92))

ggplot(sasp_05_14_depth_noon, aes(x=observed_m, y=calculated_m))+
  geom_point()
ggplot(sasp_05_14_depth_noon, aes(x=doy, y=diff))+
  geom_point()
ggplot(sasp_05_14_depth_noon, aes(x=observed_m, y=correct_m))+
  geom_point()
ggplot(sasp_05_14_depth_noon, aes(x=doy, y=diff_correct))+
  geom_point()

ggplot(sasp_05_14_depth_noon, aes(x=date))+
  geom_point(aes(y=calculated_m), color = "black")+
  geom_point(aes(y=observed_m), color = "darkolivegreen")+
  geom_point(aes(y=correct_m), color = "goldenrod4", size =0.5)

```

Usable depth dataframe
```{r}
sasp_depth_05_14 <- sasp_05_14_depth_noon%>%
  select(1,2,10,4,8)%>%
  rename("depth_m" = 5)

ggplot(sasp_depth_05_14, aes(x=wy_doy, y=depth_m))+
  geom_line()+
  facet_wrap(~WY)+
  theme_bw()+
  labs(x = "Day of Water Year", y= "Depth of Snowpack (m)")

```

Skiles Albedo and Depth dataframe
```{r}

sasp_alb_depth_05_14 <- sasp_05_14_skiles_noon %>%
  select(1,2,4,5,6,8)%>%
  mutate(wy_doy = ifelse(doy > 273, doy-273, doy+92))%>%
  merge(., sasp_05_14_depth_noon, by = "date")%>%
  select(1:7,14)%>%
  rename("WY" = 2, "doy" = 3, "wy_doy" =7)%>%
  mutate(depth_diff = correct_m - lag(correct_m))%>%
  filter(alb_unfilt < 1)

?geom_point

ggplot(sasp_alb_depth_05_14, aes(x=wy_doy, y=alb_unfilt))+
  geom_line()+
  facet_wrap(~WY)+
  theme_bw()+
  labs(x = "Day of Water Year", y= "Broadband Albedo")

ggplot(sasp_alb_depth_05_14, aes(x=wy_doy, y=alb_unfilt, color = WY))+
  color_palette(palette = "PRGn", 10)+
  geom_line()+
  theme_bw()+
  labs(x = "Day of Water Year", y= "Broadband Albedo")

ggplot(sasp_alb_depth_05_14, aes(x=depth_diff, y=alb_unfilt, color = wy_doy))+
  geom_point()+
  theme_bw()+
  labs(x = "Change in Depth (m)", y= "Broadband Albedo")+
  facet_wrap(~WY, scales = "free_x")

```


Skiles data with full years 2005-2014
```{r}
dates_05_14 <- seq.Date(from = as.Date("2005-01-25"), 
                        to = as.Date("2014-07-01"), by = "day")%>%
  as.data.frame()%>%
  rename("date" =1)%>%
  merge(., sasp_alb_depth_05_14, by = "date", all = T)


ggplot(verseghy_map%>%filter(alb_obs<1), aes(x=alb_obs, y=alb_unfilt))+
  geom_point()+
  facet_wrap(~WY)+
  geom_abline()+
  theme_bw()

ggplot(verseghy_map%>%filter(alb_obs<1), aes(x=alb_obs, y=alb_unfilt))+
  geom_point()+
  geom_abline()+
  theme_bw()

```

Ground Albedo with Skiles data
```{r}

skiles_ground_alb <- sasp_alb_depth_05_14 %>%
  filter(correct_m < 0.02)
#Only 22 observations when depth =0, will use ground albedo of OG data
#summary(skiles_ground_alb)

```


Verseghy 1991 

Assumed: 
Max albedo = 0.84
Non-melt albedo = 0.7
Melting albedo = 0.5 
Bare Ground = 0.16

```{r}
average_temp <- sasp%>%
  filter(Hour == 1200)%>%
  mutate(avg_temp_c = (LoAir_Min_C+LoAir_Max_C)/2)%>%
  select(2,18)
sasp_obs <- sasp_Skiles_obs%>%
  select(1,6,7)
sasp_alb_depth_05_14_all <- sasp_alb_depth_05_14%>%
  merge(., average_temp, by='date')%>%
  merge(., sasp_obs, by = 'date')%>%
  mutate(alb_obs = hkout_obs/hkin_obs)


verseghy_test_2005 <- sasp_alb_depth_05_14_all%>%
  filter(WY == "WY2005")%>%
  filter(!is.na(depth_diff))%>%
  mutate(bare_albedo = 0.16,
         depth_diff_pos = ifelse(depth_diff >0, depth_diff, 0),
         cume_snow = cumsum(depth_diff_pos),
         albedo_min = ifelse(avg_temp_c < 0 & depth_diff_pos == 0, 0.7, 
                             ifelse(avg_temp_c >= 0, 0.5, NA)),
         albedo_min = ifelse(avg_temp_c > 0 & cume_snow == lag(cume_snow), 
                             0.16, albedo_min))%>%
  mutate(vrsg_albedo = ifelse(cume_snow == 0,bare_albedo,NA),
         vrsg_albedo = ifelse(depth_diff_pos > 0, 0.84, vrsg_albedo),
         vrsg_albedo = ifelse(correct_m == 0, 0.18 , vrsg_albedo))
 
albedo_05 = verseghy_test_2005$vrsg_albedo

for(i in 1:nrow(verseghy_test_2005)){
  if(is.na(albedo_05[i])){
    albedo_05[i] = ((albedo_05[i-1]*exp(-0.01)))
  }
}

verseghy_test_2005$vrsg_albedo <- albedo_05

ggplot(verseghy_test_2005, aes(x=wy_doy))+
  geom_point(aes(y=alb_obs), color = "black")+
  geom_line(aes(y=vrsg_albedo),color= "sienna")+
  geom_line(aes(y=alb_unfilt), color = "cadetblue4")+
  ylim(c(0,1))+
  theme_bw()+
  labs(x="Day of Water Year", y="Broadband Albedo", 
       title = "WY 2008 Albedo Observed vs Modeled",
       subtitle= "Black = Observed, Brown = Verseghy Model, Green = Skiles Corrections")

```


Function Time

```{r}
verseghy_function <- function(wy){
df <- sasp_alb_depth_05_14_all%>%
  filter(WY == wy)%>%
  filter(!is.na(depth_diff))%>%
  mutate(bare_albedo = 0.16,
         depth_diff_pos = ifelse(depth_diff >0, depth_diff, 0),
         cume_snow = cumsum(depth_diff_pos),
         albedo_min = ifelse(avg_temp_c < 0 & depth_diff_pos == 0, 0.7, 
                             ifelse(avg_temp_c >= 0, 0.5, NA)),
         albedo_min = ifelse(avg_temp_c > 0 & cume_snow == lag(cume_snow), 
                             0.16, albedo_min))%>%
  mutate(vrsg_albedo = ifelse(cume_snow == 0,bare_albedo,NA),
         vrsg_albedo = ifelse(depth_diff_pos > 0, 0.84, vrsg_albedo),
         vrsg_albedo = ifelse(correct_m == 0, 0.18 , vrsg_albedo))
 
albedo_loop = df$vrsg_albedo

for(i in 1:nrow(df)){
  if(is.na(albedo_loop[i])){
    albedo_loop[i] = ((albedo_loop[i-1]*exp(-0.01)))
  }
}

df$vrsg_albedo <- albedo_loop

return(df)

}
```

Testing Function Out
```{r}
wy_skiles_string <- unique(sasp_alb_depth_05_14_all$WY)

verseghy_map <- map_dfr(wy_skiles_string, verseghy_function)

ggplot(verseghy_map, aes(x=wy_doy))+
  geom_point(aes(y=alb_obs), color = "black", size = 0.5)+
  geom_line(aes(y=vrsg_albedo),color= "sienna")+
  geom_line(aes(y=alb_unfilt), color = "cadetblue4")+
  ylim(c(0,1))+
  theme_bw()+
  facet_wrap(~WY)+
  labs(x="Day of Water Year", y="Broadband Albedo", 
       title = "Albedo Observed vs Modeled",
       subtitle= "Black = Observed, Brown = Verseghy Model, Green = Skiles Corrections")

```

```{r}
verseghy_long <- verseghy_map%>%
  select(1,2,3,7,8,6,13,18)%>%
  rename("Skiles_Data" = 6,
         "Observed" = 7,
         "USACoE_Model" = 8)%>%
  gather(., key = "type", value = "albedo", -date,-WY,-doy,-wy_doy,-correct_m)

ggplot(verseghy_long, aes(x=wy_doy))+
  geom_bar(aes(x = wy_doy, y = correct_m/4), stat = 'unique', fill="dodgerblue3")+
  geom_line(aes(x=wy_doy, y=albedo, color = type))+
  scale_color_manual(values = c("black", "cadetblue4", "sienna"))+
  scale_y_continuous(name = "Broadband Albedo", limits = c(0,1),
                     sec.axis = sec_axis(~.*4, name = "Depth (m)"))+
  theme_bw()+
  facet_wrap(~WY)+
  theme(legend.position = c(0.75,0.15), legend.title = element_blank())+
  labs(x="Day of Water Year", y="Albedo", title= "SASP Albedo for Muliple Water Years")

```

Albedo and Hk Values (Verseghy vs Observed)
```{r}

albedo_comparison <- sasp_alb_depth_05_14_all%>%
  mutate(delta_hkin =  hkin_obs-hkin_unfilt,
         delta_hkout =hkout_obs-hkout_unfilt,
         delta_alb = alb_obs-alb_unfilt,
         Change_Hkout = ifelse(delta_hkout > 0,
                                            "Observed_Larger", "Calculated_Larger"),
         Change_Hkin = ifelse(delta_hkin > 0,
                                            "Observed_Larger", "Calculated_Larger"))

ggplot(albedo_comparison, aes(x=delta_alb, y=delta_hkin))+
  geom_point(aes(color=Change_Hkout))+
  scale_color_manual(values = c("deepskyblue","deeppink4"))+
  theme_bw()+
  theme(legend.position = c(0.6,0.8))+
  labs(y=expression(Delta*"HKin"), x= expression(Delta*"Albedo"))

ggplot(albedo_comparison%>%filter(delta_alb >0.1), aes(x=delta_alb, y=delta_hkin))+
  geom_point(aes(color=delta_hkout))+
  theme_bw()+
  theme(legend.position = c(0.85,0.8))+
  labs(y=expression(Delta*"HKin"), x= expression(Delta*"Albedo"))+
  scale_colour_gradient2()

ggplot(albedo_comparison, aes(x=delta_alb, y=delta_hkout))+
  geom_point(aes(color=Change_Hkin))+
  scale_color_manual(values = c("deepskyblue","deeppink4"))+
  theme_bw()+
  theme(legend.position = c(0.75,0.85))+
  labs(y=expression(Delta*"HKout"), x= expression(Delta*"Albedo"))

ggplot(albedo_comparison%>%filter(delta_alb >0.1), aes(x=delta_alb, y=delta_hkout))+
  geom_point(aes(color=delta_hkin))+
  theme_bw()+
  theme(legend.position = c(0.9,0.83))+
  labs(y=expression(Delta*"HKout"), x= expression(Delta*"Albedo"))+ 
  scale_colour_gradient(low = "black", high = "white")

ggplot(albedo_comparison, aes(x=alb_obs, y=hkin_obs))+
  geom_point(aes(color=delta_hkin))+
  theme_bw()+
  theme(legend.position = c(0.7,0.7))+
  labs(y="Hkin Observed", x= "Albedo")+ 
  scale_colour_gradient2()

ggplot(albedo_comparison, aes(x=delta_alb, y=hkout_obs))+
  geom_point(aes(color=delta_hkout))+
  theme_bw()+
  labs(y="Hkout Observed", x= expression(Delta*"Albedo"))+ 
  scale_colour_gradient2()


```

Cleaned Dataset to Save
```{r}
dataset_merge <- albedo_comparison%>%
  merge(., sasp_noon, by = "date", all = TRUE)%>%
  select(1:9,19:20)%>%
  rename("hkout_obs"=10, "hkin_obs"=11)%>%
  mutate(alb_obs = hkout_obs/hkin_obs)%>%
  mutate(correct_m = ifelse(alb_obs <0.2, 0, correct_m))%>%
  merge(., average_temp, by ='date')%>%
  mutate(alb_final = ifelse(correct_m == 0, alb_obs, alb_unfilt))%>%
  mutate(depth_diff = correct_m - lag(correct_m))

doy = dataset_merge$doy
for(i in 1:nrow(dataset_merge)){
  if(is.na(doy[i])){
    doy[i] = (doy[i-1]+1)
  }
}
dataset_merge$doy <- doy

wy = dataset_merge$WY
for(i in 1:nrow(dataset_merge)){
  if(is.na(wy[i])){
    wy[i] = (wy[i-1])
  }
}
dataset_merge$WY <- wy

final_dataset_05_14 <- dataset_merge%>%
  mutate(DOWY = ifelse(doy > 273, doy-273, doy+92),
         DOWY = ifelse(WY == "WY2009", ifelse(doy > 274, doy-274, doy+92), DOWY),
         DOWY = ifelse(WY == "WY2013", ifelse(doy > 274, doy-274, doy+92), DOWY))%>%
  mutate(SY = ifelse(date >= "2004-09-01" & date < "2005-09-01", "SY2005",
              ifelse(date >= "2005-09-01" & date < "2006-09-01", "SY2006",
              ifelse(date >= "2006-09-01" & date < "2007-09-01", "SY2007",
              ifelse(date >= "2007-09-01" & date < "2008-09-01", "SY2008",
              ifelse(date >= "2008-09-01" & date < "2009-09-01", "SY2009",
              ifelse(date >= "2009-09-01" & date < "2010-09-01", "SY2010",
              ifelse(date >= "2010-09-01" & date < "2011-09-01", "SY2011",
              ifelse(date >= "2011-09-01" & date < "2012-09-01", "SY2012",                                        ifelse(date >= "2012-09-01" & date < "2013-09-01", "SY2013",
              ifelse(date >= "2013-09-01" & date < "2014-09-01", "SY2014",NA)))))))))))%>%
  mutate(DOSY = ifelse(doy > 243, doy-243, doy+122),
         DOSY = ifelse(SY == "SY2009", ifelse(doy > 244, doy-244, doy+122), DOSY),
         DOSY = ifelse(SY == "SY2013", ifelse(doy > 244, doy-244, doy+122), DOSY))%>%
  rename("DOY" = 3, "hkin_corr" = 4, "hkout_corr" = 5, "alb_corr" = 6)%>%
  select(1,3,2,15,16,17,14, 8, 9, 13, 4:6,11,10,12)%>%
  mutate(hkin_comb = ifelse(is.na(hkin_corr), hkin_obs, hkin_corr),
         hkout_comb = ifelse(is.na(hkout_corr), hkout_obs, hkout_corr))%>%
  mutate(alb_diff = alb_final - lag(alb_final))%>%
  filter(!is.na(alb_final))%>%
  filter(alb_final < 0.96)%>%
  filter(!is.na(SY))

```


```{r}
ggplot(final_dataset_05_14, aes(x=DOSY))+
  geom_bar(aes(x = DOSY, y = correct_m/4), stat = 'unique', fill="dodgerblue3")+
  geom_line(aes(y=alb_final))+
  facet_wrap(~SY, nrow = 5)+
  theme_bw()+
  scale_y_continuous(name = "Broadband Albedo",
                     sec.axis = sec_axis(~.*4, name = "Depth (m)"))+
  labs(x= "Day of Snow Year")

ggplot(final_dataset_05_14%>%filter(SY=="SY2014"), aes(x=DOSY))+
  geom_bar(aes(x = DOSY, y = correct_m/4), stat = 'unique', fill="dodgerblue3")+
  geom_point(aes(y=alb_final))+
  theme_bw()+
  scale_y_continuous(name = "Broadband Albedo",
                     sec.axis = sec_axis(~.*4, name = "Depth (m)"))+
  labs(x= "Day of Snow Year")

ggplot(final_dataset_05_14, aes(x=DOSY))+
  geom_bar(aes(x = DOSY, y = correct_m*300), stat = 'unique', fill="dodgerblue3")+
  geom_point(aes(y=hkin_comb), color = "orange")+
  geom_point(aes(y=hkout_comb), color = "gray27")+
  facet_wrap(~SY, nrow = 5)+
  theme_bw()+
  scale_y_continuous(name = "Shortwave Radiation",
                     sec.axis = sec_axis(~./300, name = "Depth (m)"))+
  labs(x= "Day of Snow Year", title = "SASP Automated Sensor Corrected Radiaiton and Snow Depth",
       subtitle = "Orange = Incoming Radiation, Dark Gray = Outgoing Radiation")

```


```{r}

max_depth <- final_dataset_05_14%>%
  group_by(SY)%>%
  summarise(depth_m = max(correct_m))

dy_final <- final_dataset_05_14%>%
  select(1,7,8)%>%
  xts(., order.by = .$date)

dygraph(dy_final)%>%
  dySeries("alb_final", color = "orange")%>%
  dySeries("correct_m", stepPlot = TRUE, fillGraph = F, color = "black")


```

Split Into Albedo Sections

```{r}
ggplot(final_dataset_05_14%>%filter(alb_final <0.2), aes(x=DOSY))+
  geom_bar(aes(x = DOSY, y = correct_m*300), stat = 'unique', fill="dodgerblue3")+
  geom_point(aes(y=hkin_comb), color = "orange")+
  geom_point(aes(y=hkout_comb), color = "gray27")+
  facet_wrap(~SY, nrow = 5)+
  theme_bw()+
  scale_y_continuous(name = "Shortwave Radiation",
                     sec.axis = sec_axis(~./300, name = "Depth (m)"))+
  labs(x= "Day of Snow Year", title = "SASP Automated Sensor Corrected Radiaiton and Snow Depth, Albedo <0.2",
       subtitle = "Orange = Incoming Radiation, Dark Gray = Outgoing Radiation")

ggplot(final_dataset_05_14%>%filter(alb_final >0.2 & alb_final <0.6), aes(x=DOSY))+
  geom_bar(aes(x = DOSY, y = correct_m*300), stat = 'unique', fill="dodgerblue3")+
  geom_point(aes(y=hkin_comb), color = "orange")+
  geom_point(aes(y=hkout_comb), color = "gray27")+
  facet_wrap(~SY, nrow = 5)+
  theme_bw()+
  scale_y_continuous(name = "Shortwave Radiation",
                     sec.axis = sec_axis(~./300, name = "Depth (m)"))+
  labs(x= "Day of Snow Year", title = "SASP Automated Sensor Corrected Radiaiton and Snow Depth, Albedo >0.2 and <0.6",
       subtitle = "Orange = Incoming Radiation, Dark Gray = Outgoing Radiation")

ggplot(final_dataset_05_14%>%filter(alb_final >0.6 & alb_final <0.75), aes(x=DOSY))+
  geom_bar(aes(x = DOSY, y = correct_m*300), stat = 'unique', fill="dodgerblue3")+
  geom_point(aes(y=hkin_comb), color = "orange")+
  geom_point(aes(y=hkout_comb), color = "gray27")+
  facet_wrap(~SY, nrow = 5)+
  theme_bw()+
  scale_y_continuous(name = "Shortwave Radiation",
                     sec.axis = sec_axis(~./300, name = "Depth (m)"))+
  labs(x= "Day of Snow Year", title = "SASP Automated Sensor Corrected Radiaiton and Snow Depth, Albedo >0.6 and <0.75",
       subtitle = "Orange = Incoming Radiation, Dark Gray = Outgoing Radiation")


```

Difference in Depth
```{r}
ggplot(final_dataset_05_14, aes(x=DOSY))+
  geom_bar(aes(x = DOSY, y = depth_diff*2000), stat = 'unique', fill="dodgerblue3")+
  geom_point(aes(y=hkin_comb), color = "orange", size=0.5)+
  geom_point(aes(y=hkout_comb), color = "gray27", size= 0.5)+
  facet_wrap(~SY, nrow = 5)+
  theme_bw()+
  scale_y_continuous(name = "Shortwave Radiation",
                     sec.axis = sec_axis(~./2000, name = "Change in Depth (m)"))+
  labs(x= "Day of Snow Year", title = "SASP Automated Sensor Corrected Radiaiton and Snow Depth",
       subtitle = "Orange = Incoming Radiation, Dark Gray = Outgoing Radiation")

ggplot(final_dataset_05_14, aes(x=DOSY))+
  geom_bar(aes(x = DOSY, y = depth_diff*2), stat = 'unique', fill="dodgerblue3")+
  geom_line(aes(y=alb_final))+
  facet_wrap(~SY, nrow = 5)+
  theme_bw()+
  scale_y_continuous(name = "Albedo",
                     sec.axis = sec_axis(~./2, name = "Change in Depth (m)"))+
  labs(x= "Day of Snow Year", title = "SASP Automated Sensor Corrected Albedo and Change in Snow Depth")
```


```{r}

change_alb_change_dep_func <- function(filter){
p1 <- ggplot(final_dataset_05_14%>%filter(SY == filter), aes(x=DOSY))+
  geom_bar(aes(x = DOSY, y = depth_diff), stat = 'unique', fill="steelblue2")+
  geom_line(aes(y=alb_diff))+
  theme_bw()+
  scale_y_continuous(name = "Change in Albedo",
                     sec.axis = sec_axis(~./1, name = "Change in Depth (m)"))+
  labs(x= "Day of Snow Year", title = filter)

return(p1)
}

change_alb_change_dep_func(filter = "SY2009")
change_alb_change_dep_func(filter = "SY2006")


```

```{r}

alb_change_dep_func <- function(filter){
p1 <- ggplot(final_dataset_05_14%>%filter(SY == filter), aes(x=DOSY))+
  geom_bar(aes(x = DOSY, y = depth_diff*2), stat = 'unique', fill="dodgerblue3")+
  geom_line(aes(y=alb_final))+
  theme_bw()+
  scale_y_continuous(name = "Albedo",
                     sec.axis = sec_axis(~./2, name = "Change in Depth (m)"))+
  labs(x= "Day of Snow Year", title = filter)
  
return(p1)
}

alb_change_dep_func(filter = "SY2005")
alb_change_dep_func(filter = "SY2009")

```


```{r}
change_alb_dep_func <- function(filter){
p1 <- ggplot(final_dataset_05_14%>%filter(SY == filter), aes(x=DOSY))+
  geom_bar(aes(x = DOSY, y = correct_m/6), stat = 'unique', fill="dodgerblue3")+
  geom_line(aes(y=alb_diff))+
  theme_bw()+
  scale_y_continuous(name = "Change in Albedo",
                     sec.axis = sec_axis(~.*6, name = "Depth (m)"))+
  labs(x= "Day of Snow Year", title = filter)
  
return(p1)
}

change_alb_dep_func(filter = "SY2007")

```



