---
title: "SASP Snow Depth and Albedo"
author: "Danielle Reimanis"
date: "1/5/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(tidyverse)
library(tidyr)
library(lubridate)
library(ggthemes)
library(ggpubr)
library(ggplot2)

```

Steven and I talked 1/4/21 about what needs to be done to finish up this semester. I need to do a lot of analysis still, I need results! This code and Rmarkdown file are to be well organized and go into depth on analysis. What patterns can we find? What are the data telling us? 

1) Plotting changes in albedo and changes in snow depth only at SASP. Is there a pattern? Can we look at the timing of the points and notice a hysteresis? 

2) We were in contact with Jeff about unfiltered and filtered data. 

"Hi - unfiltered is broadband, 305-2800, filtered is Near infrared 780-2800.  broadband minus NIR gives you the visible spectrum.  The metadata shows the below: https://snowstudies.org/archived-data/.  Look at a picture of the electromagnetic spectrum to see a visual.  

(i) Broad band CM21 pyranometer: 305-2800 nm 
(ii) NIR to SWIR CM21-RG695 pyranometer: 780-2800 nm
(iii)CG4 pyrgeometer: 4.5-42 μm (50% points)"

**Because of this new information, I will only be using Unfiltered data, as it includes visible**

Objective: Complete 2017-2019 dataset
Problem: In the 2018-2019 graphs, I noticed the albedo was 0.6 and higher even though the snow depth was 0cm. That does not make sense. 
Plan: To incorporate depth from Red Mountain Pass Snotel to the depths that read 0 in the SASP data. 
Justification: Refer to the two year comparison of SASP depth to SNOTEL depth. There are depth values, through the shoulder months of 2018, that were not accounted for in SASP.

Preliminary:
```{r}
load("data/red_mtn_pas.Rdata")

simple_red_mtn_pass <- red_mtn_pass %>%
  select(1,7,8)%>%
  rename("date" = 1,
         "depth_in" = 2,
         "swe_in" = 3)%>%
  mutate(date = as_date(date))%>%
  mutate(swe_mm = swe_in*25.4,
         depth_cm = depth_in*2.54,
         depth_m = depth_cm/100,
         density_kg_m3 = ifelse(depth_m == 0, 0, swe_mm/depth_m))

#Largest SWE in 2017-18 snowpack was 416.56 mm
#Largest SWE in 2018-19 snowpack was 924.56 mm

ggplot(simple_red_mtn_pass, aes(x=date, y=swe_mm))+
  geom_line()+
  theme_bw()+
  labs(title = "SWE for Two Years at Red Mtn Pass SNOTEL")

ggplot(simple_red_mtn_pass, aes(x=date, y=density_kg_m3))+
  geom_line()+
  theme_bw()+
  labs(title = "Density for Two Years at Red Mtn Pass SNOTEL")


```

What is needed to determine if SNOTEL or SASP depth should be used?

SASP and SNOTEL have similar depth trends. SNOTEL has more non-NA and non-zero points than SASP. I mutated SASP depth so all NAs were turned to zeros. This turned out to hinder the results, as there were SASP days that showed an albedo greater than its non-snow equivalent (SCA = 0%). Though albedo rose to 'snow-levels' the depth read 0 still. The SNOTEL data showed there was depth on these days, at least at the the SNOTEl site. 

1) What is the ground's albedo?
The mean albedo for snow free days was 0.1618064. With values ranging from 0.1115 to 0.1919.

```{r}

#First I filtered the snow depth to only be 0 cm. But since there were high albedo values even with a 0 cm snow depth, I graphed the points and noticed the only spikes that occured (showing errors in the data) were all above 0.2. Next, I filtered albedo to all values less than 0.2. Then I took the average. This is the average albedo for SNOW FREE days.

ground_albedo <- sasp_alb_depth %>%
  filter(snow_depth_cm == 0,
         alb_unfilt <= 0.2)

#mean(ground_albedo$alb_unfilt)
#summary(ground_albedo)
```

Final Steps: 
If snow depth is 0 but albedo is greater than 0.2, I will replace the depth value (0) with the depth at SNOTEL the same day. It turns out, we just needed to replace all NA values with snotel depth values instead. Also, negative values were replaced  with SNOTEL values.

```{r}
load("data/sasp_noon.Rdata")

snotel_depth_cm <- simple_red_mtn_pass$depth_cm
snotel_swe_mm <- simple_red_mtn_pass$swe_mm

sasp_alb_depth_corrected <- sasp_noon%>%
  mutate(snotel_depth_cm = snotel_depth_cm)%>%
  mutate(snotel_swe_mm = snotel_swe_mm)

sasp_alb_depth <- sasp_alb_depth_corrected  %>%
  select(1, 22, 24, 34, 37, 46, 47)%>%
  mutate(alb_unfilt = PyDwn_Unfilt_W/PyUp_Unfilt_W,
         sasp_depth_cm = Sno_Height_M * 100)%>%
  filter(alb_unfilt > 0,
         alb_unfilt < 1)%>%#filtering these values removes 108 observations (730->622)
    filter(date != "2019-03-15",
         date != "2019-03-16",
         date != "2019-03-14",
         date != "2019-03-13")#filtering these values removes 4 observations (622-618)

alb_depth_corrected <- sasp_alb_depth %>%
  select(1, 5:9)%>%
  rename("sasp_precip_mm" =2)%>%
  mutate(delta_albedo = alb_unfilt - lag(alb_unfilt))%>%
  mutate(depth_cm = ifelse(is.na(sasp_depth_cm), snotel_depth_cm, 
                           ifelse(sasp_depth_cm <0, snotel_depth_cm, sasp_depth_cm)))%>%
  mutate(depth_m = depth_cm/100,
         calc_density_kg_m3 = ifelse(depth_m == 0, 0, snotel_swe_mm/depth_m),
         snotel_depth_m = snotel_depth_cm/100,
         snotel_density_kg_m3 = ifelse(snotel_depth_m == 0, 0,
                                       snotel_swe_mm/snotel_depth_m))%>%
  select(1, 4, 5, 7:12)
  
# tail(sort(alb_depth_corrected$calc_density_kg_m3), 10)
# tail(sort(alb_depth_corrected$snotel_density_kg_m3), 10)
# this explains why I chose not to use calculated density (snotel swe/corrected sasp depth) and needed to use snotel density (snotel swe/snotel depth)
```

NEXT STEPS HERE: 
1) Redo all these graphs with the new updated corrected depths
2) Similar idea to the depth graphs, use density as the independent variable
3) Focus on the 'shoulder weeks' of snowpacks and look for albedo patterns with only a few cm of depth. 

2017-2018 Winter Season

```{r}
#filtered for snow-on. first day of accumulation was 9/30/17 last day of melt was 5/18/18
#This first day and last day are chosen so the new dataset starts at 0 cm depth, and ends with 0 cm depth.
#grouped albedo by the mean of albedo values (mean = 0.6031728)

sasp_17_18 <- sasp_alb_depth %>%
  filter(date < "2018-05-19",
         date > "2017-09-29")%>%
  mutate(group = ifelse(alb_unfilt <0.6, "Albedo<0.6", "Albedo>0.6"))

ggplot(sasp_17_18, aes(x=delta_snow_depth_cm, y=delta_albedo, 
                       color = date, shape = group))+
  geom_hline(yintercept=0)+
  geom_vline(xintercept=0)+
  geom_point()+
  theme_bw()+
  labs(title = "Change in albedo and snow depth at SASP: 9/30/2017 - 05/18/2018",
       x=expression(Delta*" Snow Depth (cm)"), y=expression(Delta*" Broadband Albedo"))

#Close up of (0,0)
ggplot(sasp_17_18, aes(x=delta_snow_depth_cm, y=delta_albedo, 
                       color = date, shape = group))+
  geom_hline(yintercept=0)+
  geom_vline(xintercept=0)+
  geom_point()+
  theme_bw()+
  labs(title = "Change in albedo and snow depth at SASP: 9/30/2017 - 05/18/2018",
       x=expression(Delta*" Snow Depth (cm)"), y=expression(Delta*" Broadband Albedo"))+
  xlim(min = -5, max = 5)+
  ylim(min = -0.2, max = 0.2)
  
ggplot(sasp_17_18, aes(x=delta_snow_depth_cm, y=alb_unfilt, 
                       color = date, shape = group))+
  geom_hline(yintercept=0)+
  geom_vline(xintercept=0)+
  geom_point()+
  theme_bw()+
  labs(title = "Albedo vs changes in snow depth at SASP: 9/30/2017 - 05/18/2018",
       x=expression(Delta*" Snow Depth (cm)"), y=expression("Broadband Albedo"))


#Depth versus albeo with stat regression line
ggplot(sasp_17_18, aes(x=snow_depth_cm, y=alb_unfilt, 
                       color = date))+
  geom_hline(yintercept=0)+
  geom_vline(xintercept=0)+
  geom_point()+
  theme_bw()+
  labs(title = "Albedo vs snow depth at SASP: 9/30/2017 - 05/18/2018",
       x=expression("Snow Depth (cm)"), y=expression("Broadband Albedo"))+
  geom_smooth(method = "lm", se = FALSE, color = "black")+
  stat_regline_equation(label.x.npc = 0.5, label.y.npc = 0.95)

#Change in depth versus albeo with stat regression line
ggplot(sasp_17_18, aes(x=delta_snow_depth_cm, y=delta_albedo, 
                       color = date))+
  geom_hline(yintercept=0)+
  geom_vline(xintercept=0)+
  geom_point()+
  theme_bw()+
  labs(title = "Albedo vs snow depth at SASP: 9/30/2017 - 05/18/2018",
       x=expression(Delta*"Snow Depth (cm)"), y=expression(Delta*"Broadband Albedo"))+
  geom_smooth(method = "lm", se = FALSE, color = "black")+
  stat_regline_equation(label.x.npc = 0.5, label.y.npc = 0.95)

```

2018-2019 Season

```{r}

#filtered for snow-on. first day of accumulation was 10/26/18 last day of melt was 7/12/19
#grouped albedo by the mean of albedo values (mean = 0.6480233)

sasp_18_19 <- sasp_alb_depth %>%
  filter(date > "2018-10-24",
         date < "2019-07-13")%>%
  filter(date != c("2019-03-13"),
         date != c("2019-03-14"))%>%
  mutate(group = ifelse(alb_unfilt <0.6, "Albedo<0.6", "Albedo>0.6"))

ggplot(sasp_18_19, aes(x=delta_snow_depth_cm, y=delta_albedo, 
                       color = date, shape = group))+
  geom_hline(yintercept=0)+
  geom_vline(xintercept=0)+
  geom_point()+
  theme_bw()+
  labs(title = "Change in albedo and snow depth at SASP: 10/25/2018 - 07/12/2019",
       x=expression(Delta*" Snow Depth (cm)"), y=expression(Delta*" Broadband Albedo"))

#With regression line
ggplot(sasp_18_19, aes(x=delta_snow_depth_cm, y=delta_albedo, 
                       color = date))+
  geom_hline(yintercept=0)+
  geom_vline(xintercept=0)+
  geom_point()+
  theme_bw()+
  labs(title = "Change in albedo and snow depth at SASP: 10/25/2018 - 07/12/2019",
       x=expression(Delta*" Snow Depth (cm)"), y=expression(Delta*" Broadband Albedo"))+
  geom_smooth(method = "lm", se = FALSE, color = "black")+
  stat_regline_equation(label.x.npc = 0.5, label.y.npc = 0.95)

ggplot(sasp_18_19, aes(x=delta_snow_depth_cm, y=alb_unfilt, 
                       color = date, shape = group))+
  geom_hline(yintercept=0)+
  geom_vline(xintercept=0)+
  geom_point()+
  theme_bw()+
  labs(title = "Albedo vs changes in snow depth at SASP: 10/25/2018 - 07/12/2019",
       x=expression(Delta*" Snow Depth (cm)"), y=expression("Broadband Albedo"))

#Depth versus albeo with stat regression line
ggplot(sasp_18_19, aes(x=snow_depth_cm, y=alb_unfilt, 
                       color = date))+
  geom_hline(yintercept=0)+
  geom_vline(xintercept=0)+
  geom_point()+
  theme_bw()+
  labs(title = "Albedo vs snow depth at SASP: 10/25/2018 - 07/12/2019",
       x=expression("Snow Depth (cm)"), y=expression("Broadband Albedo"))+
  geom_smooth(method = "lm", se = FALSE, color = "black")+
  stat_regline_equation(label.x.npc = 0.6, label.y.npc = 0.5)

#Without regression line
ggplot(sasp_18_19, aes(x=snow_depth_cm, y=alb_unfilt, 
                       color = date))+
  geom_hline(yintercept=0)+
  geom_vline(xintercept=0)+
  geom_point()+
  theme_bw()+
  labs(title = "Albedo vs snow depth at SASP: 10/25/2018 - 07/12/2019",
       x=expression("Snow Depth (cm)"), y=expression("Broadband Albedo"))

#With a line (to trace dates)
ggplot(sasp_18_19, aes(x=snow_depth_cm, y=alb_unfilt, 
                       color = date))+
  geom_hline(yintercept=0)+
  geom_vline(xintercept=0)+
  geom_point()+
  geom_path()+
  theme_bw()+
  labs(title = "Albedo vs snow depth at SASP: 10/25/2018 - 07/12/2019",
       x=expression("Snow Depth (cm)"), y=expression("Broadband Albedo"))


```

