---
title: "snotel_preliminary
author: "Danielle Reimanis"
date: "10/08/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}

library(dplyr)
library(tidyverse)
library(ggplot2)
library(tidyr)
library(RNRCS)
library(tmap)
library(sf)
library(raster)
library(mapview)
library(rgdal)
library(tigris)

```

```{r}

meta_snotel <- grabNRCS.meta(ntwrks= 'SNTL', cnvrt.elev = TRUE)

snotel_co <- meta_snotel$SNTL%>%
  filter(state=='CO')%>%
  filter(county %in% c('Gunnison','San Juan', 'San Miguel','Dolores','La Plata','Hinsdale', 'Ouray', 'Montrose'))
  
red_mtn_pass <- grabNRCS.data(network = 'SNTL', site_id  = '713',
                              timescale = 'daily',
                                DayBgn = '2017-08-01', DayEnd = '2019-10-01')

lizard_head_pass  <- grabNRCS.data(network = 'SNTL', site_id  = '586',
                              timescale = 'daily',
                                DayBgn = '2017-08-01', DayEnd = '2019-10-01')

# ggplot(lizard_head_pass, aes(x = as.POSIXct(Date), 
#                              y = Snow.Water.Equivalent..in..Start.of.Day.Values))+
#   geom_point()

```

Pulling SNOTEL sites with similar elevation and lat/long nad identifying counties
```{r}

snotel_co$latitude <- as.numeric(as.character(snotel_co$latitude))
snotel_co$longitude <- as.numeric(as.character(snotel_co$longitude))

min(snotel_co$latitude)
max(snotel_co$latitude)
min(snotel_co$longitude)
max(snotel_co$longitude)

snotel_co_mapping <- snotel_co %>%
  dplyr::select(site_name, latitude, longitude, elev_m, county, site_id)

coordinates(snotel_co_mapping) <- c("longitude","latitude")
proj4string(snotel_co_mapping) <- (CRS("+init=epsg:4326"))
colorado_counties <- counties(state= "CO", cb = TRUE)

mapview(snotel_co_mapping)

relevant_counties <- subset(colorado_counties, NAME %in% c('Gunnison','San Juan', 'San Miguel','Dolores','La Plata','Hinsdale', 'Ouray','Montrose'))

mapview(relevant_counties)

  

```


Plotting all SNOTEL and all SBBSP on one
```{r}
site_name <- c("SASP", "SBSP")
site_lat <- c(37.906909, 37.906879)
site_long <- c(-107.711317, -107.726259)
site_elev <- c(3371, 3714)
site_county <- c("NA", "NA")
site_id <- c("SBBSP", "SBBSP")

sbbsp <- data.frame(site_name, site_lat, site_long, site_elev, site_county, site_id)

coordinates(sbbsp) <- c("site_long","site_lat")
proj4string(sbbsp) <- (CRS("+init=epsg:4326"))


tm_shape(relevant_counties) +
  tm_fill(col = "NAME",
          title = "County Name") +
  tm_shape(snotel_co_mapping) +
  tm_dots(size = 0.5,
          col = "site_name",
          title = "Site Name")+
  tm_shape(sbbsp)+
  tm_dots(size = 1,
             col = "site_name",
             palette = c("yellow", "black"),
             title = "Senator Beck Basin Study Area")+
  tm_layout(legend.title.size = 1,
          legend.text.size = 0.6,
          legend.position = c("left","center"))


#TMAP without gunnison

relevant_counties_nogun <- subset(colorado_counties, NAME %in% c('San Juan', 'San Miguel','Dolores','La Plata','Hinsdale', 'Ouray','Montrose')

snotel_nogun <- subset(snotel_co_mapping, county %in% c('San Juan', 'San Miguel','Dolores','La Plata','Hinsdale', 'Ouray','Montrose'))
                       
tm_shape(relevant_counties_nogun)+
  tm_fill(col = "NAME",
          title = "County Name") +
  tm_shape(snotel_nogun)+
  tm_dots(size = 0.5,
          col = "site_name",
          title = "Site Name",
          palette = "viridis")+
  tm_shape(sbbsp)+
  tm_markers(size = 1,
             col = "site_name",
             palette = c("yellow", "black"),
             title = "Senator Beck Basin Study Area")+
  tm_layout(legend.title.size = 1,
          legend.text.size = 0.6,
          legend.position = c("left","center"))

```


Mapping SBSP and SASP (as well as Red Mountain Pass Snotel and Lizard Head Pass Snotel)

```{r}
# 
# utmE <- c(261631, 260317, 243202, 261138)
# utmN <- c(4198953, 4198988, 4187633, 4198200)
# elev <- c(3371, 3714, 3109, 3414)
# site <- c('SASP', 'SBSP', 'LHP_SNTL', 'RMP_SNTL')
# type <- c('SBBSP', 'SBBSP', 'SNTL', 'SNTL')
# 
# #SBSP sits at 3714 meters high and at latitude:  37.907 and longitude: -107.726
# #SASP sits at 3371 meters high and at latitude: 37.907 and longitude: -107.711
# 
# location_data_raw <- cbind(site, utmE, utmN, elev, type) %>%
#   as.data.frame()
# 
# location_data <- location_data_raw %>%
#   mutate(site = as.character(site),
#          type = as.character(type),
#          utmE = as.numeric(as.character(utmE)),
#          utmN = as.numeric(as.character(utmN)),
#          elev = as.numeric(as.character(elev)))
# 
# spatial_points <- location_data %>%
#   st_as_sf(coords=c('utmE','utmN'), crs=26913)
# 
# buffer_point <- spatial_points%>%
#   filter(site == 'SBSP')
# 
# buffer_20km <- st_buffer(buffer_point, 20000)
# co_elev <- elevatr::get_elev_raster(buffer_20km,z=11)
# elev_clip <- crop(co_elev, buffer_20km)
# 
# basemap <- tm_shape(elev_clip) + 
#   tm_raster(palette = 'Greys',
#             title = "Elevation (m)")+ 
#   tm_compass(type = "4star", size = 6)+
#   tm_scale_bar(position = c(0.1, 0.05), text.size = 0.6)
# 
# tm_shape(elev_clip) + 
#   tm_raster(palette = 'Greys',
#             title = "Elevation (m)")+
#   tm_shape(spatial_points %>% filter(type == 'SNTL')) + 
#   tm_bubbles(size = 1,
#              col = "elev",
#              title = "Elevation of Sites (m)",
#              palette ='viridis',
#              alpha = 0.7)
#   
# 
# ### Trying to plot snotel vs sbbsp to determine which snotel may be best. Stuck on making snotel one type of figure vs sbbsp
# 
#   tm_markers(col = "elev",
#              shape = marker_icon(),
#              title = "Elevation of Sites (m)",
#              style = "cont",
#              size = 1, 
#              palette ='viridis',
#              alpha = 0.7)+
#   tm_text('site', size = 0.5)+
#   tm_compass(type = "4star", size = 6)+
#   tm_scale_bar(position = c(0.1, 0.05), text.size = 0.6)
# 
# ?tm_squares
# 
# 
#  tm_shape(spatial_points %>% filter(type == 'SBBSP')) + 
#   tm_dots(col = "elev",
#           title = "Elevation of Sites (m)",
#           style = "cont",
#           size = 1, 
#           palette ='viridis',
#           alpha = 0.7)+

```




#### OKAY NEXT STEPS OVER HERE!!!!!

Consider creating a loop to pull data from all SNOTEL stations nearby. Then start the analysis there. Which is best? That's a whole nother Thesis... just compare snoetl stations to create logic for why you chose the few you did. Spatial Variability is key.

