---
title: "Winter Seasons (2017-2019)"
author: "Danielle Reimanis"
date: "10/15/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(tidyverse)
library(ggplot2)
library(tidyr)
library(lubridate)
library(darksky)
library(xts)
library(dygraphs)
library(ggthemes)
library(suncalc)
library(RNRCS)


```

Organizing the data - August 2017 - August 2019
(SASP, SBSP, Red Mountain Pass SNOTEL, sunlight data)

```{r}
sasp_og <- read.csv('data/SASP_1hr.csv')
sbsp_og <- read.csv('data/SBSP_1hr.csv')

# #red_mtn_pass <- grabNRCS.data(network = 'SNTL', site_id  = '713',
#                               timescale = 'daily',
#                                 DayBgn = '2017-08-01', DayEnd = '2019-07-31')
#save(red_mtn_pass, file = "data/red_mtn_pas.Rdata")

load("data/red_mtn_pas.Rdata")

date <- seq.Date(from = as.Date("2017-08-01", tz = "MST"), 
                 to = as.Date("2019-07-31", tz = "MST"), 
                 by = 1)

sunlight_data <- getSunlightTimes(date = date,
                                  lat = 37.9, 
                                  lon = -107.7, 
                                  tz = "MST", 
                                  keep = c("sunrise", "solarNoon", "sunset"))

sbsp <- sbsp_og   %>%
  mutate(., Date = mdy(Date))%>%
  mutate(., Hour0 = ifelse(nchar(Hour) < 4, 
                          paste0("0", Hour), Hour))%>%
  rename("date" = Date)%>%
  mutate(., datetime_test = paste(date, Hour0, sep = " "),
         datetime = ymd_hm(datetime_test, tz = "MST"))%>%
  filter(datetime >= "2017-08-01 01:00:00")%>%
  filter(datetime <= "2019-08-01 00:00:00")

sasp <- sasp_og %>%
  mutate(., Date = mdy(Date))%>%
  mutate(., Hour0 = ifelse(nchar(Hour) < 4, 
                          paste0("0", Hour), Hour))%>%
  rename("date" = Date)%>%
  mutate(., datetime_test = paste(date, Hour0, sep = " "),
         datetime = ymd_hm(datetime_test, tz = "MST"))%>%
  filter(datetime >= "2017-08-01 01:00:00")%>%
  filter(datetime <= "2019-08-01 00:00:00")

# Datetimes do not match starting 2019-08-13, therefore I am removing all days after 07/31/2020 at midnight This analysis was done and then I went back to change the code above. It will not work now because all values are TRUE.
# 
# datetime_sasp <- sasp$datetime
# datetime_sbsp <- sbsp$datetime
# 
# datetime_confirmation <- data.frame(sbsp = datetime_sbsp, sasp = datetime_sasp)%>%
#   mutate(check = ifelse(datetime_sasp == datetime_sbsp, "TRUE", "FALSE"))%>%
#   filter(check == "FALSE")


sbsp_sunlight_combined <- sunlight_data %>%
  mutate(sunrise = as.POSIXct(sunrise),
         sunset = as.POSIXct(sunset))%>%
  inner_join(sbsp, by = 'date')%>%
  mutate(day_night = ifelse(datetime > sunrise &
                              datetime < sunset, 'day', 'night'))%>%
  mutate(noon_time = format(solarNoon, "%H:%M:%S"))%>%
  mutate(noon = ifelse(hour(datetime) == hour(solarNoon), 'noon', 'NA'))

sasp_sunlight_combined <- sunlight_data %>%
  mutate(sunrise = as.POSIXct(sunrise),
         sunset = as.POSIXct(sunset))%>%
  inner_join(sasp, by = 'date')%>%
  mutate(day_night = ifelse(datetime > sunrise &
                              datetime < sunset, 'day', 'night'))%>%
  mutate(noon_time = format(solarNoon, "%H:%M:%S"))%>%
  mutate(noon = ifelse(hour(datetime) == 12, 'noon', 'NA'))

sbsp_noon <- sbsp_sunlight_combined%>%
  filter(noon == "noon")

sasp_noon <- sasp_sunlight_combined%>%
  filter(noon == "noon")

# save(sasp_noon, file = "data/sasp_noon.Rdata")
write.csv(sasp$datetime, "data/sasp_hours.csv")


```

Versgehy 1991 albedo model on 2017-2018
```{r}

red_mtn_pass_assumed_snow_2017_18 <- red_mtn_pass %>%
  select(1:4, 6:8)%>%
  rename("date" = 1,
         "temp_avg_F" = 2,
         "temp_max_F" = 3,
         "temp_min_F" = 4,
         "precip_accum_in" = 5,
         "snow_depth_in" = 6,
         "SWE_in" = 7)%>%
  filter(date < "2018-07-01")%>%
  mutate(snow_accum = snow_depth_in - lag(snow_depth_in),
         snow_accum_pos = ifelse(snow_accum < 0, 0, snow_accum),
         temp_avg_C = ((temp_avg_F - 32)*(5/9)))%>%
  mutate(date = ymd(date))

albedo_df_test_17 <- red_mtn_pass_assumed_snow_2017_18 %>%
  filter(!is.na(snow_accum),
         !is.na(snow_accum_pos))%>%
  mutate(bare_albedo = 0.25,
         cume_snow = cumsum(snow_accum_pos),
         fresh_albedo = ifelse(snow_accum_pos > 0, 0.84, NA),
         albedo_min = ifelse(temp_avg_C < 0 & snow_accum_pos == 0, 0.7, 
                             ifelse(temp_avg_C >= 0, 0.5, NA)),
         albedo_min = ifelse(temp_avg_C > 0 & cume_snow == lag(cume_snow), 
                             0.25, albedo_min))%>%
  mutate(actual_albedo = ifelse(cume_snow == 0,bare_albedo,NA),
         actual_albedo = ifelse(snow_accum_pos > 0, 0.84, actual_albedo),
         actual_albedo = ifelse(snow_depth_in == 0, 0.25, actual_albedo))
         
albedo_17 = albedo_df_test_17$actual_albedo

for(i in 1:nrow(albedo_df_test_17)){
  if(is.na(albedo_17[i])){
    albedo_17[i] = ((albedo_17[i-1]*exp(-0.01)))
  }
}

albedo_df_test_17$actual_albedo <- albedo_17

ggplot(albedo_df_test_17,aes(x=date,y=actual_albedo)) +
  geom_line()+
  theme_bw()+
  labs(x='Day', y='Albedo')

```

Versgehy 1991 albedo model on 2018-2019

```{r}

red_mtn_pass_assumed_snow_2018_19 <- red_mtn_pass %>%
  select(1:4, 6:8)%>%
  rename("date" = 1,
         "temp_avg_F" = 2,
         "temp_max_F" = 3,
         "temp_min_F" = 4,
         "precip_accum_in" = 5,
         "snow_depth_in" = 6,
         "SWE_in" = 7)%>%
  filter(date > "2018-09-01")%>%
  mutate(snow_accum = snow_depth_in - lag(snow_depth_in),
         snow_accum_pos = ifelse(snow_accum < 0, 0, snow_accum),
         temp_avg_C = ((temp_avg_F - 32)*(5/9)))%>%
  mutate(date = ymd(date))

albedo_df_test_18 <- red_mtn_pass_assumed_snow_2018_19 %>%
  filter(!is.na(snow_accum),
         !is.na(snow_accum_pos))%>%
  mutate(bare_albedo = 0.25,
         cume_snow = cumsum(snow_accum_pos),
         fresh_albedo = ifelse(snow_accum_pos > 0, 0.84, NA),
         albedo_min = ifelse(temp_avg_C < 0 & snow_accum_pos == 0, 0.7, 
                             ifelse(temp_avg_C >= 0, 0.5, NA)),
         albedo_min = ifelse(temp_avg_C > 0 & cume_snow == lag(cume_snow), 
                             0.25, albedo_min))%>%
  mutate(actual_albedo = ifelse(cume_snow == 0,bare_albedo,NA),
         actual_albedo = ifelse(snow_accum_pos > 0, 0.84, actual_albedo),
         actual_albedo = ifelse(snow_depth_in == 0, 0.25, actual_albedo))
         
albedo_18 = albedo_df_test_18$actual_albedo

for(i in 1:nrow(albedo_df_test_18)){
  if(is.na(albedo_18[i])){
    albedo_18[i] = ((albedo_18[i-1]*exp(-0.01))) ### Extinction coefficient is either 0.01, likely not 0.24. 
  }
}

albedo_df_test_18$actual_albedo <- albedo_18

ggplot(albedo_df_test_18,aes(x=date,y=actual_albedo)) +
  geom_line()+
  theme_bw()+
  labs(x='Day', y='Albedo')


```


SASP snow depth against albedo for SASP and SBSP
```{r}

sasp_noon_17 <- sasp_noon%>%
  filter(date < "2018-07-01")%>%
  mutate(Sno_Height_M = ifelse(is.na(Sno_Height_M), 0, Sno_Height_M))

ggplot(sasp_noon_17, aes(x=date, y=Sno_Height_M))+
  geom_line()+
  theme_bw()

sasp_noon_17_alb_depth <- sasp_noon_17%>%
  select(date, 22:25, Sno_Height_M)%>%
  mutate(Filtered_Albedo = PyDwn_Filt_W/PyUp_Filt_W,
         Unfiltered_Albedo = PyDwn_Unfilt_W/PyUp_Unfilt_W,
         snow_height_cm = Sno_Height_M*100)

sasp_noon_17_alb_depth_graph <- sasp_noon_17_alb_depth %>%
  select(1, 6:9)%>%
  gather(., key = "Filt_Unfilt", value = "Albedo", 
         -date, -Sno_Height_M, -snow_height_cm)
  
ggplot(sasp_noon_17_alb_depth_graph)+
  geom_line(aes(x=date, y=Albedo, color=Filt_Unfilt))+
  scale_color_manual(values = c("red","black"))+
  labs(x="Date", y="Snow Height (m) & Albedo")+
  geom_bar(aes(x=date, y=Sno_Height_M), stat = 'identity', fill="steelblue")+
  theme_bw()+
  labs(x="Date", y="Snow Height (m) & Albedo", 
       title = "Winter 2017-18 SASP Albedo versus SASP Snow Depth (m)")+
  theme(legend.title = element_blank())


#The following graph was filtered to remove albedo > 1
ggplot(sasp_noon_17_alb_depth_graph %>% filter(Albedo <= 1))+
  geom_bar(aes(x=date, y=Sno_Height_M), stat = 'unique', fill="steelblue")+
  geom_line(aes(x=date, y= Albedo, color=Filt_Unfilt))+
  scale_y_continuous(name = "Albedo", sec.axis = sec_axis(~.*100, name="Snow Height (cm)"))+
  theme_bw()+
  scale_color_manual(values = c("red","black"))+
  labs(x="Date", y="Snow Height (m) & Albedo")+
  labs(x="Date", 
       title = "Winter 2017-18 SASP Albedo versus SASP Snow Depth")+
  theme(legend.title = element_blank())
  

## The following code is for the Winter Season 2018-2019

sasp_noon_18 <- sasp_noon%>%
  filter(date >= "2018-09-01")%>%
  mutate(Sno_Height_M = ifelse(is.na(Sno_Height_M), 0, Sno_Height_M))

sasp_noon_18_graph <- sasp_noon_18%>%
  filter(date != c("2019-03-24"),
         date != c("2019-03-22"),
         date != c("2019-03-15"))
  
ggplot(sasp_noon_18_graph, aes(x=date, y=Sno_Height_M))+
  geom_line()+
  theme_bw()

sasp_noon_18_alb_depth <- sasp_noon_18%>%
  select(date, 22:25, Sno_Height_M)%>%
  mutate(Filtered_Albedo = PyDwn_Filt_W/PyUp_Filt_W,
         Unfiltered_Albedo = PyDwn_Unfilt_W/PyUp_Unfilt_W,
         snow_height_cm = Sno_Height_M*100)

sasp_noon_18_alb_depth_graph <- sasp_noon_18_alb_depth %>%
  select(1, 6:9)%>%
  gather(., key = "Filt_Unfilt", value = "Albedo", 
         -date, -Sno_Height_M, -snow_height_cm)
  
ggplot(sasp_noon_18_alb_depth_graph)+
  geom_line(aes(x=date, y=Albedo, color=Filt_Unfilt))+
  scale_color_manual(values = c("red","black"))+
  labs(x="Date", y="Snow Height (m) & Albedo")+
  geom_bar(aes(x=date, y=Sno_Height_M), stat = 'identity', fill="steelblue")+
  theme_bw()


#The following graph was filtered to remove albedo > 1
ggplot(sasp_noon_18_alb_depth_graph %>% filter(Albedo <= 1))+
  geom_bar(aes(x=date, y=Sno_Height_M), stat = 'unique', fill="steelblue")+
  geom_line(aes(x=date, y= Albedo, color=Filt_Unfilt))+
  scale_y_continuous(name = "Albedo", sec.axis = sec_axis(~.*100, name="Snow Height (cm)"))+
  theme_bw()+
  scale_color_manual(values = c("red","black"))+
  labs(x="Date", y="Snow Height (m) & Albedo")+
  labs(x="Date", 
       title = "Winter 2018-19 SASP Albedo versus SASP Snow Depth")+
  theme(legend.title = element_blank())

ggplot(sasp_noon_18_alb_depth_graph %>% filter(Albedo <= 1))+
  geom_line(aes(x=date, y= Albedo, color=Filt_Unfilt))+
  scale_color_manual(values = c("red","black"))+
  labs(x="Date", y= "Albedo")+
  theme_bw()


```

Red Mountain Pass Snow Depth to SASP Snow Depth

```{r}

red_mtn_pass_assumed_snow <- red_mtn_pass_assumed_snow_2017_18%>%
  rbind(., red_mtn_pass_assumed_snow_2018_19)

rmp_snotel_simple <- red_mtn_pass_assumed_snow%>%
  mutate(snow_depth_cm = snow_depth_in*2.54,
         SWE_cm = SWE_in*2.54,
         snow_accum_pos_cm = snow_accum_pos*2.54,
         date = as.Date(date))%>%
  filter(date <= "2019-07-31")%>%
  select(date, SWE_cm, snow_depth_cm, snow_accum_pos_cm, temp_avg_C)

ggplot(rmp_snotel_simple, aes(x = date, y=snow_depth_cm))+
  geom_line()+
  theme_bw()

#Breaking it Up into years

rmp_snotel_17 <- rmp_snotel_simple %>%
  filter(date < "2018-07-01")
  
rmp_snotel_18 <- rmp_snotel_simple %>%
  filter(date >= "2018-09-01")

sasp_snotel_17 <- rmp_snotel_17 %>%
  select(1:3,5)%>%
  rename(snotel_SWE_cm = 2,
         snotel_depth_cm = 3,
         snotel_temp_c = 4)%>%
  inner_join(sasp_noon_17_alb_depth, by = "date")

ggplot(sasp_snotel_17, aes(x=snotel_depth_cm, y=snow_height_cm))+
  geom_point()+
  geom_abline()+
  theme_bw()+
  labs(x="Snow Depth at RMS_SNOTEL (cm)", 
       y = "Snow Depth at SASP (cm)", 
       title = "Snow Depth at SASP vs Red Mountain Pass SNOTEL, Winter 2017-18")

sasp_snotel_17_graph <- sasp_snotel_17%>%
  select(1,3,12)%>%
  rename(SNOTEL = 2,
         SASP = 3)%>%
  gather(key = "Location", 
         value = "snow_depth_cm", -date)
  
ggplot(sasp_snotel_17_graph, aes(x=date, y=snow_depth_cm, color = Location))+
  geom_line()+
  theme_bw()+
  scale_color_manual(values = c("dodgerblue4","tan2"))+
  labs(x="Date", y="Snow Depth (cm)", 
       title= "SASP vs Red Mountain Pass SNOTEL Depth, Winter 2017-18")

## The following is for 2018-2019
  
sasp_snotel_18 <- rmp_snotel_18 %>%
  select(1:3,5)%>%
  rename(snotel_SWE_cm = 2,
         snotel_depth_cm = 3,
         snotel_temp_c = 4)%>%
  inner_join(sasp_noon_18_alb_depth, by = "date")

ggplot(sasp_snotel_18, aes(x=snotel_depth_cm, y=snow_height_cm))+
  geom_point()+
  geom_abline()+
  theme_bw()+
  labs(x="Snow Depth at RMS_SNOTEL (cm)", 
       y = "Snow Depth at SASP (cm)", 
       title = "Snow Depth at SASP vs Red Mountain Pass SNOTEL, Winter 2018-19")

sasp_snotel_18_graph <- sasp_snotel_18%>%
  select(1,3,12)%>%
  rename(SNOTEL = 2,
         SASP = 3)%>%
  gather(key = "Location", 
         value = "snow_depth_cm", -date)%>%
  filter(date != c("2019-03-24"),
         date != c("2019-03-22"),
         date != c("2019-03-15"))
  
ggplot(sasp_snotel_18_graph, aes(x=date, y=snow_depth_cm, color = Location))+
  geom_line()+
  theme_bw()+
  scale_color_manual(values = c("dodgerblue4","tan2"))+
  labs(x="Date", y="Snow Depth (cm)", 
       title= "SASP vs Red Mountain Pass SNOTEL Depth, Winter 2018-19")

#### Combining both years

# view(rmp_snotel_simple)
# str(rmp_snotel_simple)
# names(sasp_noon)
# str(sasp_noon_two_years)

sasp_noon_two_years <- sasp_noon%>%
  select(date, 22:25, Sno_Height_M)%>%
  mutate(Sno_Height_M = ifelse(is.na(Sno_Height_M), 0, Sno_Height_M))%>%
  mutate(Filtered_Albedo = PyDwn_Filt_W/PyUp_Filt_W,
         Unfiltered_Albedo = PyDwn_Unfilt_W/PyUp_Unfilt_W,
         snow_height_cm = Sno_Height_M*100)

rmp_sasp_two_years <- rmp_snotel_simple%>%
  select(1:3,5)%>%
  rename(snotel_SWE_cm = 2,
         snotel_depth_cm = 3,
         snotel_temp_c = 4)%>%
  inner_join(sasp_noon_two_years, by = "date")

ggplot(rmp_sasp_two_years, aes(x=snotel_depth_cm, y=snow_height_cm))+
  geom_point()+
  geom_abline()+
  theme_bw()+
  labs(x="Snow Depth at RMS_SNOTEL (cm)", 
       y = "Snow Depth at SASP (cm)", 
       title = "Snow Depth at SASP vs Red Mountain Pass SNOTEL, 2017-2019")

sasp_snotel_twoyears_graph <- rmp_sasp_two_years%>%
  select(1,3,12)%>%
  rename(SNOTEL = 2,
         SASP = 3)%>%
  gather(key = "Location", 
         value = "snow_depth_cm", -date)%>%
  filter(date != c("2019-03-24"),
         date != c("2019-03-22"),
         date != c("2019-03-15"))

ggplot(sasp_snotel_twoyears_graph, aes(x=date, y=snow_depth_cm, color = Location))+
  geom_line()+
  theme_bw()+
  scale_color_manual(values = c("dodgerblue4","tan2"))+
  labs(x="Date", y="Snow Depth (cm)", 
       title= "SASP vs Red Mountain Pass SNOTEL Depth, 2017-2019")


```

Change in Snow Depth at RMP and SASP

```{r}

change_in_depth <- rmp_sasp_two_years %>%
  select(1,3,4,10:12)%>%
  rename("sasp_snow_depth_cm" = 6)%>%
  mutate(snotel_change_cm = snotel_depth_cm - lag(snotel_depth_cm),
         sasp_change_cm = sasp_snow_depth_cm - lag(sasp_snow_depth_cm))%>%
  filter(sasp_change_cm < 50 & sasp_change_cm >-100)


ggplot(change_in_depth, aes(x=snotel_change_cm, y=sasp_change_cm))+
  geom_point()+
  theme_bw()+
  geom_abline()

change_in_depth_graphing <- change_in_depth %>%
  select(1, 7:8)%>%
  gather(key = "snotel_sasp", value = "change_depth_cm", -date)

ggplot(change_in_depth_graphing, aes(x= date, y= change_depth_cm, color = snotel_sasp))+
  geom_point(size = 1)+
  theme_bw()+
  scale_color_manual(values = c("dodgerblue4","tan2"))

ggplot(change_in_depth_graphing %>% filter(change_depth_cm > 0))+
  geom_point(size = 1, aes(x= date, y= change_depth_cm, color = snotel_sasp))+
  theme_bw()+
  scale_color_manual(values = c("dodgerblue4","tan2"))

```

SASP albedo and change in snow depth at SASP

```{r}

sasp_change_depth_alb <- rmp_sasp_two_years %>%
  select(1, 10:12)%>%
  mutate(change_depth_cm = snow_height_cm - lag(snow_height_cm))%>%
  gather(., key = "Filt_Unfilt", value = "Albedo", 
         -date, -snow_height_cm, -change_depth_cm)%>%
  filter(date != c("2019-03-15"),
         date != c("2019-03-16"),
         date != c("2019-03-22"),
         date != c("2019-03-23"),
         date != c("2019-03-24"),
         date != c("2019-03-25"),
         date != c("2019-07-11"))%>%
  mutate(change_depth_cm_graph = change_depth_cm/20)%>%
  filter(Albedo < 1)

ggplot(sasp_change_depth_alb)+
  geom_bar(aes(x=date, y=change_depth_cm_graph), stat = 'unique', fill="steelblue")+
  geom_line(aes(x=date, y= Albedo, color=Filt_Unfilt), size =0.3)+
  scale_y_continuous(name = "Albedo", 
                     sec.axis = sec_axis(~.*20, name="Change in Snow Depth (cm)"))+
  scale_color_manual(values = c("red","black"))+
  theme_bw()+
  labs(title = "SASP Albedo versus changes in Snow Depth")

```


Breaking previous graph into two datasets based on date

```{r}

sasp_change_2017 <- sasp_change_depth_alb%>%
  filter(date < "2018-07-01")

ggplot(sasp_change_2017)+
  geom_bar(aes(x=date, y=change_depth_cm_graph), stat = 'unique', fill="steelblue")+
  geom_line(aes(x=date, y= Albedo, color=Filt_Unfilt), size =0.3)+
  scale_y_continuous(name = "Albedo", 
                     sec.axis = sec_axis(~.*20, name="Change in Snow Depth (cm)"))+
  scale_color_manual(values = c("red","black"))+
  theme_bw()+
  labs(title = "2017-18 SASP Albedo versus changes in Snow Depth")


sasp_change_2018 <- sasp_change_depth_alb%>%
  filter(date > "2018-09-01")

ggplot(sasp_change_2018)+
  geom_bar(aes(x=date, y=change_depth_cm_graph), stat = 'unique', fill="steelblue")+
  geom_line(aes(x=date, y= Albedo, color=Filt_Unfilt), size =0.3)+
  scale_y_continuous(name = "Albedo", 
                     sec.axis = sec_axis(~.*20, name="Change in Snow Depth (cm)"))+
  scale_color_manual(values = c("red","black"))+
  theme_bw()+
  labs(title = "2018-19 SASP Albedo versus changes in Snow Depth")
```


Snow depth vs Red Mountain Pass SNOTEL against albedo, SASP

*Not finished*

```{r}

names(red_mtn_pass_assumed_snow_2017_18)

snow_depth_alb_17 <- red_mtn_pass_assumed_snow_2017_18%>%
  mutate(snow_depth_cm = snow_depth_in*2.54,
         SWE_cm = SWE_in*2.54,
         snow_accum_pos_cm = snow_accum_pos*2.54)%>%
  select(date, SWE_cm, snow_depth_cm, snow_accum_pos_cm)

```

