---
title: "Dust Events at SBB"
author: "Danielle Reimanis"
date: "1/29/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(tidyverse)
library(tidyr)
library(lubridate)
library(ggthemes)
library(ggpubr)
library(ggplot2)
library(stringr)
library(purrr)
library(xts)
library(dygraphs)

```

### Reading in Dust Data
```{r}

dust_files <- list.files('data/Dust_Events', full.names = TRUE)

dust_read_in <- function(file){
  data_names = str_sub(file, -8,-5)
  name = paste("WY", data_names, sep = "")
 df <- read_delim(file = file, delim = " ", col_names=TRUE)%>%
  mutate(date = mdy(date))%>%
  mutate_if(is.character, as.numeric)%>%
  mutate(WY = name)%>%
  rename("date" =1, "doy"=2,"dust_event"=3)
return(df)
}

dust_06_14 <- map_dfr(dust_files, dust_read_in)

```

## Dust Events by Year
```{r}

events_yearly <- dust_06_14%>%
  filter(!is.na(dust_event))%>%
  mutate(DE_1 = ifelse(dust_event >0,1,NA))
  
ggplot(events_yearly, aes(x=date))+
  geom_col(aes(y=DE_1), width = 1)+
  facet_wrap(~WY, scales="free_x")+
  theme_bw()

```

## Connecting DE to SASP Radiation Data
```{r}

load("data/sasp_final_05_14.Rdata")

sasp_alb_dust <- dust_06_14%>%
  select(1,3)%>%
  rename("dust_raw" =2)%>%
  merge(., sasp_final_05_14, by = 'date', all = TRUE)%>%
  mutate(dust_event_num = ifelse(is.na(dust_raw), 0, dust_raw),
         dust_event = ifelse(is.na(dust_raw), 0 ,1))%>%
  select(1,3:23)

```


```{r}

ggplot(sasp_alb_dust%>%filter(!is.na(SY)), aes(x=DOSY))+
  geom_bar(aes(x = DOSY, y = dust_event), stat = 'unique', fill="red")+
  geom_bar(aes(x = DOSY, y = correct_m/4), stat = 'unique', fill="dodgerblue3")+
  geom_line(aes(y=alb_final))+
  facet_wrap(~SY, nrow = 5)+
  theme_bw()+
  scale_y_continuous(name = "Broadband Albedo",
                     sec.axis = sec_axis(~.*4, name = "Depth (m)"))+
  labs(x= "Day of Snow Year")

ggplot(sasp_alb_dust%>%filter(SY == "SY2013"), aes(x=DOSY))+
  geom_bar(aes(x = DOSY, y = dust_event), stat = 'unique', fill="red")+
  geom_bar(aes(x = DOSY, y = correct_m/4), stat = 'unique', fill="dodgerblue3")+
  geom_line(aes(y=alb_obs), color = "yellow3")+
  geom_line(aes(y=alb_final))+
  facet_wrap(~SY, nrow = 5)+
  theme_bw()+
  scale_y_continuous(name = "Broadband Albedo",
                     sec.axis = sec_axis(~.*4, name = "Depth (m)"))+
  labs(x= "Day of Snow Year", title = "SASP Albedo, Depth, and Dust Events",
       subtitle = "Black = corrected albedo, yellow = observed albedo, red = dust event")
```

### Random Hk DyGraph 
```{r}
sasp_incoming_xts <- sasp_alb_dust%>%
  select(1,10,13)%>%
  xts(., order.by = .$date)

sasp_outgoing_xts <- sasp_alb_dust%>%
  select(1,11,14)%>%
  xts(., order.by = .$date)
  
dygraph(sasp_incoming_xts)
dygraph(sasp_outgoing_xts)

```

### Final Data Depth/Albedo Graphs
```{r}

sasp_alb_dust_filter <- sasp_alb_dust%>%
  filter(!is.na(SY))

ggplot(sasp_alb_dust_filter, aes(x=correct_m, y=alb_final))+
  geom_point(aes(color = DOSY))+
  facet_wrap(~SY, nrow = 5)+
  theme_bw()+
  labs(x="Depth (m)", y="Broadband Albedo", title = "SASP Depth vs. Albedo with Day of Snow Year")

ggplot(sasp_alb_dust_filter%>%filter(correct_m < 0.5), aes(x=correct_m, y=alb_final))+
  geom_path(aes(color = DOSY))+
  geom_point(aes(color = DOSY))+
  facet_wrap(~SY, nrow = 5)+
  theme_bw()+
  labs(x="Depth (m)", y="Broadband Albedo", title = "SASP Depth vs. Albedo with Day of Snow Year, filtered to depths <0.5")

ggplot(sasp_alb_dust_filter, aes(x=depth_diff, y=alb_final))+
  geom_point(aes(color = correct_m))+
  facet_wrap(~SY, nrow = 5)+
  theme_bw()+
  labs(x=expression(Delta*"Depth (m)"), y="Broadband Albedo", title = "SASP Depth vs. Albedo with Day of Snow Year")+
  geom_vline(xintercept = 0)

ggplot(sasp_alb_dust_filter, aes(x=depth_diff, y=alb_diff))+
  geom_hline(yintercept = 0)+
  geom_vline(xintercept = 0)+
  geom_point(aes(color = correct_m))+
  facet_wrap(~SY, nrow = 5)+
  theme_bw()+
  labs(x=expression(Delta*"Depth (m)"), y=expression(Delta*"Broadband Albedo"), title = "SASP Depth vs. Albedo with Actual Depth (m)")

ggplot(sasp_alb_dust_filter, aes(x=correct_m, y=alb_diff))+
  geom_hline(yintercept = 0)+
  geom_vline(xintercept = 0)+
  geom_point(aes(color = alb_final))+
  facet_wrap(~SY, nrow = 5)+
  theme_bw()+
  labs(x="Depth (m)", y=expression(Delta*"Broadband Albedo"), title = "SASP Depth vs. Albedo with Actual Depth (m)")



```

### Max Depth
```{r}
peak_depth <- sasp_alb_dust_filter %>%
  group_by(SY)%>%
  mutate(max_depth = max(correct_m),
         SAG = ifelse(lag(correct_m) >0 & correct_m == 0, 1,0))%>%
  ungroup()%>%
  mutate(max_no_depth = ifelse(max_depth == correct_m, 1,0),
         max_no_depth = ifelse(SY == "SY2006" & 
                              lag(max_no_depth) == 1, 1, max_no_depth),
         max_no_depth = ifelse(SY == "SY2010" & 
                              lag(max_no_depth) == 1, 1, max_no_depth),
         SAG = ifelse(DOSY <100, 0, SAG))

```


### Radiation Absorbed
```{r}

hk_absorbed <- peak_depth%>%
  mutate(hk_absorbed = hkin_comb - hkout_comb)

ggplot(hk_absorbed%>%filter(correct_m > 0), aes(x=correct_m, y=hk_absorbed))+
  geom_point(aes(color = DOSY))+
  facet_wrap(~SY, nrow = 5)+
  theme_bw()+
  labs(x="Depth (m)", y = "Absorbed Shortwave Radiation")

ggplot(hk_absorbed%>%filter(correct_m > 0), aes(x=DOSY))+
  geom_col(aes(y = max_no_depth*800))+
  geom_point(aes(y = hk_absorbed, color = correct_m))+
  facet_wrap(~SY, nrow = 5)+
  theme_bw()+
  labs(x="DOSY", y = "Absorbed Shortwave Radiation")

```

### Visible Light Albedo
```{r}
load("data/sasp_05_14_skiles.Rdata")

visible_sasp <- sasp_05_14_skiles%>%
  filter(hour == 12)%>%
  filter(date > "2005-01-24")%>%
  mutate(hvis_in = hkin_unfilt - hkin_filt,
         hvis_out = hkout_unfilt - hkout_filt,
         alb_vis = hvis_out/hvis_in)%>%
  select(1,17:19)%>%
  merge(., hk_absorbed, all = TRUE)%>%
  filter(!is.na(SY))%>%
  mutate(SAG = ifelse(is.na(SAG), 0, SAG))%>%
  filter(alb_vis < 1)%>%
  select(1, 5:29, 2:4)%>%
  mutate(hkin_filt = hkin_comb - hvis_in,
         hkout_filt = hkout_comb - hvis_out,
         alb_filt = hkout_filt/hkin_filt)
  
```

### Vis vs Broadband & Filtered for graphing
```{r}
alb_long<- visible_sasp%>%
  filter(DOSY<300)%>%
  select(1,5:7, 29,8,22,25,24)%>%
  rename("Depth_meters" = correct_m,
         "Broadband" = alb_final,
         "Visible" = alb_vis)%>%
  mutate(dust_event = dust_event*0.5,
         max_no_depth = max_no_depth*0.5)%>%
  gather(key = "type", value = "albedo", 
         -date, -Depth_meters, -max_no_depth,-dust_event,-SY,-DOSY,-SAG)

alb_long_nir_swir <- visible_sasp%>%
  filter(DOSY<300)%>%
  select(1,5:6, 32, 29,8,22,24,25)%>%
  rename("Depth_meters" = correct_m,
         "NIR_SWIR" = alb_filt,
         "Visible" = alb_vis)%>%
  mutate(dust_event = dust_event*0.5,
         max_no_depth = max_no_depth*0.5)%>%
  gather(key = "type", value = "albedo", 
         -date, -Depth_meters, -max_no_depth,-dust_event,-SY,-DOSY,-SAG)

alb_long_all <- visible_sasp%>%
  filter(DOSY<300)%>%
  select(1,5:7, 32, 29,8,22,24,25)%>%
  rename("Depth_meters" = correct_m,
         "NIR_SWIR" = alb_filt,
         "Visible" = alb_vis,
         "Broadband" = alb_final)%>%
  mutate(dust_event = dust_event*0.35,
         max_no_depth = max_no_depth*0.35)%>%
  gather(key = "type", value = "albedo", 
         -date, -Depth_meters, -max_no_depth,-dust_event,-SY,-DOSY, -SAG)

alb_long_pos_all <- visible_sasp%>%
  filter(DOSY<300)%>%
  select(1,5:7, 32, 29,8,9, 22,24,25)%>%
  rename("Depth_meters" = correct_m,
         "NIR_SWIR" = alb_filt,
         "Visible" = alb_vis,
         "Broadband" = alb_final)%>%
  mutate(dust_event = dust_event*(1/3),
         max_no_depth = max_no_depth*(1/3),
         depth_positive = ifelse(depth_diff >0, depth_diff*(1/3), 0),
         depth_diff = depth_diff*(1/3))%>%
  gather(key = "type", value = "albedo", 
         -date, -Depth_meters, -max_no_depth,-dust_event,
         -SY,-DOSY, -depth_diff, -depth_positive, -SAG)
  
```

Visible vs Broadband Graphing
```{r}
ggplot(alb_long_pos_all, aes(x=DOSY))+
  geom_col(aes(y=dust_event), color = "salmon3", width = 0.25)+
  geom_col(aes(y=max_no_depth), width = 2, color = "darkslateblue")+
  geom_col(aes(y=SAG/3), width =2, color = "darkgreen")+
  geom_line(aes(y=albedo, color = type, linetype = type))+
  facet_wrap(~SY, nrow=5)+
  scale_color_manual(values=c("grey22","maroon4","cyan3"))+
  theme_bw()+
  labs(x="Day of Snow Year", y= "Albedo", title = "SASP Albedo and Dust Events", subtitle = "Brown Lines = Dust Event, Black Line = Peak Snow Depth")+
  theme(legend.title = element_blank())

ggplot(alb_long_pos_all%>%filter(DOSY>175), aes(x=DOSY))+
  geom_col(aes(y=dust_event), color = "salmon3", width = 0.25)+
  geom_col(aes(y=max_no_depth), width = 1, fill = "darkslateblue")+
  geom_col(aes(y=SAG/3), width =1, fill = "darkgreen")+
  geom_line(aes(y=albedo, color = type, linetype = type))+
  facet_wrap(~SY, nrow=5)+
  scale_color_manual(values=c("grey22","maroon4","cyan3"))+
  theme_bw()+
  labs(x="Day of Snow Year", y= "Albedo", title = "SASP Albedo and Dust Events", subtitle = "Brown Lines = Dust Event, Purple Line = Peak Snow Depth, Green Line = SAG")+
  theme(legend.title = element_blank())

ggplot(alb_long%>%filter(DOSY>175), aes(x=DOSY))+
  geom_bar(aes(y=Depth_meters/4), stat = 'unique', fill = "steelblue2", width = 0.5)+
  geom_col(aes(y=dust_event), fill = "salmon3", width = 0.5)+
  geom_col(aes(y=max_no_depth), fill = "purple4", width = 0.6)+
  geom_line(aes(y=albedo, color = type))+
  facet_wrap(~SY, nrow=5)+
  scale_color_manual(values=c("grey22","cyan3"))+
  scale_y_continuous(name = "Albedo",
                     sec.axis = sec_axis(~.*4, name = "Depth (m)"))+
  theme_bw()+
  labs(x="Day of Snow Year", title = "SASP Albedo and Dust Events", subtitle = "Brown Lines = Dust Event, Purple Line = Peak Snow Depth")+
  theme(legend.title = element_blank())
  

```

Visible vs NIR/SWIR Plot
```{r}
ggplot(alb_long_nir_swir%>%filter(DOSY>175), aes(x=DOSY))+
  geom_col(aes(y=dust_event/4), color = "salmon3", width = 0.25)+
  geom_col(aes(y=max_no_depth), width = 1, fill = "darkslateblue")+
  geom_line(aes(y=albedo, color = type))+
  geom_col(aes(y=SAG/2), width =1, fill = "darkgreen")+
  facet_wrap(~SY, nrow=5)+
  scale_color_manual(values=c("plum4","cyan3"))+
  theme_bw()+
  labs(x="Day of Snow Year", y= "Albedo", title = "SASP Albedo and Dust Events", subtitle = "Brown Lines = Dust Event, Purple Line = Peak Snow Depth, Green Line = SAG")+
  theme(legend.title = element_blank())

```

All Albedos
```{r}
ggplot(alb_long_all%>%filter(DOSY>175), aes(x=date))+
  geom_col(aes(y=dust_event/4), color = "salmon3", width = 0.25)+
  geom_col(aes(y=max_no_depth), width = 1, fill = "darkslateblue")+
  geom_col(aes(y=SAG/3), width =1, fill = "darkgreen")+
  geom_line(aes(y=albedo, color = type, linetype = type))+
  facet_wrap(~SY, nrow=5, scales = "free_x")+
  scale_color_manual(values=c("grey22","plum4", "cyan3"))+
  theme_bw()+
  labs(x="", y= "Albedo", title = "SASP Albedo and Dust Events", subtitle = "Brown Lines = Dust Event, Purple = Peak Snow Depth, Green = SAG")+
  theme(legend.title = element_blank())

alb_long_all_2 <- alb_long_all%>%
  group_by(type)%>%
  mutate(depth_diff = Depth_meters-lag(Depth_meters),
         depth_diff_pos = ifelse(depth_diff >0,depth_diff,0))%>%
  ungroup()

ggplot(alb_long_all_2%>%filter(DOSY>175), aes(x=date))+
  geom_col(aes(y=dust_event/4), color = "salmon3", width = 0.25)+
  geom_col(aes(y=max_no_depth), width = 1, fill = "darkslateblue")+
  geom_col(aes(y=depth_diff_pos/3), width = 1, fill = "steelblue4")+
  geom_col(aes(y=SAG/3), width =1, fill = "darkgreen")+
  geom_line(aes(y=albedo, color = type, linetype = type))+
  facet_wrap(~SY, nrow=5, scales = "free_x")+
  scale_color_manual(values=c("grey22","plum4", "cyan3"))+
  theme_bw()+
  labs(x="", y= "Albedo", title = "SASP Albedo and Dust Events", subtitle = "Brown Lines = Dust Event, Purple = Peak Snow Depth, Green = SAG")+
  theme(legend.title = element_blank())

ggplot(alb_long_all_2%>%filter(DOSY>175), aes(x=date))+
  geom_col(aes(y=dust_event/4), color = "salmon3", width = 0.25)+
  geom_col(aes(y=depth_diff_pos/3), width = 1, fill = "steelblue4")+
  geom_col(aes(y=SAG/3), width =1, fill = "darkgreen")+
  geom_line(aes(y=albedo, color = type, linetype = type))+
  facet_wrap(~SY, nrow=5, scales = "free_x")+
  scale_color_manual(values=c("grey22","plum4", "cyan3"))+
  theme_bw()+
  labs(x="", y= "Albedo", title = "SASP Albedo and Dust Events", subtitle = "Brown Lines = Dust Event, Purple = Peak Snow Depth, Green = SAG")+
  theme(legend.title = element_blank())

ggplot(alb_long_all%>%filter(DOSY>175), aes(x=DOSY))+
  geom_bar(aes(y=Depth_meters/4), stat = 'unique', fill = "steelblue2", width = 0.5)+
  geom_col(aes(y=dust_event), color = "salmon3", width = 0.25)+
  geom_col(aes(y=max_no_depth), width = 1)+
  geom_line(aes(y=albedo, color = type))+
  facet_wrap(~SY, nrow=5)+
  scale_color_manual(values=c("grey22","plum4", "cyan3"))+
  theme_bw()+
  labs(x="Day of Snow Year", title = "SASP Albedo and Dust Events", subtitle = "Brown Lines = Dust Event, Black Line = Peak Snow Depth")+
  theme(legend.title = element_blank())+
  scale_y_continuous(name = "Albedo",
                     sec.axis = sec_axis(~.*4, name = "Depth (m)"))


```

More Albedo graphs
```{r}

# ggplot(alb_long_pos_all%>%filter(DOSY>175), aes(x=DOSY))+
#   geom_col(aes(y=dust_event), color = "salmon3", width = 0.25)+
#   geom_col(aes(y=max_no_depth), width = 1)+
#   geom_line(aes(y=1.25-depth_positive*4), color = "steelblue2", size = 1)+
#   geom_line(aes(y=albedo, color = type))+
#   facet_wrap(~SY, nrow=5)+
#   scale_color_manual(values=c("grey22","plum4", "cyan3"))+
#   theme_bw()+
#   labs(x="Day of Snow Year", title = "SASP Albedo and Dust Events", subtitle = "Brown Lines = Dust Event, Black Line = Peak Snow Depth")+
#   theme(legend.title = element_blank())+
#   scale_y_continuous(name = "Albedo",
#                      sec.axis = sec_axis(~(1.25-.)/4, name = expression(Delta*"Depth (m)")))


ggplot(alb_long_pos_all%>%filter(DOSY>175), aes(x=DOSY))+
  geom_col(aes(y=dust_event), fill = "salmon3", width = 0.25)+
  geom_col(aes(y=max_no_depth), width = 0.5)+
  geom_col(aes(y=depth_positive), fill = "steelblue2", width = 1)+
  scale_y_reverse(name = expression(Delta*" Depth (m)"),
                     sec.axis = sec_axis(~(1-.)/(3/4), name = "Albedo"))+
  theme_bw()+
  facet_wrap(~SY, nrow=5)+
  geom_line(aes(y=1-albedo*(3/4), color = type))+
  scale_color_manual(values=c("grey22","plum4", "cyan3"))+
  labs(x="Day of Snow Year", title = "SASP Albedo and Dust Events", subtitle = "Brown Lines = Dust Event, Black Line = Peak Snow Depth")+
  theme(legend.title = element_blank())

ggplot(alb_long_pos_all%>%filter(DOSY<100&DOSY>25), aes(x=DOSY))+
  geom_col(aes(y=dust_event), fill = "salmon3", width = 0.25)+
  geom_col(aes(y=max_no_depth), width = 0.5)+
  geom_col(aes(y=depth_positive), fill = "steelblue2", width = 1)+
  scale_y_reverse(name = expression(Delta*" Depth (m)"),
                     sec.axis = sec_axis(~(1-.)/(3/4), name = "Albedo"))+
  theme_bw()+
  facet_wrap(~SY, nrow=5)+
  geom_line(aes(y=1-albedo*(3/4), color = type))+
  scale_color_manual(values=c("grey22","plum4", "cyan3"))+
  labs(x="Day of Snow Year", title = "SASP Albedo and Dust Events", subtitle = "Brown Lines = Dust Event")+
  theme(legend.title = element_blank())

```

More Random Graphs
```{r}

ggplot(visible_sasp%>%filter(DOSY<300), aes(x=DOSY))+
  geom_col(aes(y=dust_event), color = "salmon3", width = 0.5)+
  geom_col(aes(y=max_no_depth), width = 1)+
  geom_line(aes(y=alb_final), color = "black", size = 0.5)+
  geom_line(aes(y=alb_vis, color = correct_m))+
  facet_wrap(~SY, nrow=5)+
  theme_bw()+
  labs(x="Day of Snow Year", y= "Visible Light Albedo", title = "SASP Visible Albedo and Dust Events", subtitle = "Red Lines = Dust Event, Black Line = Peak Snow Depth, Blue Gradient = Depth (m)")+
  theme(legend.title = element_blank())

ggplot(visible_sasp, aes(x=alb_vis, y=alb_final))+
  geom_point(aes(color = correct_m))+
  theme_bw()+
  geom_abline()+
  labs(x="Visible Albedo (305-780nm)", y= "Broadband Albedo (305-2800nm)")
  
ggplot(visible_sasp, aes(x=alb_vis, y=alb_filt))+
  geom_point(aes(color = correct_m))+
  theme_bw()+
  geom_abline()+
  labs(x="Visible Albedo (305-780nm)", y= "NIR/SWIR Albedo (780-2800nm)")


```

## Dust Event Focus

```{r}
pre_post_dust <- function(filter_sy){
    dust_event <- visible_sasp%>%
      filter(SY == filter_sy)%>%
      filter(dust_event == 1)
    
    dosy_dust_event = dust_event$DOSY
    
    startframe <- data.frame(DOSY = c(0), event = c(0), day_away = c(0))

    for(i in as.list(dosy_dust_event)){
      print(i)
      local <- c(i-3,i-2,i-1,i,i+1,i+2,i+3)
      event <- paste("DE", i, sep = "")
      day_away <- c(-3,-2,-1,0,1,2,3)
    midframe <- data.frame(DOSY = local)%>%
      mutate(event = event,
             day_away = day_away)
    startframe <- rbind(startframe, midframe)
    }
    
    endframe <- startframe%>%
      filter(DOSY != 0)%>%
      filter(!duplicated(DOSY))
    end_vector <- endframe$DOSY
    
    filtered_dust <- visible_sasp%>%
      filter(SY == filter_sy)%>%
      filter(DOSY %in% end_vector)%>%
      merge(endframe, by ="DOSY")

return(filtered_dust)
}

sy_unique <- visible_sasp$SY%>%
  unique()
sy_unique <- sy_unique[sy_unique!="SY2005"]

filtered_dust_all <- map_dfr(sy_unique,pre_post_dust)

filtered_dust_graphing <- filtered_dust_all%>%
  mutate(seq = NA)
filtered_dust_graphing$seq <- with(filtered_dust_graphing, ave(SY, SY, FUN = seq_along))
filtered_dust_graphing <- filtered_dust_graphing%>%
  mutate(seq = as.numeric(as.character(seq)))%>%
  mutate(group = ifelse(event != lag(event), 1,0))

```


```{r}

ggplot(filtered_dust_graphing, aes(x=seq, group = event))+
  geom_col(aes(y=correct_m/4), fill = "steelblue2", width = 0.5)+
  geom_col(aes(y=dust_event), fill = "salmon3", width = 0.2)+
  geom_line(aes(y=alb_vis), color = "cyan4")+
  geom_point(aes(y=alb_vis), color = "cyan4", size = 0.5)+
  geom_line(aes(y=alb_filt), color = "plum4")+
  geom_point(aes(y=alb_filt), color = "plum4", size = 0.5)+
  facet_wrap(~SY, scales = "free_x")+
  theme_bw()+
  labs(x="", title = "SASP Albedo and Dust", subtitle = "Cyan = Visible Albedo, Plum = NIR & SWIR, Brown Lines = Dust Events" )+
  theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())+
  scale_y_continuous(name = "Albedo",
                     sec.axis = sec_axis(~.*4, name = "Depth (m)"))

ggplot(filtered_dust_graphing, aes(x=seq, group = event))+
  geom_col(aes(y=depth_diff), fill = "steelblue2", width = 0.5)+
  geom_col(aes(y=dust_event), fill = "salmon3", width = 0.2)+
  geom_line(aes(y=alb_vis), color = "cyan4")+
  geom_point(aes(y=alb_vis), color = "cyan4", size = 0.5)+
  geom_line(aes(y=alb_filt), color = "plum4")+
  geom_point(aes(y=alb_filt), color = "plum4", size = 0.5)+
  facet_wrap(~SY, scales = "free_x")+
  theme_bw()+
  labs(x="", title = "SASP Albedo and Dust", subtitle = "Cyan = Visible Albedo, Plum = NIR & SWIR, Brown Lines = Dust Events" )+
  theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())+
  scale_y_continuous(name = "Albedo",
                     sec.axis = sec_axis(~.*1, name = expression(Delta*"Depth (m)")))

```

### Zenith Exploration & Max Sunlight

```{r}
cos_zen <- read_csv(file = "data/cos_zenith_angle.csv", col_names=TRUE)%>%
  as.data.frame()

visible_sasp_zenith <- visible_sasp%>%
  merge(., cos_zen, by ="DOY")%>%
  mutate(zen_rad = acos(cos_zen),
         zen_deg = zen_rad*(180/pi))%>%
  distinct(.keep_all=T)%>%
  arrange(date, decreasing = FALSE)%>%
  mutate(max_hkin = cos_zen * 1367,
         max_hkabs_alb = max_hkin*(1-alb_final))

ggplot(visible_sasp_zenith, aes(x=Et, y=zen_deg))+
  geom_point(aes(color = DOY))+
  theme_minimal()+
  labs(x="Change in Time from Solar Noon",y= "Zenith Angle °")

```


```{r}
ggplot(visible_sasp_zenith, aes(x=DOSY))+
  geom_line(aes(y=max_hkin), size = 0.5)+
  geom_col(aes(y=correct_m*400), fill = "steelblue2", width = 0.75)+
  geom_col(aes(y=hk_absorbed), fill = "black")+
  scale_y_continuous(name = "Shortwave Radiation (W/m2)",
                     sec.axis = sec_axis(~./400, name = "Depth (m)"))+
  labs(title= "SASP Absorbed Shortwave vs Max Incoming Radiation from Zenith Angle")+
  facet_wrap(~SY, nrow=5)+
  theme_bw()

```

For this next graph I mulitpled the absorportion coefficent (1-albedo) by the max incoming solar radiation for the location (1367 w/m2 * zenith angle). There was no cloud cover calculation - but it turned out surprisingly close to to the real during snowpack

```{r}
ggplot(visible_sasp_zenith, aes(x=DOSY))+
  geom_col(aes(y=correct_m*400), fill = "steelblue2", width = 0.75)+
  geom_line(aes(y=max_hkabs_alb), size = 0.5, color = "cyan")+
  geom_col(aes(y=hk_absorbed), fill = "black")+
  scale_y_continuous(name = "Shortwave Radiation (W/m2)",
                     sec.axis = sec_axis(~./400, name = "Depth (m)"))+
  labs(title= "SASP Absorbed Shortwave vs Max Incoming Radiation from Zenith Angle")+
  facet_wrap(~SY, nrow=5)+
  theme_bw()

ggplot(visible_sasp_zenith %>% filter(correct_m >0), aes(x=DOSY))+
  geom_col(aes(y=correct_m*400), fill = "steelblue2", width = 0.75)+
  geom_line(aes(y=max_hkabs_alb), size = 0.5, color = "cyan")+
  geom_line(aes(y=hk_absorbed), size = 0.5, color = "black")+
  scale_y_continuous(name = "Abosrbed Shortwave Radiation (W/m2)",
                     sec.axis = sec_axis(~./400, name = "Depth (m)"))+
  labs(title= "SASP Absorbed Shortwave vs Max Incoming Radiation from Zenith Angle")+
  facet_wrap(~SY, nrow=5, scales = "free_x")+
  theme_bw()

ggplot(visible_sasp_zenith , aes(x=DOSY))+
  geom_line(aes(y=max_hkabs_alb), size = 0.5, color = "cyan")+
  geom_line(aes(y=hk_absorbed), size = 0.5, color = "black")+
  scale_y_continuous(name = "Abosrbed Shortwave Radiation (W/m2)")+
  labs(title= "SASP Absorbed Shortwave vs Max Incoming Radiation from Zenith Angle")+
  facet_wrap(~SY, nrow=5, scales = "free_x")+
  theme_bw()
```

### First 70 cm

```{r}
visible_sasp_early <- visible_sasp_zenith%>%
  filter(correct_m < 0.7)%>%
  filter(DOSY < 125)

ggplot(visible_sasp_early%>%filter(DOSY>25), aes(x=DOSY))+
  geom_line(aes(y=alb_final))+
  geom_col(aes(y=correct_m), fill = "steelblue2", width = 0.5)+
  facet_wrap(~SY, scales = "free_x")+
  scale_y_continuous(name = "Albedo",
                     sec.axis = sec_axis(~., name = "Depth (m)"), limits = c(0,1))+
  
  theme_bw()
```

### Last 70 cm

```{r}
visible_sasp_late <- visible_sasp_zenith%>%
  filter(correct_m < 0.9)%>%
  filter(DOSY > 150)%>%
  mutate(final_days = ifelse(lag(correct_m) >0, "keep", "delete"),
         final_days = ifelse(lag(final_days) == "keep", "keep", "delete"))%>%
  filter(final_days == "keep")%>%
  mutate(depth_diff_pos = ifelse(depth_diff >0, depth_diff, 0))

ggplot(visible_sasp_late, aes(x=DOSY))+
  geom_col(aes(y=correct_m/1), fill = "steelblue2", width = 0.5)+
  geom_line(aes(y=alb_final))+
  facet_wrap(~SY, scales = "free_x", nrow = 5)+
  scale_y_continuous(name = "Albedo",
                     sec.axis = sec_axis(~.*1, name = "Depth (m)"))+
  
  theme_bw()

```
Add on new depth via precip levels not depth?

```{r}
save(visible_sasp_zenith, file= "data/visible_sasp_zenith.Rdata")

```

#SBSP Intro
```{r}
load("data/sbsp.Rdata")
```

### SBSP Radiation
```{r}
skiles_rad_depth <- list.files('data/Skiles_SBSP_radiation', full.names = TRUE)

skiles_sbsp_readin <- function(file){
  data_names = str_sub(file, -8,-5)
  name = paste("WY", data_names, sep = "")
  df <- read.table(file, header  = F)%>%
    select(1:17)%>%
    rename("year" = 1, "month" = 2, "day" = 3, "hour" = 4, "doy" = 5,
          "hkin_unfilt" = 6, "hkout_unfilt" = 7, "hkabs_unfilt" = 8, "alb_unfilt" = 9,
          "hkin_filt" = 10, "hkout_filt" = 11, "hkabs_filt" = 12, "alb_filt" = 13,
          "hkin_shad" = 14, "hkout_shad" = 15, "hkabs_shad" = 16, "alb_shad" = 17)%>%
    mutate_if(is.character, as.numeric)%>%
    mutate(date = paste(month, day, year, sep = " "),
          date = mdy(date))%>%
    mutate(WY = name)%>%
    select(18:19, 4:17)%>%
    mutate_all(funs(replace(., .<0,NA)))
  
  return(df)
}

sbsp_05_14_skiles <- map_dfr(skiles_rad_depth, skiles_sbsp_readin)%>%
  mutate(hour0 = paste(hour, "00", sep=""),
         hour0 = ifelse(nchar(hour0) < 4, paste0("0", hour0), hour0))%>%
  mutate(datetime = paste(date, hour0, sep = " "),
         datetime = ymd_hm(datetime, tz = "MST"))

```


Quick Radiation Graphs
```{r}
sbsp_graph <- sbsp_05_14_skiles%>%
  filter(hour %in% c(8,9,10,11,12,13,14,15,16,17))

ggplot(sbsp_graph, aes(x=hour))+
  geom_point(aes(y=alb_unfilt))+
  facet_wrap(~WY, scales = "free_x")+
  theme_bw()

ggplot(sbsp_graph%>%filter(date == "2005-03-11"), aes(x=hour))+
  geom_line(aes(y=alb_unfilt))+
  geom_point(aes(y=alb_unfilt), shape =2)+
  ylim(c(0.6,1))+
  xlim(8,17)+
  theme_bw()

```


### SBSP Depth

```{r}
skiles_depth_sbsp <- list.files('data/Skiles_SBSP_depth', full.names = TRUE)

depth_reader_sbsp <- function(file){
  data_year = str_sub(file, -18, -15)
  name = paste("WY", data_year, sep = "")
  df <- read.table(file, header = F)%>%
    rename("year" =1, "month" = 2, "day" = 3, 
           "hour" = 4, "doy" = 5, "depth_m" =6)%>%
    mutate_if(is.character, as.numeric)%>%
    mutate(date = paste(month, day, year, sep = " "),
         date = mdy(date))%>%
    mutate(WY = name)%>%
    select(7,8,4,5,6)%>%
    mutate_all(funs(replace(., .<0,NA)))%>%
    mutate(depth_m = ifelse(depth_m > 9000, NA, depth_m))
         
   return(df)
}

sbsp_05_14_depth_skiles <- map_dfr(skiles_depth_sbsp, depth_reader_sbsp)%>%
   mutate(hour0 = paste(hour, "00", sep=""),
         hour0 = ifelse(nchar(hour0) < 4, paste0("0", hour0), hour0))%>%
  mutate(datetime = paste(date, hour0, sep = " "),
         datetime = ymd_hm(datetime, tz = "MST"))%>%
  select(7,5)
  

```

### SBSP Combined
```{r}

load(file = "data/SBSP.Rdata")

dust_df <- dust_06_14%>%
  select(1,3)%>%
  mutate(DE = ifelse(dust_event > 0,1,0),
         DE = ifelse(is.na(DE), 0, DE))
  
sbsp_og_depth <- sbsp %>%
  select(datetime, Sno_Height_M)%>%
  rename(depth_m_obs = 2)%>%
  mutate(depth_m_obs = ifelse(depth_m_obs<0,0,depth_m_obs),
         depth_m_obs = round(depth_m_obs, 2))

sbsp_obs_merge <- sbsp%>%
  select(1,6:8,10)%>%
  mutate(Tavg_C = (LoAir_Min_C+LoAir_Max_C)/2)%>%
  rename(RH = "Lo_RH", Uavg_MS = "LoWind_Uavg_MS")%>%
  select(1,4:6)

#radiation = 1:87624
#depth = 1:87648
#unique of radiation = 1:87624
#unique of depth = 1:87648
  
sep2011depth <- sbsp_05_14_depth_skiles %>%
  filter(datetime > "2013-09-01 00:00:00" & datetime <= "2013-10-01 00:00:00")%>%
  mutate(datetime = datetime - years(2))%>%
  rename(d2011 = 2)

```


```{r}

sbsp_combined <- merge(sbsp_05_14_depth_skiles, sbsp_05_14_skiles,
                       by ="datetime", all = T)%>%
  filter(datetime >	"2005-01-21 11:00:00")%>%
  rename(depth_m_skiles = "depth_m")%>%
  merge(., sbsp_og_depth, by = "datetime")%>%
  mutate(depth_diff = depth_m_obs - depth_m_skiles)%>%
  select(1,2,20,21,3:18)%>%
  mutate(depth_m = ifelse(depth_diff >-0.25, depth_m_skiles, depth_m_obs),
         depth_m = ifelse(WY == "WY2005", depth_m_obs, depth_m),
         depth_m = ifelse(year(date) == 2013 & month(date) == 09, 
                          depth_m_obs, depth_m))%>%
  merge(., sep2011depth, by = "datetime", all =T)%>%
  mutate(depth_m = ifelse(year(date) == 2011 & month(date) == 09, d2011, depth_m),
         depth_m = ifelse(year(date) == 2012 & month(date) == 09, depth_m_obs, depth_m))%>%
  select(1:21)%>%
  filter(!is.na(WY))%>%
  mutate(SY = ifelse(date >= "2004-09-01" & date < "2005-09-01", "SY2005",
              ifelse(date >= "2005-09-01" & date < "2006-09-01", "SY2006",
              ifelse(date >= "2006-09-01" & date < "2007-09-01", "SY2007",
              ifelse(date >= "2007-09-01" & date < "2008-09-01", "SY2008",
              ifelse(date >= "2008-09-01" & date < "2009-09-01", "SY2009",
              ifelse(date >= "2009-09-01" & date < "2010-09-01", "SY2010",
              ifelse(date >= "2010-09-01" & date < "2011-09-01", "SY2011",
              ifelse(date >= "2011-09-01" & date < "2012-09-01", "SY2012",
              ifelse(date >= "2012-09-01" & date < "2013-09-01", "SY2013",
              ifelse(date >= "2013-09-01" & date < "2014-09-01", "SY2014",NA)))))))))))%>%
  mutate(DOSY = 1)%>%
  mutate(DOSY = ifelse(doy > 243, doy-243, doy+122),
         DOSY = ifelse(SY == "SY2009" | SY == "SY2013",
                       ifelse(doy > 244, doy-244, doy+122), DOSY),
         DOSY = ifelse(date == "2012-08-31" | date == "2008-08-31", 366, DOSY))%>%
  select(1,5,8,7,6,22,23,9:16,21)%>%
  rename(DOY = "doy")%>%
  merge(., dust_df, by ="date", all=T)%>%
  merge(., sbsp_obs_merge, by = "datetime", all = T)%>%
  filter(!is.na(SY))

ggplot(sbsp_combined%>%filter(hour==12), aes(x=datetime, y=depth_m))+
  geom_point()+
  facet_wrap(~SY, scales = "free")+
  theme_bw()

save(sbsp_combined, file = "data/SBSP_combined.Rdata")
  
```

2013 Depth at both sites
```{r}

depth_2013 <- sbsp_combined%>%
  filter(datetime > "2013-09-01 00:00:00" & datetime <= "2013-10-01 00:00:00")%>%
  select(datetime, depth_m)%>%
  rename(sbsp_depth = 2)

```


### SASP Copy
```{r}
load(file = "data/SASP.Rdata")
load(file = "data/sasp_05_14_skiles.Rdata")
load(file = "data/sasp_05_14_depth_skiles.Rdata")

sasp_skiles_rad <- sasp_05_14_skiles%>%
  mutate(hour0 = paste(hour, "00", sep=""),
         hour0 = ifelse(nchar(hour0) < 4, paste0("0", hour0), hour0))%>%
  mutate(datetime = paste(date, hour0, sep = " "),
         datetime = ymd_hm(datetime, tz = "MST"))

sasp_skiles_dep <- sasp_05_14_depth_skiles %>%
  mutate(hour0 = paste(hour, "00", sep=""),
         hour0 = ifelse(nchar(hour0) < 4, paste0("0", hour0), hour0))%>%
  mutate(datetime = paste(date, hour0, sep = " "),
         datetime = ymd_hm(datetime, tz = "MST"))%>%
  select(7,5)

```

```{r}
test <- sasp_skiles_dep%>%
  rename(sasp_dep_m =2)%>%
  merge(., sbsp_05_14_depth_skiles, by ="datetime", all=T)%>%
  rename(sbsp_dep_m = 3)%>%
  filter(!is.na(datetime))

ggplot(test%>%filter(month(datetime) == 09 & hour(datetime) == 12), aes(x=datetime))+
  geom_line(aes(y=sasp_dep_m), color = "black")+
  geom_line(aes(y=sbsp_dep_m), color = "lightgray")+
  facet_wrap(~year(datetime), scales = "free")+
  theme_bw()

ggplot(sasp_skiles_dep%>%filter(month(datetime) == 09 & hour(datetime) == 12), aes(x=datetime))+
  geom_line(aes(y=depth_m), color = "black")+
  facet_wrap(~year(datetime), scales = "free")+
  theme_bw()

```



```{r}

sasp_og_depth <- sasp %>%
  select(datetime, Sno_Height_M)%>%
  rename(depth_m_obs = 2)%>%
  mutate(depth_m_obs = round(depth_m_obs, 2))%>%
  merge(., depth_2013, all= T, by ="datetime")%>%
  mutate(depth_m_obs = ifelse(year(datetime) ==2013 & month(datetime) == 09,
                              sbsp_depth, depth_m_obs))%>%
  select(1,2)


sasp_obs_merge <- sasp%>%
  select(1,6:8,9)%>%
  mutate(Tavg_C = (LoAir_Min_C+LoAir_Max_C)/2)%>%
  rename(RH = "Lo_RH", Uavg_MS = "UpWind_Uavg_MS")%>%
  select(1,4:6)
  
sasp_combined <- merge(sasp_skiles_rad, sasp_skiles_dep,
                       by ="datetime", all = T)%>%
  filter(datetime >	"2005-01-21 11:00:00")%>%
  rename(depth_m_skiles = "depth_m")%>%
  merge(., sasp_og_depth, by = "datetime")%>%
  mutate(depth_diff = depth_m_obs - depth_m_skiles)%>%
  select(1,2,19,20,3:17,21)%>%
  mutate(depth_m = ifelse(depth_diff >-0.25, depth_m_skiles, depth_m_obs),
         depth_m = ifelse(WY == "WY2005", depth_m_obs, depth_m))%>%
  merge(., sep2011depth, by = "datetime", all =T)%>%
  mutate(depth_m = ifelse(year(date) == 2011 & month(date) == 09, d2011, depth_m),
         depth_m = ifelse(year(date) == 2012 & month(date) == 09, depth_m_obs, depth_m),
         depth_m = ifelse(year(date) == 2013 & month(date) == 09, depth_m_obs, depth_m))%>%
  select(1:21)%>%
  filter(!is.na(WY))%>%
  mutate(SY = ifelse(date >= "2004-09-01" & date < "2005-09-01", "SY2005",
              ifelse(date >= "2005-09-01" & date < "2006-09-01", "SY2006",
              ifelse(date >= "2006-09-01" & date < "2007-09-01", "SY2007",
              ifelse(date >= "2007-09-01" & date < "2008-09-01", "SY2008",
              ifelse(date >= "2008-09-01" & date < "2009-09-01", "SY2009",
              ifelse(date >= "2009-09-01" & date < "2010-09-01", "SY2010",
              ifelse(date >= "2010-09-01" & date < "2011-09-01", "SY2011",
              ifelse(date >= "2011-09-01" & date < "2012-09-01", "SY2012",                               ifelse(date >= "2012-09-01" & date < "2013-09-01", "SY2013",
              ifelse(date >= "2013-09-01" & date < "2014-09-01", "SY2014",NA)))))))))))%>%
  mutate(DOSY = 1)%>%
  mutate(DOSY = ifelse(doy > 243, doy-243, doy+122),
         DOSY = ifelse(SY == "SY2009" | SY == "SY2013",
                       ifelse(doy > 244, doy-244, doy+122), DOSY),
         DOSY = ifelse(date == "2012-08-31" | date == "2008-08-31", 366, DOSY))%>%
  select(2,1,7,6,5,22,23,8:15,21)%>%
  rename(DOY = "doy")%>%
  merge(., dust_df, by ="date", all=T)%>%
  merge(., sasp_obs_merge, by = "datetime", all = T)%>%
  filter(!is.na(SY))

ggplot(sasp_combined, aes(x=datetime, y=depth_m))+
  geom_point()+
  facet_wrap(~SY, scales = "free")+
  theme_bw()

save(sasp_combined, file = "data/SASP_combined.Rdata")
  

```


