---
title: "FreshSnowStats"
author: "Danielle Reimanis"
date: "5/18/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(tidyverse)
library(tidyr)
library(lubridate)
library(ggthemes)
library(ggpubr)
library(ggplot2)
library(stringr)
library(purrr)
library(xts)
library(dygraphs)
library(hms)
library(RNRCS)
library(hydroGOF)
library(wesanderson)

setwd("~/Desktop/Albedo Analysis/albedo-research")

```


```{r}

load(file = "data/sasp_sbsp_long.Rdata")
load(file = "data/sasp.Rdata")
load(file = "data/sbsp.Rdata")

```

### Dust Read-In (again)
```{r}
dust_files <- list.files('data/Dust_Events', full.names = TRUE)

dust_read_in <- function(file){
  data_names = str_sub(file, -8,-5)
  name = paste("WY", data_names, sep = "")
 df <- read_delim(file = file, delim = " ", col_names=TRUE)%>%
  mutate(date = mdy(date))%>%
  mutate_if(is.character, as.numeric)%>%
  mutate(WY = name)%>%
  rename("date" =1, "doy"=2,"dust_event"=3)
return(df)
}

dust_06_14 <- map_dfr(dust_files, dust_read_in)%>%
  select(1,3)%>%
  mutate(dust_event = ifelse(is.na(dust_event), 0, dust_event))
```


### Dust Setup
```{r}
sasp_sbsp_long_2 <- sasp_sbsp_long%>%
  select(1:16,19:26)%>%
  merge(., dust_06_14, by ="date", all = T)%>%
  filter(!is.na(date) & !is.na(dust_event))%>%
  filter(!SY == "SY2005")

# dust_loop_sasp <- sasp_sbsp_long_2%>%
#   filter(site == "SASP")%>%
#   filter(SY == "SY2008")
# sd2 <- dust_loop_sasp$dust_event
# sd3 <- rep(0, nrow(dust_loop_sasp))
# for(i in 2:nrow(dust_loop_sasp)){
#   if(sd2[i] > sd2[i-1]){
#       sd3[i] = sd3[i-1]+1} else{
#       sd3[i] = sd3[i-1]}
# }
# final_dust <- dust_loop_sasp%>%
#   mutate(newdust = sd3)

dust_cumulative_sasp <- function(SY2){
  dust_loop_sasp <- sasp_sbsp_long_2%>%
    filter(site == "SASP")%>%
    filter(SY == SY2)
  sd2 <- dust_loop_sasp$dust_event
  sd3 <- rep(0, nrow(dust_loop_sasp))
  for(i in 2:nrow(dust_loop_sasp)){
    if(sd2[i] > sd2[i-1]){
      sd3[i] = sd3[i-1]+1} else{
      sd3[i] = sd3[i-1]}
    }
  final_dust <- dust_loop_sasp%>%
      mutate(newdust = sd3)
  
  return(final_dust)
}

SY <- unique(sasp_sbsp_long_2$SY)
sasp_dust <- map_dfr(SY, dust_cumulative_sasp)



dust_cumulative_sbsp <- function(SY2){
  dust_loop_sbsp <- sasp_sbsp_long_2%>%
    filter(site == "SBSP")%>%
    filter(SY == SY2)
  sd2 <- dust_loop_sbsp$dust_event
  sd3 <- rep(0, nrow(dust_loop_sbsp))
  for(i in 2:nrow(dust_loop_sbsp)){
    if(sd2[i] > sd2[i-1]){
      sd3[i] = sd3[i-1]+1} else{
      sd3[i] = sd3[i-1]}
    }
  final_dust <- dust_loop_sbsp%>%
      mutate(newdust = sd3)
  
  return(final_dust)
}

SY <- unique(sasp_sbsp_long_2$SY)
sbsp_dust <- map_dfr(SY, dust_cumulative_sbsp)

saspdust <- sasp_dust%>%
  select(datetime, site, newdust)
sbspdust <- sbsp_dust%>%
  select(datetime, site, newdust)
dustfinal <- rbind(saspdust, sbspdust)

new_df <- sasp_sbsp_long%>%
  select(-DE, -dust_event)%>%
  merge(., dustfinal, by = c("datetime", "site"), all = T)%>%
  mutate(newdust = ifelse(is.na(newdust), 0, newdust))
  #filter(!SY == "SY2005")

hist(new_df$alb_unfilt, breaks = 100)
hist(sasp_sbsp_long_2$alb_unfilt, breaks = 100)
hist(sasp_sbsp_long$alb_unfilt, breaks = 100)
hist(stats_setup$alb_unfilt, breaks = 100)

names(new_df)

avg_dust <- new_df%>%
  filter(!SY == "SY2005")%>%
  filter(!is.na(depth_m))%>%
  group_by(SY)%>%
  summarise(max = max(depth_m))%>%
  ungroup()%>%
  summarise(mean = mean(max))

```

### LM by Wavelength (all)

```{r}
lm_all <- new_df%>%
  filter(!is.na(alb_unfilt) & alb_unfilt < 0.98 & alb_unfilt > 0.16)%>%
  filter(!is.na(alb_filt) & alb_filt < 0.98 & alb_filt > 0)%>%
  filter(!is.na(alb_vis) & alb_vis < 1 & alb_vis > 0)%>%
  filter(SY %in%  c("SY2005","SY2006", "SY2007", "SY2008", "SY2009", "SY2010", "SY2011"))%>%
 lm(data = ., alb_unfilt ~ alb_vis + alb_filt)

summary(lm_all)
confint(lm_all)

all_combined <- new_df%>%
  filter(!is.na(alb_unfilt) & alb_unfilt < 0.98 & alb_unfilt > 0.16)%>%
  filter(!is.na(alb_filt) & alb_filt < 0.98 & alb_filt > 0)%>%
  filter(!is.na(alb_vis) & alb_vis < 1 & alb_vis > 0)%>%
  mutate(mod_alb = coef(lm_all)[1] + coef(lm_all)[2]*alb_vis + coef(lm_all)[3]*alb_filt)%>%
  mutate(model_bin = ifelse(datetime < "2011-09-01 11:00:00", "Calibration", "Evaluation"))
  #filter(model_bin == "Evaluation")

cor(all_combined$alb_unfilt, all_combined$mod_alb, method = "pearson")^2
NSE(all_combined$alb_unfilt, all_combined$mod_alb)


ggplot(all_combined %>%filter(mod_alb < 2), aes(x=alb_unfilt, y=mod_alb))+
  geom_point()+
  geom_abline()+
  xlim(c(0, 1))+
  ylim(c(0, max(all_combined$mod_alb)))+
  theme_bw()+
  #scale_color_gradient(low = "gray20", high = "cyan3")+
  labs(x="Observed α", y="Modeled α", color = "Observed Vis α")+
   theme(text = element_text(size = 17.5, family = "Times New Roman"), legend.position = c(0.86,0.15))+
  facet_wrap(~model_bin)

cor(all_combined$alb_unfilt, all_combined$mod_alb, method = "pearson")^2
NSE(all_combined$alb_unfilt, all_combined$mod_alb)

```

#### LM by Outgoing & Incoming
```{r}

ratios <- new_df%>%
  filter(!is.na(alb_unfilt), alb_unfilt < 0.98)%>%
  filter(!is.na(alb_filt), alb_filt < 1)%>%
  filter(alb_vis < 1 & alb_vis > 0)%>%
  filter(hour %in% c(10,11,12,13,14))%>%
  mutate(outvis = hkout_vis/hkout_unfilt,
         outfilt = hkout_filt/hkout_unfilt,
         invis = hkin_vis/hkin_unfilt,
         infilt = hkin_filt/hkin_unfilt)

ggplot(ratios%>%filter(!SY == "SY2005", site == "SBSP"), aes(x=DOSY))+
  geom_point(aes(y=outvis), shape = 6, color = "yellow3")+
  geom_point(aes(y=outfilt), shape = 6, color = "red4")+
  facet_wrap(~SY)+
  labs(y="Outgoing Radiation %")+
  theme_bw()

ggplot(ratios%>%filter(!SY == "SY2005", site == "SBSP"), aes(x=DOSY))+
  geom_point(aes(y=invis), shape = 2, color = "yellow3")+
  geom_point(aes(y=infilt), shape = 2, color = "red4")+
  facet_wrap(~SY)+
  labs(y="Incoming Radiation %")+
  theme_bw()

```


### Stats Setup
```{r}

ggplot(stats_setup, aes(x=DOSY, y=alb_unfilt))+
  geom_point()+
  facet_wrap(~SY, scales= "free_x")

filter_setup <- new_df%>%
  filter(!SY == "SY2005")%>%
  filter(!is.na(alb_unfilt) & alb_unfilt < 0.98 & alb_unfilt > 0.15)%>%
  arrange(site,datetime)%>%
  group_by(site)%>%
  mutate(depth_diff = depth_m - lag(depth_m),
         depth_diff = ifelse(is.na(depth_diff), 0 , depth_diff),
         alb_diff = alb_unfilt - lag(alb_unfilt), 
         alb_diff = ifelse(is.na(alb_diff), 0, alb_diff),
         alb_tminus1 = alb_unfilt - alb_diff,
         temp_tminus1 = lag(Tavg_C),
         temp_tminus1 = ifelse(is.na(temp_tminus1), 0, temp_tminus1),
         vis_tminus1 = lag(alb_vis),
         vis_tminus1 = ifelse(is.na(vis_tminus1),0,vis_tminus1),
         filt_tminus1 = lag(alb_filt),
         filt_tminus1 = ifelse(is.na(filt_tminus1), 0, filt_tminus1))%>%
  ungroup()
  
stats_setup <- filter_setup%>%
  filter(hour %in% c(10,11,12,13,14))%>%
  mutate(depth_diff = as.numeric(depth_diff),
         depth_diff = round(depth_diff, digits =2))%>%
  filter(depth_diff > -0.2 & depth_diff < 0.3)%>%
  filter(alb_diff > 0.01)%>%
  filter(depth_diff > 0)%>%
  mutate(esat = 6.112*exp((22.46*Tavg_C)/(272.62 + Tavg_C)),
         ea = (RH/100) * esat,
         dewpointT = (log(ea) - 1.810)/(0.0653 - 0.00421*log(ea)))


ggplot(stats_setup, aes(x=temp_tminus1, y = alb_unfilt))+
  geom_point()
ggplot(stats_setup, aes(x=Tavg_C, y = dewpointT))+
  geom_point()+
  geom_abline()
ggplot(stats_setup, aes(x=Tavg_C, y = alb_tminus1))+
  geom_point()
ggplot(stats_setup, aes(x = dewpointT, y= alb_tminus1))+
  geom_point()
ggplot(stats_setup, aes(x = Uavg_MS, y= alb_tminus1))+
  geom_point()


stats <- stats_setup%>%
  filter(Tavg_C > 0)

```


### Working Stats
```{r}
mltivar_setup <- stats_setup%>%
  filter(SY %in% c("SY2006", "SY2007", "SY2008", "SY2009", "SY2010", "SY2011"))

str(mltivar_setup)
names(mltivar_setup)

multivar <- lm(alb_unfilt ~ temp_tminus1 + log(depth_m) + depth_diff + Uavg_MS, data = mltivar_setup)
summary(multivar)
head(fitted(multivar))
vcov(multivar)

multivar2 <- lm(alb_unfilt ~ alb_tminus1 + temp_tminus1 + log(depth_m) + depth_diff, data = mltivar_setup)

summary(multivar2)
cor(mltivar_setup$alb_tminus1, mltivar_setup$temp_tminus1, method = "kendall")
head(fitted(multivar2))
vcov(multivar2)

multivar3 <- lm(alb_unfilt ~ log(depth_m) + depth_diff + Tavg_C + alb_diff, data = mltivar_setup)
summary(multivar3)

```

### Plot Stats
```{r}
mltivar_mod <- stats_setup%>%
  mutate(model = coef(multivar)[1] + coef(multivar)[2]*temp_tminus1 + coef(multivar)[3]*log(depth_m) + 
           coef(multivar)[4]*depth_diff + coef(multivar)[5]*Uavg_MS)%>%
  mutate(model2 = coef(multivar2)[1] + coef(multivar2)[2]*alb_tminus1 + coef(multivar2)[3]*temp_tminus1 + 
           coef(multivar2)[4]*log(depth_m)+coef(multivar2)[5]*depth_diff)%>%
  mutate(model3 = coef(multivar3)[1] + coef(multivar3)[2]*log(depth_m) + coef(multivar3)[3]*depth_diff + coef(multivar3)[4]*Tavg_C + coef(multivar3)[5]*alb_diff)%>%
  mutate(model_bin = ifelse(datetime < "2011-09-01 11:00:00", "Included", "Not Included"))%>%
  filter(!is.na(model))

ggplot(mltivar_mod, aes(x=alb_unfilt, y=model))+
  geom_point(aes(color = newdust))+
  ylim(c(0,max(mltivar_mod$model)))+
  geom_abline()+
  xlim(c(0,1))+
  theme_bw()+
  labs(x="Observed", y="Modeled")+
  facet_wrap(~model_bin)

ggplot(mltivar_mod%>%filter(alb_vis < 1), aes(x=alb_unfilt, y=model3))+
  geom_point(aes(color = newdust))+
  ylim(c(0,max(mltivar_mod$model3)))+
  geom_abline()+
  xlim(c(0,1))+
  theme_bw()+
  labs(x="Observed", y="Modeled with Albedo Difference")+
  facet_wrap(~model_bin)

ggplot(mltivar_mod, aes(x=alb_unfilt, y=model2))+
  geom_point(aes(color = newdust))+
  ylim(c(0,max(mltivar_mod$model2)))+
  geom_abline()+
  xlim(c(0,1))+
  theme_bw()+
  labs(x="Observed", y="Modeled with Albedo (t-1)")+
  facet_wrap(~model_bin)


cor(mltivar_mod$alb_unfilt, mltivar_mod$model, method = "pearson")^2
NSE(mltivar_mod$alb_unfilt, mltivar_mod$model)

cor(mltivar_mod$alb_unfilt, mltivar_mod$model2, method = "pearson")^2
NSE(mltivar_mod$alb_unfilt, mltivar_mod$model2)

cor(mltivar_mod$alb_unfilt, mltivar_mod$model3, method = "pearson")^2
NSE(mltivar_mod$alb_unfilt, mltivar_mod$model3)

```

### Splitting Albedos

```{r}
ggplot(stats_setup%>%filter(alb_vis < 1), aes(x=alb_unfilt))+
  geom_point(aes(y=alb_vis), color = "magenta")+
  geom_point(aes(y=alb_filt))+
  ylim(c(0,1))+
  xlim(c(0,1))+
  theme_bw()

str(mltivar_setup)

lm_alb <- mltivar_setup%>%
  filter(alb_vis < 1)%>%
  lm(data = ., alb_unfilt ~ alb_filt + alb_vis)
summary(lm_alb)
confint(lm_alb)

spectrumalb <- stats_setup%>%
  filter(alb_vis < 1)%>%
  mutate(model_alb = coef(lm_alb)[1] + coef(lm_alb)[2]*alb_filt + coef(lm_alb)[3]*alb_vis)%>%
  mutate(model_bin = ifelse(datetime < "2011-09-01 11:00:00", "Calibration", "Evaluation"))
#%>%filter(model_bin == "Evaluation")


cor(spectrumalb$alb_unfilt, spectrumalb$model_alb, method = "pearson")^2
NSE(spectrumalb$alb_unfilt, spectrumalb$model_alb)

ggplot(spectrumalb, aes(x=alb_unfilt, y=model_alb))+
  geom_point()+
  geom_abline()+
  facet_wrap(~model_bin)+
  theme_bw()+
  labs(x="Observed Albedo", y="Modeled Albedo", color = "#Dust Events")+
   theme(text = element_text(size = 17.5, family = "Times New Roman"), legend.position = c(0.85,0.2))+
  ylim(c(0,1))+
  xlim(c(0,1))
```


```{r}
names(spectrumalb)
names(all_combined)
summary(lm_alb)
confint(lm_alb)
summary(lm_all)
confint(lm_all)

all <- all_combined%>%
  select(datetime, site,alb_unfilt, mod_alb, alb_filt, alb_vis)%>%
  rename(all = mod_alb)%>%
  mutate(fresh = coef(lm_alb)[1] + coef(lm_alb)[2]*alb_filt + coef(lm_alb)[3]*alb_vis)

cor(all$all, all$alb_unfilt, method = "pearson")^2
NSE(all$alb_unfilt, all$fresh)

a <- all_combined%>%
  dplyr::select(alb_unfilt, mod_alb, model_bin)%>%
  mutate(Model = "All-Values")%>%
  rename("Albedo" = mod_alb)

b <- spectrumalb%>%
  dplyr::select(alb_unfilt, model_alb, model_bin)%>%
  mutate(Model = "Fresh-Snow")%>%
  rename("Albedo" = model_alb)

c <- all_combined%>%
  dplyr::select(alb_unfilt, alb_vis, alb_filt)%>%
  mutate(fresh = 
           coef(lm_alb)[1] + 
           coef(lm_alb)[2]*alb_filt + 
           coef(lm_alb)[3]*alb_vis)%>%
  dplyr::select(alb_unfilt, fresh)%>%
  mutate(model_bin = "Evaluation")%>%
  mutate(Model = "Fresh-All")%>%
  rename("Albedo" = fresh)

cor(c$Albedo, c$alb_unfilt, method = "pearson")^2
NSE(c$alb_unfilt, c$Albedo)

all_long <- rbind(a,b,c)

ggplot(all_long, aes(x=alb_unfilt, y=Albedo))+
  geom_point(alpha = 0.5, color = "blue4")+
  geom_abline(linetype = "dashed", color = "snow1")+
  facet_grid(model_bin~Model)+
  theme_bw()+
  labs(x="Observed α", y = "Modeled α")+
  theme(text = element_text(size = 17.5, family = "Times New Roman"))




```

### PLOT Vis vs NIR/SWIR
```{r}
# ggplot(stats_setup%>%filter(!SY == "SY2005" & hour %in% c(11,12,13) & alb_vis < 1), aes(x=temp_tminus1))+
#   geom_point(aes(y=alb_unfilt, shape = site), color = "gray30")+
#   geom_point(aes(y=alb_filt, shape = site), color = "red4")+
#   geom_point(aes(y=alb_vis, shape = site), color = "cyan")+
#   theme_bw()+
#   facet_wrap(~newdust)+
#   ylim(c(0,1))

# names(stats_setup)
improved_vis <- stats_setup%>%
  filter(alb_vis < 1)%>%
  select(1,2,4,6,7,11,15,16,20,24,26,27,30)%>%
  gather(., key = "Wavelength", value = "Albedo",
         -datetime, -alb_unfilt, -date, -hour, -SY, -DOSY, -depth_m, -newdust, -site, -depth_diff, -temp_tminus1)

ggplot(improved_vis, aes(x=temp_tminus1))+
  geom_point(aes(y=Albedo, color = newdust))+
  facet_wrap(~Wavelength)

```

### Variable LM

#### VIS LM
```{r}

vis <- stats_setup%>%
  filter(alb_vis < 1 & alb_vis >0)%>%
  select(date, datetime, hour, SY, DOSY, hkin_vis, hkout_vis, alb_vis, newdust, depth_diff, depth_m, temp_tminus1, Tavg_C, Uavg_MS, site, RH, vis_tminus1, ea, esat, dewpointT)

# ggplot(stats_setup, aes(x=depth_m))+
#   geom_point(aes(y=alb_vis), color = "magenta")+
#   geom_point(aes(y=alb_unfilt), color = "black")

vis_lm <- vis%>%
  filter(SY %in% c("SY2006", "SY2007", "SY2008", "SY2009", "SY2010", "SY2011"))%>%
  #filter(temp_tminus1 > -3)%>%
  lm(data = ., alb_vis ~  depth_diff + log(depth_m) + Uavg_MS + RH + temp_tminus1 + newdust + vis_tminus1)
summary(vis_lm)
confint(vis_lm)

cov(vis$temp_tminus1, vis$vis_tminus1)

vis_model <- vis%>%
  mutate(vis_mod = coef(vis_lm)[1]+coef(vis_lm)[2]*depth_diff+coef(vis_lm)[3]*log(depth_m) + coef(vis_lm)[4]*Uavg_MS + coef(vis_lm)[5]*RH + coef(vis_lm)[6]*temp_tminus1 + coef(vis_lm)[7]*newdust + coef(vis_lm)[8]*vis_tminus1)

cor(vis_model$alb_vis, vis_model$vis_mod, method = "pearson")^2
NSE(vis_model$alb_vis, vis_model$vis_mod)

ggplot(vis_model, aes(x=alb_vis, y=vis_mod))+
  geom_point(aes(color = newdust))+
  ylim(c(0,max(vis_model$vis_mod)))+
  xlim(c(0,1))+
  theme_bw()+
  geom_abline()+
  scale_color_gradient(low = "snow3", high = "red4")+
  labs(x="Observed Visible α", y="Modeled Visible α", color = "#Dust Events")+
   theme(text = element_text(size = 17.5, family = "Times New Roman"), legend.position = c(0.85,0.2))


```

#### NIR/SWIR LM
```{r}
nir_swir <- stats_setup%>%
  filter(!is.na(filt_tminus1))%>%
  select(date, datetime, hour, SY, DOSY, hkin_filt, hkout_filt, alb_filt, newdust, depth_diff, depth_m, temp_tminus1, Tavg_C, Uavg_MS, site, RH, filt_tminus1, ea, esat, dewpointT)%>%
  filter(!is.na(alb_filt))

# ggplot(stats_setup, aes(x=temp_tminus1))+
#   geom_point(aes(y=alb_filt), color = "red4")+
#   geom_point(aes(y=alb_unfilt), color = "black")

filt_lm <- nir_swir%>%
  filter(SY %in% c("SY2005", "SY2006", "SY2007", "SY2008", "SY2009", "SY2010", "SY2011"))%>%
  #filter(temp_tminus1 > -3)%>%
  lm(data = ., alb_filt ~  depth_diff + depth_m + Uavg_MS + RH + temp_tminus1 + filt_tminus1)
summary(filt_lm)
confint(filt_lm)

#alb_filt ~  depth_diff + log(depth_m) + Uavg_MS + RH + temp_tminus1 + newdust + filt_tminus1)

filt_model <- nir_swir%>%
  mutate(filt_mod = coef(filt_lm)[1]+coef(filt_lm)[2]*depth_diff+coef(filt_lm)[3]*depth_m + coef(filt_lm)[4]*Uavg_MS + coef(filt_lm)[5]*RH + coef(filt_lm)[6]*temp_tminus1 + coef(filt_lm)[7]*filt_tminus1)

cor(filt_model$alb_filt, filt_model$filt_mod, method = "pearson")^2
NSE(filt_model$alb_filt, filt_model$filt_mod)

ggplot(filt_model, aes(x=alb_filt, y=filt_mod))+
  geom_point(aes(color = newdust))+
  ylim(c(0,max(filt_model$filt_mod)))+
  xlim(c(0,1))+
  theme_bw()+
  geom_abline()+
  scale_color_gradient(low = "snow3", high = "red4")+
  labs(x="Observed NIR/SWIR α", y="Modeled NIR/SWIR α", color = "#Dust Events")+
   theme(text = element_text(size = 17.5, family = "Times New Roman"), legend.position = c(0.85,0.2))


```

#### Combined LM
```{r}
vis2 <- vis_model%>%
  select(datetime, vis_mod)
filt2 <- filt_model%>%
  select(datetime, filt_mod)
unfilt2 <- stats_setup%>%
  select(datetime, alb_unfilt, newdust)

combined <- unfilt2%>%
  merge(., vis2, by = "datetime")%>%
  merge(., filt2, by = "datetime")%>%
  mutate(model_unfilt = coef(lm_alb)[1] + coef(lm_alb)[2]*filt_mod + coef(lm_alb)[3]*vis_mod)

cor(combined$alb_unfilt, combined$model_unfilt, method = "pearson")^2
NSE(combined$alb_unfilt, combined$model_unfilt)

ggplot(combined, aes(x=alb_unfilt, y=model_unfilt))+
  geom_point(aes(color = newdust))+
  geom_abline()+
  xlim(c(0,1))+
  ylim(c(0,1))+
  theme_bw()+
  scale_color_gradient(low = "snow3", high = "red4")+
  labs(x="Observed α", y="Modeled α", color = "#Dust Events")+
   theme(text = element_text(size = 17.5, family = "Times New Roman"), legend.position = c(0.85,0.2))

 

```

### Simplified LM
#### VIS LM

```{r}
vis_simp  <- stats_setup%>%
  filter(alb_vis < 1 & vis_tminus1 > 0)%>%
  #filter(depth_diff > 0.01)
  #filter(alb_tminus1 > 0.3)%>%
  select(date, datetime, hour, SY, DOSY, hkin_vis, hkout_vis, alb_vis, newdust, depth_diff, depth_m, temp_tminus1, Tavg_C, Uavg_MS, site, RH, vis_tminus1, ea, esat, dewpointT, alb_tminus1)

vis_lm_simp <- vis_simp%>%
  filter(SY %in% c("SY2005", "SY2006", "SY2007", "SY2008", "SY2009", "SY2010", "SY2011"))%>%
  lm(data = ., alb_vis ~  depth_diff + log(depth_m) + alb_tminus1 +Tavg_C +newdust)
summary(vis_lm_simp)
confint(vis_lm_simp)

vis_model_simp <- vis_simp%>%
  mutate(vis_mod = coef(vis_lm_simp)[1]+coef(vis_lm_simp)[2]*depth_diff+coef(vis_lm_simp)[3]*log(depth_m) + coef(vis_lm_simp)[4]*alb_tminus1 + coef(vis_lm_simp)[5]*Tavg_C + coef(vis_lm_simp)[6]*newdust)%>%
  mutate(model_bin = ifelse(datetime < "2011-09-01 11:00:00", "Included", "Not Included"))

cor(vis_model_simp$alb_vis, vis_model_simp$vis_mod, method = "pearson")^2
NSE(vis_model_simp$alb_vis, vis_model_simp$vis_mod)

ggplot(vis_model_simp, aes(x=alb_vis, y=vis_mod))+
  geom_point(aes(color = newdust))+
  ylim(c(0,max(vis_model$vis_mod)))+
  xlim(c(0,1))+
  theme_bw()+
  geom_abline()+
  scale_color_gradient(low = "snow3", high = "red4")+
  labs(x="Observed Visible α", y="Modeled Visible α", color = "#Dust Events")+
   theme(text = element_text(size = 17.5, family = "Times New Roman"),legend.position = c(0.85,0.2))+
  facet_wrap(~model_bin)

```



#### NIR/SWIR LM

```{r}
filt_simp <- stats_setup%>%
  filter(alb_filt < 1 & !is.na(alb_filt))%>%
  #filter(depth_diff>0.01)
  #filter(alb_tminus1 > 0.3)%>%
  select(date, datetime, hour, SY, DOSY, hkin_filt, hkout_filt, alb_filt, newdust, depth_diff, depth_m, temp_tminus1, Tavg_C, Uavg_MS, site, RH, filt_tminus1, ea, esat, dewpointT, alb_tminus1)

filt_lm_simp <- filt_simp%>%
  filter(SY %in% c("SY2005", "SY2006", "SY2007", "SY2008", "SY2009", "SY2010", "SY2011"))%>%
  lm(data = ., alb_filt ~  depth_diff + alb_tminus1 +Tavg_C +log(depth_m))
summary(filt_lm_simp)
confint(filt_lm_simp)

filt_model_simp <- filt_simp%>%
  mutate(filt_mod = coef(filt_lm_simp)[1]+coef(filt_lm_simp)[2]*depth_diff + coef(filt_lm_simp)[3]*alb_tminus1 + coef(filt_lm_simp)[4]*Tavg_C + coef(filt_lm_simp)[5]*log(depth_m))%>%
  mutate(model_bin = ifelse(datetime < "2011-09-01 11:00:00", "Included", "Not Included"))

cor(filt_model_simp$alb_filt, filt_model_simp$filt_mod, method = "pearson")^2
NSE(filt_model_simp$alb_filt, filt_model_simp$filt_mod)

ggplot(filt_model_simp, aes(x=alb_filt, y=filt_mod))+
  geom_point(aes(color = newdust))+
  ylim(c(0,max(filt_model$filt_mod)))+
  xlim(c(0,1))+
  theme_bw()+
  geom_abline()+
  scale_color_gradient(low = "snow3", high = "red4")+
  labs(x="Observed Filtered α", y="Modeled Filtered α", color = "#Dust Events")+
   theme(text = element_text(size = 17.5, family = "Times New Roman"), legend.position = c(0.85,0.2))+
  facet_wrap(~model_bin)

```


#### Combined LM
```{r}
vis_simp <- vis_model_simp%>%
  select(datetime, vis_mod, alb_vis, site)
filt_simp <- filt_model_simp%>%
  select(datetime, filt_mod, alb_filt, site)
unfilt2 <- stats_setup%>%
  select(datetime, alb_unfilt, newdust, site)

combined_simp <- unfilt2%>%
  merge(., vis_simp, by = c("datetime","site"))%>%
  merge(., filt_simp, by = c("datetime", "site"))%>%
  mutate(model_unfilt = coef(lm_alb)[1] + coef(lm_alb)[2]*filt_mod + coef(lm_alb)[3]*vis_mod)%>%
  mutate(model_all = coef(lm_all)[1] + coef(lm_all)[2]*vis_mod + coef(lm_all)[3]*filt_mod)%>%
  mutate(reset = 0.85)

#Fresh Snow LM
cor(combined_simp$alb_unfilt, combined_simp$model_unfilt, method = "pearson")^2
NSE(combined_simp$alb_unfilt, combined_simp$model_unfilt)

#All snow LM
cor(combined_simp$alb_unfilt, combined_simp$model_all, method = "pearson")^2
NSE(combined_simp$alb_unfilt, combined_simp$model_all)

##Reset LM
cor(combined_simp$alb_unfilt, combined_simp$reset, method = "pearson")^2
NSE(combined_simp$alb_unfilt, combined_simp$reset)


ggplot(combined_simp, aes(x=alb_unfilt, y=model_unfilt))+
  geom_abline(alpha = 0.8)+
  geom_point(aes(y=model_unfilt), color = "red4", size = 0.7, alpha = 0.75)+
  geom_point(aes(y=model_all), color = "cyan4", size = 0.7, alpha = 0.75)+
  geom_point(aes(y=reset), color = "black", size = 0.5, alpha = 0.8)+
  xlim(c(0,1))+
  ylim(c(0,1))+
  theme_bw()+
  labs(x="Observed α", y="Modeled α", color = "#Dust Events")+
   theme(text = element_text(size = 17.5, family = "Times New Roman"), legend.position = c(0.85,0.2))

combined_long <- combined_simp%>%
  rename("All Values" = model_all, "Fresh Snow Values" = model_unfilt, "Reset Values" = reset)%>%
  gather(., key = "model", value = "albedo", -datetime, -site,- alb_unfilt, -newdust, -vis_mod, -filt_mod, -alb_vis, -alb_filt)

ggplot(combined_long, aes(x=alb_unfilt, y=albedo))+
  geom_abline(alpha = 0.8, linetype = "dashed")+
  geom_point(aes(color = model, shape = model), size = 1, alpha = 0.75)+
  xlim(c(0,1))+
  ylim(c(0,1))+
  scale_color_manual(values = c("cyan4","red4", "black"))+
  scale_shape_manual(values = c(15,17,16))+
  theme_bw()+
  labs(x="Observed α", y="Modeled α", color = "Model Type", shape = "Model Type")+
  theme(text = element_text(size = 17.5, family = "Times New Roman"), legend.position = c(0.75,0.2))

```
 
### Odd Values
```{r}
# names(combined_simp)
# 
# oddmodel <- combined_simp %>%
#   mutate(diff = alb_unfilt - model_unfilt)%>%
#   filter(diff > abs(0.32))
# oddmodel
# odd_dates = oddmodel$datetime
# odd_dates
# view(filter_setup)
# odd_filter <- filter_setup%>%
#   filter(datetime %in% odd_dates)

```

###Ground by Wavelength

```{r}
filt_ground <- new_df%>%
  filter(hour %in% c(10,11,12,13,14))%>%
  filter(alb_filt < 1 & alb_filt > 0)%>%
  filter(depth_m == 0)%>%
  filter(alb_filt < 0.45)%>%
  group_by(site)%>%
  summarise(mean = mean(alb_filt))
filt_ground

vis_ground <- new_df%>%
  filter(hour %in% c(10,11,12,13,14))%>%
  filter(alb_vis < 1 & alb_vis > 0)%>%
  filter(depth_m == 0)%>%
  filter(alb_vis < 0.2)%>%
  group_by(site)%>%
  summarise(mean = mean(alb_vis))
vis_ground
```

### TEST

```{r}
modeltest <- new_df%>%
  filter(site == "SASP")%>%
  filter(SY == "SY2009")%>%
  select(datetime, date, hour, SY, DOSY, alb_unfilt, depth_m, Tavg_C, newdust)%>%
  mutate(depth_diff = depth_m - lag(depth_m),
         depth_diff = ifelse(is.na(depth_diff), 0 , depth_diff),
         depth_diff = round(depth_diff, digits = 2),
         depth_diff_pos = ifelse(depth_diff > 0, depth_diff, 0),
         albedo_filt = ifelse(depth_m == 0, 0.30, NA),
         albedo_vis = ifelse(depth_m == 0, 0.07, NA),
         fresh =  ifelse(depth_diff > 0 & Tavg_C < 3, NA, 
                    ifelse(depth_diff > 0.01 & Tavg_C >= 3, NA, 0)),
         albedo = ifelse(depth_m == 0, 0.2, NA),
         reset_alb = ifelse(depth_diff_pos > 0,0.84, NA),
         reset_alb = ifelse(depth_m == 0, 0.2, reset_alb))

alb_vis <- modeltest$albedo_vis
alb_filt <- modeltest$albedo_filt
alb_model <- modeltest$albedo
fresh <- modeltest$fresh
diff <- modeltest$depth_diff_pos
depth <- modeltest$depth_m
temp <- modeltest$Tavg_C
dust <- modeltest$newdust
vrsg_alb <- modeltest$reset_alb


for(i in 1:nrow(modeltest)){
  if(is.na(vrsg_alb[i])){
    vrsg_alb[i] = ((vrsg_alb[i-1])*exp(-0.01))
  }
}

modeltest$reset_alb <- vrsg_alb

for(i in 1:nrow(modeltest)){
  if(is.na(alb_model[i]) & is.na(fresh[i]) & temp[i] < 3){
    
     alb_vis[i] = coef(lm_cool_vis)[1]+
                          coef(lm_cool_vis)[2]*diff[i]+
                          coef(lm_cool_vis)[3]*depth[i]+
                          coef(lm_cool_vis)[4]*alb_model[i-1]
                          #coef(lm_cool_vis)[5]*temp[i]+
                          #coef(lm_cool_vis)[6]*dust[i]
     
     alb_filt[i] = coef(lm_cool_filt)[1]+
                            coef(lm_cool_filt)[2]*diff[i]+
                            coef(lm_cool_filt)[3]*depth[i]+
                            coef(lm_cool_filt)[4]*alb_model[i-1]
                            #coef(lm_cool_filt)[4]*temp[i]
     
     alb_model[i] = coef(lm_alb)[1]+
                            coef(lm_alb)[2]*alb_filt[i]+
                            coef(lm_alb)[3]*alb_vis[i]
     
  }
  if(is.na(alb_model[i]) & is.na(fresh[i]) & temp[i] >= 3){
     
    alb_vis[i] = coef(lm_warm_vis)[1]+
                            coef(lm_warm_vis)[2]*diff[i]+
                            coef(lm_warm_vis)[3]*alb_model[i-1]+
                            coef(lm_warm_vis)[4]*temp[i]+
                            coef(lm_warm_vis)[5]*dust[i]+
                            coef(lm_warm_vis)[6]*depth[i]
    
    alb_filt[i] = coef(lm_warm_filt)[1]+
                            coef(lm_warm_filt)[2]*diff[i]+
                            coef(lm_warm_filt)[3]*alb_model[i-1]+
                            coef(lm_warm_filt)[4]*temp[i]+
                            coef(lm_warm_filt)[5]*depth[i]
    
   alb_model[i] = coef(lm_alb)[1]+
                            coef(lm_alb)[2]*alb_filt[i]+
                            coef(lm_alb)[3]*alb_vis[i]
       
  }else{if(is.na(alb_model[i]) & fresh[i] == 0 & temp[i] < 3){
    alb_model[i] = ((alb_model[i-1]*exp(-0.005)))
  }else{if(is.na(alb_model[i]) & fresh[i] == 0 & temp[i] >= 3){
    alb_model[i] = ((alb_model[i-1]*exp(-0.01)))}
    }
  }
}

modeltest$albedo <- alb_model

modeltest_xts <- modeltest%>%
  select(datetime, albedo, depth_m, alb_unfilt, reset_alb)%>%
  xts(., order.by = .$datetime)
dygraph(modeltest_xts)

ggplot(modeltest%>%filter(DOSY < 300), aes(x=alb_unfilt))+
  geom_point(aes(y=reset_alb), size =1, color = "red4")+
  geom_point(aes(y=albedo), size =1, color = "cyan4")+
  ylim(c(0,1))+
  geom_abline()+
  theme_bw()+
  labs(x="Observed", y="Modeled", color = "Depth (m)")+
  theme(text = element_text(family = "Times New Roman", size = 17.5))+
  xlim(c(0,1))

removeNA <- modeltest%>%
  filter(!is.na(alb_unfilt) &  alb_unfilt < 0.98 & alb_unfilt > 0)

cor(removeNA$alb_unfilt, removeNA$albedo, method = "pearson")^2
NSE(removeNA$alb_unfilt, removeNA$albedo)

cor(removeNA$alb_unfilt, removeNA$reset_alb, method = "pearson")^2
NSE(removeNA$alb_unfilt, removeNA$reset_alb)


```

#### Fresh test
```{r}

modeltest_fresh <- modeltest%>%
  filter(!is.na(alb_unfilt))%>%
  filter(depth_diff > 0)%>%
  mutate(reset_alb = ifelse(DOSY == 31 & hour == 10, 0.83, reset_alb))

ggplot(modeltest_fresh%>%filter(DOSY < 300), aes(x=alb_unfilt))+
  geom_point(aes(y=reset_alb), size =1, color = "red4")+
  geom_point(aes(y=albedo), size =1)+
  ylim(c(0,max(modeltest$albedo)))+
  geom_abline()+
  theme_bw()+
  labs(x="Observed", y="Modeled", color = "Depth (m)")+
  theme(text = element_text(family = "Times New Roman", size = 17.5))+
  xlim(c(0,1))

cor(modeltest_fresh$alb_unfilt, modeltest_fresh$albedo, method = "pearson")^2
NSE(modeltest_fresh$alb_unfilt, modeltest_fresh$albedo)

cor(modeltest_fresh$alb_unfilt, modeltest_fresh$reset_alb, method = "pearson")^2
NSE(modeltest_fresh$alb_unfilt, modeltest_fresh$reset_alb)

```

#### VIS

```{r}
coef(vis_lm_simp)
coef(filt_lm_simp)
coef(lm_alb)

view(new_df)
plot(vis_ground$alb_vis)
vis_ground <- new_df%>%
  filter(hour %in% c(10,11,12,13,14))%>%
  filter(alb_vis < 1 & alb_vis > 0)%>%
  filter(depth_m == 0)%>%
  filter(alb_vis < 0.2)%>%
  group_by(site)%>%
  summarise(mean = mean(alb_vis))
vis_ground

modeltest <- new_df%>%
  filter(site == "SBSP")%>%
  filter(SY == "SY2009")%>%
  select(datetime, date, hour, SY, DOSY, alb_unfilt, depth_m, Tavg_C, newdust)%>%
  mutate(depth_diff = depth_m - lag(depth_m),
         depth_diff = ifelse(is.na(depth_diff), 0 , depth_diff),
         depth_diff = round(depth_diff, digits = 2),
         depth_diff_pos = ifelse(depth_diff > 0, depth_diff, 0),
         albedo_vis = ifelse(depth_m == 0, 0.07, NA),
         alb_min = ifelse(Tavg_C <= -3 & depth_diff_pos == 0, 0.7, 
                               ifelse(Tavg_C > -3, 0.5, NA)),
         fresh_vis = ifelse(depth_diff > 0, NA, 0))

albedo <- modeltest$albedo_vis
fresh <- modeltest$fresh_vis
diff <- modeltest$depth_diff
depth <- modeltest$depth_m
temp <- modeltest$Tavg_C
dust <- modeltest$newdust

for(i in 1:nrow(modeltest)){
  if(is.na(albedo[i]) & is.na(fresh[i])){
    albedo[i] = coef(vis_lm_simp)[1]- coef(vis_lm_simp)[2]*diff[i] + coef(vis_lm_simp)[3]*log(depth[i]) + coef(vis_lm_simp)[4]*albedo[i-1] + coef(vis_lm_simp)[5]*temp[i] + coef(vis_lm_simp)*dust[i]
  }else{if(is.na(albedo[i] & fresh[i] == 0)){
    albedo[i] = ((albedo[i-1]*exp(-0.02)))
    }
  }
}

modeltest$albedo_vis <- albedo

modeltest_xts <- modeltest%>%
  select(datetime, albedo_vis, depth_m, alb_unfilt)%>%
  xts(., order.by = .$datetime)
dygraph(modeltest_xts)
```


### Binning
#### VIS
```{r}

lm_cool_vis <- vis_simp%>%
  filter(Tavg_C < 3)%>%
  filter(SY %in% c("SY2006", "SY2007", "SY2008", "SY2009", "SY2010", "SY2011"))%>%
  lm(data = ., alb_vis ~  depth_diff + depth_m + alb_tminus1) #+ Tavg_C + newdust)
summary(lm_cool_vis)
confint(lm_cool_vis)

lm_warm_vis <- vis_simp%>%
  filter(temp_tminus1 >= 3 )%>%
  #mutate(newdust = newdust/100)%>%
  filter(SY %in% c("SY2006", "SY2007", "SY2008", "SY2009", "SY2010", "SY2011"))%>%
  lm(data = ., alb_vis ~ depth_diff + alb_tminus1 +Tavg_C +newdust + depth_m)
summary(lm_warm_vis)
confint(lm_warm_vis)

vis_model_T <- vis_simp%>%
  mutate(vis_mod = ifelse(Tavg_C < 3, 
                            coef(lm_cool_vis)[1]+
                            coef(lm_cool_vis)[2]*depth_diff+
                            coef(lm_cool_vis)[3]*depth_m+
                            coef(lm_cool_vis)[4]*alb_tminus1,
                            #coef(lm_cool_vis)[5]*Tavg_C+
                            #coef(lm_cool_vis)[6]*newdust,
                          coef(lm_warm_vis)[1]+
                            coef(lm_warm_vis)[2]*depth_diff+
                            coef(lm_warm_vis)[3]*alb_tminus1+
                            coef(lm_warm_vis)[4]*Tavg_C+
                            coef(lm_warm_vis)[5]*newdust+
                            coef(lm_warm_vis)[6]*depth_m))%>%
  mutate(model_bin = ifelse(datetime < "2011-09-01 11:00:00", "Calibration", "Evaluation"))

cor(vis_model_T$alb_vis, vis_model_T$vis_mod, method = "pearson")^2
NSE(vis_model_T$alb_vis, vis_model_T$vis_mod)

ggplot(vis_model_T, aes(x=alb_vis, y=vis_mod))+
  geom_point(aes(color = newdust))+
  ylim(c(0,max(vis_model$vis_mod)))+
  xlim(c(0,1))+
  theme_bw()+
  geom_abline()+
  scale_color_gradient(low = "snow3", high = "red4")+
  labs(x="Observed Visible α", y="Modeled Visible α", color = "#Dust Events")+
   theme(text = element_text(size = 17.5, family = "Times New Roman"),legend.position = c(0.85,0.2))+
  facet_wrap(~model_bin)

```

#### NIR/SWIR
```{r}

lm_cool_filt <- filt_simp%>%
  filter(Tavg_C < 3)%>%
  filter(SY %in% c("SY2006", "SY2007", "SY2008", "SY2009", "SY2010", "SY2011"))%>%
  lm(data = ., alb_filt ~  depth_diff + depth_m + alb_tminus1)
summary(lm_cool_filt)
confint(lm_cool_filt)

lm_warm_filt <- filt_simp%>%
  filter(Tavg_C >= 3)%>%
  filter(SY %in% c("SY2006", "SY2007", "SY2008", "SY2009", "SY2010", "SY2011"))%>%
  lm(data = ., alb_filt ~ depth_diff + alb_tminus1 +Tavg_C +depth_m)
summary(lm_warm_filt)
confint(lm_warm_filt)

filt_model_T <- filt_simp%>%
  mutate(filt_mod = ifelse(Tavg_C < 3, coef(lm_cool_filt)[1]+
                            coef(lm_cool_filt)[2]*depth_diff+
                            coef(lm_cool_filt)[3]*depth_m+
                            coef(lm_cool_filt)[4]*alb_tminus1,
                            #coef(lm_cool_filt)[4]*Tavg_C,
                          coef(lm_warm_filt)[1]+
                            coef(lm_warm_filt)[2]*depth_diff+
                            coef(lm_warm_filt)[3]*alb_tminus1+
                            coef(lm_warm_filt)[4]*Tavg_C+
                            coef(lm_warm_filt)[5]*depth_m))%>%
  mutate(model_bin = ifelse(datetime < "2011-09-01 11:00:00", "Calibration", "Evalution"))

cor(filt_model_T$alb_filt, filt_model_T$filt_mod, method = "pearson")^2
NSE(filt_model_T$alb_filt, filt_model_T$filt_mod)

ggplot(filt_model_T, aes(x=alb_filt, y=filt_mod))+
  geom_point(aes(color = depth_m))+
  ylim(c(0,max(vis_model$vis_mod)))+
  xlim(c(0,1))+
  theme_bw()+
  geom_abline()+
  scale_color_gradient(low = "snow3", high = "red4")+
  labs(x="Observed Filtered α", y="Modeled Filtered α", color = "Depth (m)")+
   theme(text = element_text(size = 17.5, family = "Times New Roman"),legend.position = c(0.85,0.2))+
  facet_wrap(~model_bin)

```

#### Combined

```{r}
filt_T <- filt_model_T%>%
  select(datetime, site, filt_mod)
vis_T <- vis_model_T%>%
  select(datetime, site, vis_mod)
unfilt2 <- stats_setup%>%
  select(datetime, alb_unfilt, newdust, site)

combined_simp_T <- unfilt2%>%
  merge(., vis_T, by = c("datetime","site"))%>%
  merge(., filt_T, by = c("datetime", "site"))%>%
  mutate(model_unfilt = coef(lm_alb)[1] + coef(lm_alb)[2]*filt_mod + coef(lm_alb)[3]*vis_mod)%>%
  mutate(model_all = coef(lm_all)[1] + coef(lm_all)[2]*vis_mod + coef(lm_all)[3]*filt_mod)%>%
  mutate(reset = 0.85)

#Fresh Snow LM
cor(combined_simp_T$alb_unfilt, combined_simp_T$model_unfilt, method = "pearson")^2
NSE(combined_simp_T$alb_unfilt, combined_simp_T$model_unfilt)

#All snow LM
cor(combined_simp_T$alb_unfilt, combined_simp_T$model_all, method = "pearson")^2
NSE(combined_simp_T$alb_unfilt, combined_simp_T$model_all)

cor(combined_simp_T$alb_unfilt, combined_simp_T$reset, method = "pearson")^2
NSE(combined_simp_T$alb_unfilt, combined_simp_T$reset)


ggplot(combined_simp_T, aes(x=alb_unfilt, y=model_unfilt))+
  geom_abline(alpha = 0.8)+
  geom_point(aes(y=model_unfilt), color = "red4", size = 0.7, alpha = 0.75)+
  geom_point(aes(y=model_all), color = "cyan4", size = 0.7, alpha = 0.75)+
  geom_point(aes(y=reset), color = "black", size = 0.5, alpha = 0.8)+
  xlim(c(0,1))+
  ylim(c(0,1))+
  theme_bw()+
  labs(x="Observed α", y="Modeled α", color = "#Dust Events")+
   theme(text = element_text(size = 17.5, family = "Times New Roman"), legend.position = c(0.85,0.2))

names(combined_long_T)

combined_long_T <- combined_simp_T%>%
  rename("All-Snow" = model_all, "Fresh-Snow" = model_unfilt, "CLASS" = reset)%>%
  gather(., key = "model", value = "albedo", -datetime, -site,- alb_unfilt, -newdust, -vis_mod, -filt_mod)

combined_long_T$model <- factor(combined_long_T$model, levels = c( "CLASS","All-Snow","Fresh-Snow"))

combined_long_T <- combined_long_T%>%
  arrange(model)

ggplot(combined_long_T, aes(x=alb_unfilt, y=albedo))+
  geom_abline(alpha = 0.8, linetype = "dashed")+
  geom_point(aes(color = model, shape = model), size = 1, alpha = 0.75)+
  xlim(c(0,1))+
  ylim(c(0,1))+
  scale_color_manual(values = c("red4", "purple3", "cyan4"))+
  scale_shape_manual(values = c(16,15,17))+
  theme_bw()+
  labs(x="Observed Fresh Snow α", y="Modeled Fresh Snow α", color = "Model", shape = "Model")+
  theme(text = element_text(size = 17.5, family = "Times New Roman"), legend.position = c(0.75,0.15))

```


### TEST (separate)

```{r}
modeltest_sep <- new_df%>%
  filter(site == "SBSP")%>%
  filter(SY == "SY2009")%>%
  select(datetime, date, hour, SY, DOSY, alb_unfilt, depth_m, Tavg_C, newdust)%>%
  mutate(depth_diff = depth_m - lag(depth_m),
         depth_diff = ifelse(is.na(depth_diff), 0 , depth_diff),
         depth_diff = round(depth_diff, digits = 2),
         depth_diff_pos = ifelse(depth_diff > 0, depth_diff, 0),
         albedo_filt = ifelse(depth_m == 0, 0.30, NA),
         albedo_vis = ifelse(depth_m == 0, 0.07, NA),
         fresh =  ifelse(depth_diff > 0, NA, 0),
         albedo = ifelse(depth_m == 0, 0.2, NA),
         reset_alb = ifelse(depth_diff_pos > 0, 0.84, NA),
         reset_alb = ifelse(depth_m == 0, 0.2, reset_alb))

alb_vis <- modeltest_sep$albedo_vis
alb_filt <- modeltest_sep$albedo_filt
alb_model <- modeltest_sep$albedo
fresh <- modeltest_sep$fresh
diff <- modeltest_sep$depth_diff_pos
depth <- modeltest_sep$depth_m
temp <- modeltest_sep$Tavg_C
dust <- modeltest_sep$newdust
vrsg_alb <- modeltest_sep$reset_alb

for(i in 1:nrow(modeltest_sep)){
  if(is.na(vrsg_alb[i])){
    vrsg_alb[i] = ((vrsg_alb[i-1])*exp(-0.01))
  }
}

modeltest_sep$reset_alb <- vrsg_alb

# coef(lm_cool_vis_sep)
# coef(lm_warm_vis_sep)
# coef(lm_cool_filt_sep)
# coef(lm_warm_filt_sep)

for(i in 1:nrow(modeltest_sep)){
  if(is.na(alb_model[i]) & is.na(fresh[i]) & temp[i] < 3){
    
     alb_vis[i] = coef(lm_cool_vis_sep)[1]+
                          coef(lm_cool_vis_sep)[2]*diff[i]+
                          coef(lm_cool_vis_sep)[3]*depth[i]+
                          coef(lm_cool_vis_sep)[4]*alb_vis[i-1]
                          #coef(lm_cool_vis)[5]*temp[i]+
                          #coef(lm_cool_vis)[6]*dust[i]
     
     alb_filt[i] = coef(lm_cool_filt_sep)[1]+
                            coef(lm_cool_filt_sep)[2]*diff[i]+
                            coef(lm_cool_filt_sep)[3]*depth[i]+
                            coef(lm_cool_filt_sep)[4]*alb_filt[i-1]
                            #coef(lm_cool_filt)[4]*temp[i]
     
     alb_model[i] = coef(lm_alb)[1]+
                            coef(lm_alb)[2]*alb_filt[i]+
                            coef(lm_alb)[3]*alb_vis[i]
    
  }
  if(is.na(alb_model[i]) & is.na(fresh[i]) & temp[i] >= 3){
     
    alb_vis[i] = coef(lm_warm_vis_sep)[1]+
                            coef(lm_warm_vis_sep)[2]*diff[i]+
                            #coef(lm_warm_vis)[3]*depth[i]+
                            coef(lm_warm_vis_sep)[3]*alb_vis[i-1]+
                            coef(lm_warm_vis_sep)[4]*temp[i]
                            coef(lm_warm_vis_sep)[5]*dust[i]
    
    alb_filt[i] = coef(lm_warm_filt_sep)[1]+
                            coef(lm_warm_filt_sep)[2]*diff[i]+
                            #coef(lm_warm_filt)[3]*depth[i]+
                            coef(lm_warm_filt_sep)[3]*alb_filt[i-1]+
                            coef(lm_warm_filt_sep)[4]*temp[i]
    
   alb_model[i] = coef(lm_alb)[1]+
                            coef(lm_alb)[2]*alb_filt[i]+
                            coef(lm_alb)[3]*alb_vis[i]
       
  }else{if(is.na(alb_model[i]) & fresh[i] == 0 & temp[i] < 3){
    
    alb_vis[i] = ((alb_vis[i-1]*exp(-0.005)))
    
    alb_filt[i] = ((alb_filt[i-1]*exp(-0.005)))
    
    alb_model[i] = coef(lm_alb)[1]+
                            coef(lm_alb)[2]*alb_filt[i]+
                            coef(lm_alb)[3]*alb_vis[i]
    
  }else{if(is.na(alb_model[i]) & fresh[i] == 0 & temp[i] >= 3){
      
    alb_vis[i] = ((alb_vis[i-1]*exp(-0.01)))
    
    alb_filt[i] = ((alb_filt[i-1]*exp(-0.04)))
    
    alb_model[i] = coef(lm_alb)[1]+
                            coef(lm_alb)[2]*alb_filt[i]+
                            coef(lm_alb)[3]*alb_vis[i]
  }
  }
  }
}


modeltest_sep$albedo <- alb_model

modeltest_xts_sep <- modeltest_sep%>%
  select(datetime, albedo, depth_m, alb_unfilt, reset_alb)%>%
  xts(., order.by = .$datetime)
dygraph(modeltest_xts_sep)

ggplot(modeltest_sep%>%filter(DOSY < 300), aes(x=alb_unfilt))+
  geom_point(aes(y=reset_alb), size =1, color = "red4")+
  geom_point(aes(y=albedo), size =1)+
  ylim(c(0,1))+
  geom_abline()+
  theme_bw()+
  labs(x="Observed", y="Modeled", color = "Depth (m)")+
  theme(text = element_text(family = "Times New Roman", size = 17.5))+
  xlim(c(0,1))

removeNA_sep <- modeltest_sep%>%
  filter(!is.na(alb_unfilt))

cor(removeNA_sep$alb_unfilt, removeNA_sep$albedo, method = "pearson")^2
NSE(removeNA_sep$alb_unfilt, removeNA_sep$albedo)

cor(removeNA_sep$alb_unfilt, removeNA_sep$reset_alb, method = "pearson")^2
NSE(removeNA_sep$alb_unfilt, removeNA_sep$reset_alb)


```
#### VIS
```{r}

lm_cool_vis_sep <- vis_simp%>%
  filter(Tavg_C < 3)%>%
  filter(SY %in% c("SY2006", "SY2007", "SY2008", "SY2009", "SY2010", "SY2011"))%>%
  lm(data = ., alb_vis ~  depth_diff + depth_m + vis_tminus1) #+ Tavg_C + newdust)
summary(lm_cool_vis_sep)
confint(lm_cool_vis_sep)

lm_warm_vis_sep <- vis_simp%>%
  filter(temp_tminus1 >= 3)%>%
  filter(SY %in% c("SY2006", "SY2007", "SY2008", "SY2009", "SY2010", "SY2011"))%>%
  lm(data = ., alb_vis ~  depth_diff + vis_tminus1 +Tavg_C +newdust) #+depth_m)
summary(lm_warm_vis_sep)
confint(lm_warm_vis_sep)

vis_model_T_sep <- vis_simp%>%
  mutate(vis_mod = ifelse(Tavg_C < 3, coef(lm_cool_vis_sep)[1]+
                            coef(lm_cool_vis_sep)[2]*depth_diff+
                            coef(lm_cool_vis_sep)[3]*depth_m+
                            coef(lm_cool_vis_sep)[4]*vis_tminus1,
                            #coef(lm_cool_vis)[5]*Tavg_C+
                            #coef(lm_cool_vis)[6]*newdust,
                          coef(lm_warm_vis_sep)[1]+
                            coef(lm_warm_vis_sep)[2]*depth_diff+
                            #coef(lm_warm_vis)[3]*depth_m+
                            coef(lm_warm_vis_sep)[3]*vis_tminus1+
                            coef(lm_warm_vis_sep)[4]*Tavg_C+
                            coef(lm_warm_vis_sep)[5]*newdust))%>%
  mutate(model_bin = ifelse(datetime < "2011-09-01 11:00:00", "Calibration", "Evaluation"))

cor(vis_model_T_sep$alb_vis, vis_model_T_sep$vis_mod, method = "pearson")^2
NSE(vis_model_T_sep$alb_vis, vis_model_T_sep$vis_mod)

ggplot(vis_model_T_sep, aes(x=alb_vis, y=vis_mod))+
  geom_point(aes(color = newdust))+
  ylim(c(0,max(vis_model$vis_mod)))+
  xlim(c(0,1))+
  theme_bw()+
  geom_abline()+
  scale_color_gradient(low = "snow3", high = "red4")+
  labs(x="Observed Visible α", y="Modeled Visible α", color = "#Dust Events")+
   theme(text = element_text(size = 17.5, family = "Times New Roman"),legend.position = c(0.85,0.2))+
  facet_wrap(~model_bin)


```
#### FILT
```{r}

lm_cool_filt_sep <- filt_simp%>%
  filter(Tavg_C < 3)%>%
  filter(SY %in% c("SY2006", "SY2007", "SY2008", "SY2009", "SY2010", "SY2011"))%>%
  lm(data = ., alb_filt ~  depth_diff + depth_m + filt_tminus1)
summary(lm_cool_filt_sep) 
confint(lm_cool_filt_sep)

lm_warm_filt_sep <- filt_simp%>%
  filter(temp_tminus1 >= 3)%>%
  filter(SY %in% c("SY2006", "SY2007", "SY2008", "SY2009", "SY2010", "SY2011"))%>%
  lm(data = ., alb_filt ~ depth_diff + filt_tminus1 +Tavg_C)#+depth_m)
summary(lm_warm_filt_sep)
confint(lm_warm_filt_sep)

filt_model_T_sep <- filt_simp%>%
  mutate(filt_mod = ifelse(Tavg_C < 3, coef(lm_cool_filt_sep)[1]+
                            coef(lm_cool_filt_sep)[2]*depth_diff+
                            coef(lm_cool_filt_sep)[3]*depth_m+
                            coef(lm_cool_filt_sep)[4]*filt_tminus1,
                            #coef(lm_cool_filt)[4]*Tavg_C,
                          coef(lm_warm_filt_sep)[1]+
                            coef(lm_warm_filt_sep)[2]*depth_diff+
                            #coef(lm_warm_filt)[3]*depth_m+
                            coef(lm_warm_filt_sep)[3]*filt_tminus1+
                            coef(lm_warm_filt_sep)[4]*Tavg_C))%>%
  mutate(model_bin = ifelse(datetime < "2011-09-01 11:00:00", "Calibration", "Evalution"))

cor(filt_model_T_sep$alb_filt, filt_model_T_sep$filt_mod, method = "pearson")^2
NSE(filt_model_T_sep$alb_filt, filt_model_T_sep$filt_mod)

ggplot(filt_model_T_sep, aes(x=alb_filt, y=filt_mod))+
  geom_point(aes(color = newdust))+
  ylim(c(0,max(vis_model$vis_mod)))+
  xlim(c(0,1))+
  theme_bw()+
  geom_abline()+
  scale_color_gradient(low = "snow3", high = "red4")+
  labs(x="Observed Filtered α", y="Modeled Filtered α", color = "#Dust Events")+
   theme(text = element_text(size = 17.5, family = "Times New Roman"),legend.position = c(0.85,0.2))+
  facet_wrap(~model_bin)
```

### Temp vs Albedo
```{r}
names(new_df)

fresh_temp <- new_df%>%
  group_by(site)%>%
  mutate(depth_diff = depth_m - lag(depth_m),
         depth_diff = ifelse(is.na(depth_diff), 0, depth_diff),
         alb_diff = alb_unfilt - lag(alb_unfilt),
         alb_diff = ifelse(is.na(alb_unfilt), 0, alb_diff))%>%
  ungroup()%>%
  filter(alb_unfilt < 0.98 & alb_unfilt > 0.15)%>%
  filter(depth_diff > 0)%>%
  filter(alb_diff > 0)%>%
  filter(hour %in% c(10,11,12,13,14))%>%
  dplyr::select(SY, DOSY, site, datetime, depth_m, Tavg_C, alb_unfilt)
  
ggplot(fresh_temp, aes(x=Tavg_C, y=alb_unfilt))+
  #geom_vline(xintercept = 2, color = "black", linetype = "dashed", alpha = 0.7)+
  geom_point(aes(color = DOSY, shape = site), alpha = 0.9)+
  scale_shape_manual(values = c(1,4))+
  theme_bw()+
  ylim(c(0,1))+
  scale_color_gradient2(low = "tan4", mid = "snow3", high = "gray25", midpoint = 182)+
  #facet_wrap(~site)+
  theme(legend.position = c(0.2, 0.27), text = element_text(size = 17.5, family = "Times New Roman"))+
  labs(x="Temperature (°C)", y= "Observed Albedo", shape = element_blank())
  

```


### Mapping SBSP
```{r}

sbspmodel <- function(snowyear){

      df <- new_df%>%
        filter(site == "SBSP")%>%
        filter(SY == snowyear)%>%
        select(datetime, date, hour, SY, DOSY, alb_unfilt, depth_m, Tavg_C, newdust)%>%
        mutate(depth_diff = depth_m - lag(depth_m),
               depth_diff = ifelse(is.na(depth_diff), 0 , depth_diff),
               depth_diff = round(depth_diff, digits = 2),
               depth_diff_pos = ifelse(depth_diff > 0, depth_diff, 0),
               albedo_filt = ifelse(depth_m == 0, 0.30, NA),
               albedo_vis = ifelse(depth_m == 0, 0.07, NA),
               fresh =  ifelse(depth_diff > 0 & Tavg_C <= 3, NA, 
                    ifelse(depth_diff > 0.01 & Tavg_C > 3, NA, 0)),
               albedo = ifelse(depth_m == 0, 0.2, NA),
               reset_alb = ifelse(depth_diff_pos > 0, 0.84, NA),
               reset_alb = ifelse(depth_m == 0, 0.2, reset_alb),
               alb_min = ifelse(Tavg_C < 0, 0.7, 0.5))
      
      alb_vis <- df$albedo_vis
      alb_filt <- df$albedo_filt
      alb_model <- df$albedo
      fresh <- df$fresh
      diff <- df$depth_diff_pos
      depth <- df$depth_m
      temp <- df$Tavg_C
      dust <- df$newdust
      vrsg_alb <- df$reset_alb
      alb_min <- df$ alb_min
      
      for(i in 1:nrow(df)){
        if(is.na(vrsg_alb[i])){
          vrsg_alb[i] = ((vrsg_alb[i-1] - alb_min[i])*exp(-0.01) + alb_min[i])
        }
      }
      
      df$reset_alb <- vrsg_alb
      
      for(i in 1:nrow(df)){
        if(is.na(alb_model[i]) & is.na(fresh[i]) & temp[i] < 3){
          
           alb_vis[i] = coef(lm_cool_vis)[1]+
                                coef(lm_cool_vis)[2]*diff[i]+
                                coef(lm_cool_vis)[3]*depth[i]+
                                coef(lm_cool_vis)[4]*alb_model[i-1]
                                #coef(lm_cool_vis)[5]*temp[i]+
                                #coef(lm_cool_vis)[6]*dust[i]
           
           alb_filt[i] = coef(lm_cool_filt)[1]+
                                  coef(lm_cool_filt)[2]*diff[i]+
                                  coef(lm_cool_filt)[3]*depth[i]+
                                  coef(lm_cool_filt)[4]*alb_model[i-1]
                                  #coef(lm_cool_filt)[4]*temp[i]
           
           alb_model[i] = coef(lm_alb)[1]+
                                  coef(lm_alb)[2]*alb_filt[i]+
                                  coef(lm_alb)[3]*alb_vis[i]
           
           alb_model[i] = ifelse(alb_model[i] > 0.97, 0.97, alb_model[i])
           
        }
        if(is.na(alb_model[i]) & is.na(fresh[i]) & temp[i] >= 3){
           
          alb_vis[i] = coef(lm_warm_vis)[1]+
                                  coef(lm_warm_vis)[2]*diff[i]+
                                  coef(lm_warm_vis)[3]*alb_model[i-1]+
                                  coef(lm_warm_vis)[4]*temp[i]+
                                  coef(lm_warm_vis)[5]*dust[i]+
                                  coef(lm_warm_vis)[6]*depth[i]
          
          alb_filt[i] = coef(lm_warm_filt)[1]+
                                  coef(lm_warm_filt)[2]*diff[i]+
                                  coef(lm_warm_filt)[3]*alb_model[i-1]+
                                  coef(lm_warm_filt)[4]*temp[i]+
                                  coef(lm_warm_filt)[5]*depth[i]
          
         alb_model[i] = coef(lm_alb)[1]+
                                  coef(lm_alb)[2]*alb_filt[i]+
                                  coef(lm_alb)[3]*alb_vis[i]
         
         alb_model[i] = ifelse(alb_model[i] > 0.97, 0.97, alb_model[i])
             
        }else{if(is.na(alb_model[i]) & fresh[i] == 0 & temp[i] < 3){
          alb_model[i] = (((alb_model[i-1] - 0.2)*exp(-0.005))+0.2)
        }else{if(is.na(alb_model[i]) & fresh[i] == 0 & temp[i] >= 3){
          alb_model[i] = (((alb_model[i-1] - 0.2)*exp(-0.01))+0.2)}
          }
        }
      }
      
      df$albedo <- alb_model
      
  return(df)
      
}

SY = unique(new_df$SY)
SY = SY[!is.na(SY)]
SY = SY[!SY == "SY2005"]
SY = SY[!SY == "SY2012"]

sbsp_model <- map_dfr(SY, sbspmodel)

sbsp_clean <- sbsp_model%>%
  filter(alb_unfilt > 0 & alb_unfilt < 0.98)%>%
  filter(!is.na(alb_unfilt))%>%
  mutate(site = "SBSP")

cor(sbsp_clean$alb_unfilt, sbsp_clean$albedo, method = "pearson")^2
NSE(sbsp_clean$alb_unfilt, sbsp_clean$albedo)

cor(sbsp_clean$alb_unfilt, sbsp_clean$reset_alb, method = "pearson")^2
NSE(sbsp_clean$alb_unfilt, sbsp_clean$reset_alb)

ggplot(sbsp_clean%>%filter(hour %in% c(12)), aes(x=DOSY))+
  geom_point(aes(y=reset_alb))+
  geom_point(aes(y=alb_unfilt), color = "blue4", alpha = 0.2)+
  facet_wrap(~SY)+
  theme_bw()

ggplot(sbsp_clean, aes(x=alb_unfilt))+
  geom_point(aes(y=reset_alb), size = 0.7, alpha = 0.2, color = "red4")+
  geom_point(aes(y=albedo), size = 0.7, alpha = 0.4, color = "cyan4")+
  theme_bw()+
  xlim(c(0,1))+
  ylim(c(0,1))+
  geom_abline(linetype = "dashed")+
  labs(x="Observed", y = "Modeled", subtitle = "SBSP")+
  theme(text = element_text(size = 17.5, family = "Times New Roman"))

ggplot(sbsp_clean%>%filter(depth_diff > 0), aes(x=alb_unfilt))+
  geom_point(aes(y=reset_alb), size = 0.7, alpha = 0.2, color = "red4")+
  geom_point(aes(y=albedo), size = 0.7, alpha = 0.4, color = "cyan4")+
  theme_bw()+
  xlim(c(0,1))+
  ylim(c(0,1))+
  geom_abline(linetype = "dashed")+
  labs(x="Observed", y = "Modeled")

sbsp_xts <- sbsp_model%>%
  select(datetime, alb_unfilt, albedo, depth_m, reset_alb)%>%
  xts(., order.by = .$datetime)
dygraph(sbsp_xts)

```


### Mapping SASP

```{r}
saspmodel <- function(snowyear){

      df <- new_df%>%
        filter(site == "SASP")%>%
        filter(SY == snowyear)%>%
        select(datetime, date, hour, SY, DOSY, alb_unfilt, depth_m, Tavg_C, newdust)%>%
        mutate(depth_diff = depth_m - lag(depth_m),
               depth_diff = ifelse(is.na(depth_diff), 0 , depth_diff),
               depth_diff = round(depth_diff, digits = 2),
               depth_diff_pos = ifelse(depth_diff > 0, depth_diff, 0),
               albedo_filt = ifelse(depth_m == 0, 0.30, NA),
               albedo_vis = ifelse(depth_m == 0, 0.07, NA),
               fresh =  ifelse(depth_diff > 0 & Tavg_C <= 3, NA, 
                    ifelse(depth_diff > 0.01 & Tavg_C > 3, NA, 0)),
               albedo = ifelse(depth_m == 0, 0.2, NA),
               reset_alb = ifelse(depth_diff_pos > 0, 0.84, NA),
               reset_alb = ifelse(depth_m == 0, 0.2, reset_alb),
               alb_min = ifelse(Tavg_C < 0, 0.7, 0.5))
      
      alb_vis <- df$albedo_vis
      alb_filt <- df$albedo_filt
      alb_model <- df$albedo
      fresh <- df$fresh
      diff <- df$depth_diff_pos
      depth <- df$depth_m
      temp <- df$Tavg_C
      dust <- df$newdust
      vrsg_alb <- df$reset_alb
      alb_min <- df$ alb_min
      
      for(i in 1:nrow(df)){
        if(is.na(vrsg_alb[i])){
          vrsg_alb[i] = ((vrsg_alb[i-1]-alb_min)*exp(-0.01)+alb_min)
        }
      }
      
      df$reset_alb <- vrsg_alb
      
      for(i in 1:nrow(df)){
        if(is.na(alb_model[i]) & is.na(fresh[i]) & temp[i] < 3){
          
           alb_vis[i] = coef(lm_cool_vis)[1]+
                                coef(lm_cool_vis)[2]*diff[i]+
                                coef(lm_cool_vis)[3]*depth[i]+
                                coef(lm_cool_vis)[4]*alb_model[i-1]
                                #coef(lm_cool_vis)[5]*temp[i]+
                                #coef(lm_cool_vis)[6]*dust[i]
           
           alb_filt[i] = coef(lm_cool_filt)[1]+
                                  coef(lm_cool_filt)[2]*diff[i]+
                                  coef(lm_cool_filt)[3]*depth[i]+
                                  coef(lm_cool_filt)[4]*alb_model[i-1]
                                  #coef(lm_cool_filt)[4]*temp[i]
           
           alb_model[i] = coef(lm_alb)[1]+
                                  coef(lm_alb)[2]*alb_filt[i]+
                                  coef(lm_alb)[3]*alb_vis[i]
           
           alb_model[i] = ifelse(alb_model[i] > 0.97, 0.97, alb_model[i])
           
        }
        if(is.na(alb_model[i]) & is.na(fresh[i]) & temp[i] >= 3){
           
          alb_vis[i] = coef(lm_warm_vis)[1]+
                                  coef(lm_warm_vis)[2]*diff[i]+
                                  coef(lm_warm_vis)[3]*alb_model[i-1]+
                                  coef(lm_warm_vis)[4]*temp[i]+
                                  coef(lm_warm_vis)[5]*dust[i]+
                                  coef(lm_warm_vis)[6]*depth[i]
          
          alb_filt[i] = coef(lm_warm_filt)[1]+
                                  coef(lm_warm_filt)[2]*diff[i]+
                                  coef(lm_warm_filt)[3]*alb_model[i-1]+
                                  coef(lm_warm_filt)[4]*temp[i]+
                                  coef(lm_warm_filt)[5]*depth[i]
          
         alb_model[i] = coef(lm_alb)[1]+
                                  coef(lm_alb)[2]*alb_filt[i]+
                                  coef(lm_alb)[3]*alb_vis[i]
         
         alb_model[i] = ifelse(alb_model[i] > 0.97, 0.97, alb_model[i])
             
        }else{if(is.na(alb_model[i]) & fresh[i] == 0 & temp[i] < 3){
          alb_model[i] = ((alb_model[i-1]-0.2)*exp(-0.005)+0.2)
        }else{if(is.na(alb_model[i]) & fresh[i] == 0 & temp[i] >= 3){
          alb_model[i] = ((alb_model[i-1]-0.2)*exp(-0.01)+0.2)}
          }
        }
      }
      
      df$albedo <- alb_model
      
  return(df)
      
}

SY = unique(new_df$SY)
SY = SY[!is.na(SY)]
SY = SY[!SY == "SY2005"]
SY = SY[!SY == "SY2012"]
SY = SY[!SY == "SY2011"]

sasp_model <- map_dfr(SY, saspmodel)

sasp_clean <- sasp_model%>%
  filter(alb_unfilt > 0 & alb_unfilt < 0.98)%>%
  filter(!is.na(alb_unfilt))%>%
  mutate(site = "SASP")

cor(sasp_clean$alb_unfilt, sasp_clean$albedo, method = "pearson")^2
NSE(sasp_clean$alb_unfilt, sasp_clean$albedo)

cor(sasp_clean$alb_unfilt, sasp_clean$reset_alb, method = "pearson")^2
NSE(sasp_clean$alb_unfilt, sasp_clean$reset_alb)

ggplot(sasp_clean%>%filter(hour %in% c(10,11,12,13,14)), aes(x=DOSY))+
  geom_point(aes(y=albedo))+
  geom_point(aes(y=alb_unfilt), color = "blue4", alpha = 0.2)+
  facet_wrap(~SY)+
  theme_bw()

ggplot(sasp_clean, aes(x=alb_unfilt))+
  geom_point(aes(y=reset_alb), size = 0.7, alpha = 0.2, color = "red4")+
  geom_point(aes(y=albedo), size = 0.7, alpha = 0.3, color = "cyan4")+
  theme_bw()+
  xlim(c(0,1))+
  ylim(c(0,1))+
  geom_abline(linetype = "dashed")+
  labs(x="Observed", y = "Modeled", subtitle = "SASP")+
   theme(text = element_text(size = 17.5, family = "Times New Roman"))


ggplot(sasp_clean%>%filter(depth_diff > 0), aes(x=alb_unfilt))+
  geom_point(aes(y=reset_alb), size = 0.7, alpha = 0.2, color = "red4")+
  geom_point(aes(y=albedo), size = 0.7, alpha = 0.4, color = "cyan4")+
  theme_bw()+
  xlim(c(0,1))+
  ylim(c(0,1))+
  geom_abline(linetype = "dashed")+
  labs(x="Observed", y = "Modeled")

sasp_xts <- sasp_model%>%
  select(datetime, alb_unfilt, albedo, depth_m, reset_alb)%>%
  xts(., order.by = .$datetime)
dygraph(sasp_xts)

```

### Final Combined

```{r}
final <- rbind(sasp_clean, sbsp_clean)%>%
  mutate(fresh = ifelse(depth_diff > 0.01, "Fresh", "Decay"))#%>%
  #filter(depth_m > 0)

cor(final$alb_unfilt, final$albedo, method = "pearson")^2
NSE(final$alb_unfilt, final$albedo)

cor(final$alb_unfilt, final$reset_alb, method = "pearson")^2
NSE(final$alb_unfilt, final$reset_alb)

final_cov <- final%>%
  filter(!is.na(depth_m) & !is.na(Tavg_C))

cov(final_cov$depth_m, final_cov$Tavg_C)

names(final)
final_long <- final %>%
  dplyr::select(datetime, SY, DOSY, alb_unfilt, depth_m, albedo, reset_alb, site, hour, fresh)%>%
  rename("CLASS Fresh α" = reset_alb, "Variable Fresh α" = albedo)%>%
  gather(., key = "Model", value = "Albedo", -datetime, -SY, -alb_unfilt, -depth_m, -site, - hour, -fresh, -DOSY)%>%
  arrange(Model)

ggplot(final_long, aes(x=alb_unfilt))+
  geom_point(aes(y=Albedo, color = Model), size = 0.7, alpha = 0.3)+
  scale_color_manual(values = c("red4", "cyan4"))+
  theme_bw()+
  xlim(c(0,1))+
  ylim(c(0,1))+
  geom_abline(linetype = "dashed")+
  labs(x="Observed α", y = "Modeled α")+
  theme(text = element_text(size = 17.5, family = "Times New Roman"), legend.title = element_blank(), legend.position = c(0.85,0.07))+
  facet_grid(site~fresh)


fresh_decay_stats <- final%>%
  filter(fresh == "Decay")
  #filter(depth_m > 0)

cor(fresh_decay_stats$alb_unfilt, fresh_decay_stats$albedo, method = "pearson")^2
NSE(fresh_decay_stats$alb_unfilt, fresh_decay_stats$albedo)

cor(fresh_decay_stats$alb_unfilt, fresh_decay_stats$reset_alb, method = "pearson")^2
NSE(fresh_decay_stats$alb_unfilt, fresh_decay_stats$reset_alb)

```

### Absorption
```{r}
abs <- new_df%>%
  select(datetime, site, hkin_unfilt)

names(absorption)
 
absorption <- final%>%
  merge(., abs, by = c("datetime", "site"))%>%
  select(datetime, SY, DOSY, site, alb_unfilt, albedo, reset_alb, hkin_unfilt)%>%
  rename("Static Fresh α" = reset_alb, "Variable Fresh α" = albedo, "Observed α"= alb_unfilt)%>%
  gather(., key = "Model", value = "Albedo", -datetime, -SY, -site, - hkin_unfilt, -DOSY)%>%
  mutate(Absorbed = (1-Albedo)*hkin_unfilt)%>%
  mutate(time = ifelse(DOSY <= 91, "First Events", 
                       ifelse(DOSY < 227 & DOSY > 91, "Accumulation", "Melt")))%>%
  mutate(filter = ifelse(DOSY > 227 & Albedo < 0.25, NA, 0))%>%
  filter(!is.na(filter))%>%
  select(!filter)

absorption$time <- factor(absorption$time, levels = c("First Events", "Accumulation", "Melt"))
str(absorption)

abs_stats <- absorption%>%
  group_by(site, SY, Model, time)%>%
  filter(!is.na(hkin_unfilt))%>%
  summarise(net = sum(Absorbed))%>%
  spread(., key = "Model", value = "net")%>%
  rename("static" = 5, "observed" = 4, "variable" = 6)%>%
  mutate(static_diff = static -observed,
         variable_diff = variable - observed,
         static_diff = round(static_diff, digits = 0),
         variable_diff = round(variable_diff, digits = 0))%>%
  mutate_if(is.numeric, round)%>%
  mutate(percent_static = static_diff/observed,
         percent_variable = variable_diff/observed)

abs_short <-abs_stats%>%
  group_by(site, time)%>%
  summarise(mean_static = mean(static),
            mean_variable = mean(variable),
            mean_observed = mean(observed),
            max_static =max(static),
            max_variable = max(variable),
            max_observed = max(observed),
            min_static = min(static),
            min_variable = min(variable),
            min_observed = min(observed),
            mean_percent_static = mean(percent_static),
            min_percent_static = min(percent_static),
            max_percent_static = max(percent_static),
            mean_percent_variable = mean(percent_variable),
            min_percent_variable = min(percent_variable),
            max_percent_variable = max(percent_variable))

names(abs_short)

abs_mean<- abs_short%>%
  select(1,2,5,3,4)%>%
  rename("Observed" = mean_observed, "CLASS" = mean_static, "Variable Fresh" = mean_variable)%>%
  gather(., key = "Model", value = "Mean", -site, -time)

abs_max<- abs_short%>%
  select(1,2,8,6,7)%>%
  rename("Observed" = max_observed, "CLASS" = max_static, "Variable Fresh" = max_variable)%>%
  gather(., key = "Model", value = "Max", -site, -time)

abs_min<- abs_short%>%
  select(1,2,11,9,10)%>%
  rename("Observed" = min_observed, "CLASS" = min_static, "Variable Fresh" = min_variable)%>%
  gather(., key = "Model", value = "Min", -site, -time)

abs_stats_wide <- merge(abs_mean, abs_max, by = c("site", "time", "Model"))%>%
  merge(., abs_min, by = c("site", "time", "Model"))

abs_stats_wide$Model <- factor(abs_stats_wide$Model, levels = c("Observed", "Variable Fresh", "CLASS"))

abs_stats_long <- abs_stats_wide%>%
  gather(., key = "Statistic", value = "Absorption", -site, -time, -Model)

ggplot(abs_stats_wide, aes(x=site, y=Mean, fill = Model))+
  geom_bar(stat = "identity", color = "white", position = position_dodge())+
  geom_errorbar(aes(ymin = Min, ymax = Max), width = 0.2, position = position_dodge(0.9))+
  facet_wrap(~time)+
  theme_bw()+
  scale_fill_manual(values = c("grey25", "cyan4" , "red4"))+
  theme(legend.position = c(0.5, 0.85), text = element_text(size = 17.5, family = "Times New Roman"), legend.title = element_blank())+
  labs(x=element_blank(), y="Net Shortwave Radiation (w/m^2)")


  
abs_long <- abs_stats%>%
  select(SY, site, static_diff, variable_diff)%>%
  rename("Static Fresh α " = static_diff, "Variable Fresh α" = variable_diff)%>%
  gather(., key = "Model", value = "Difference", -SY, -site)


ggplot(abs_long%>%filter(!SY == "SY2011"), aes(x=SY))+
  geom_bar(aes(y=Difference, fill = Model), stat ="identity", position = position_dodge())+
  facet_wrap(~site)+
  theme_bw()+
  labs(x = element_blank(), y = "Energy Absorbed Difference (w/m2)")+
  theme(legend.position = c(0.5, 0.15), text = element_text(size = 17.5, family = "Times New Roman"))+
  scale_fill_manual(values = c("red4", "cyan4"))


```

### Coefficents

```{r}

summary(lm_warm_vis)
confint(lm_warm_vis)
summary(lm_cool_vis)

summary(lm_warm_filt)
summary(lm_cool_filt)
coef(lm_warm_vis)

df1 <- variable.names(lm_warm_vis)%>%
  as_tibble(.)%>%
  mutate(coef = coef(lm_warm_vis),
         min_2.5 = confint(lm_warm_vis)[,1],
         max_97.5 = confint(lm_warm_vis)[,2],
         r2 = summary(lm_warm_vis)$adj.r.squared,
         df = summary(lm_warm_vis)$df[2])%>%
  mutate(LM = "Warm Vis")

str(df1)

df2 <- variable.names(lm_warm_filt)%>%
  as_tibble(.)%>%
  mutate(coef = coef(lm_warm_filt),
         min_2.5 = confint(lm_warm_filt)[,1],
         max_97.5 = confint(lm_warm_filt)[,2],
         r2 = summary(lm_warm_filt)$adj.r.squared,
         df = summary(lm_warm_filt)$df[2])%>%
  mutate(LM = "Warm NSWIR")

df3 <- variable.names(lm_cool_filt)%>%
  as_tibble(.)%>%
  mutate(coef = coef(lm_cool_filt),
         min_2.5 = confint(lm_cool_filt)[,1],
         max_97.5 = confint(lm_cool_filt)[,2],
         r2 = summary(lm_cool_filt)$adj.r.squared,
         df = summary(lm_cool_filt)$df[2])%>%
  mutate(LM = "Cold NSWIR")

df4 <- variable.names(lm_cool_vis)%>%
  as_tibble(.)%>%
  mutate(coef = coef(lm_cool_vis),
         min_2.5 = confint(lm_cool_vis)[,1],
         max_97.5 = confint(lm_cool_vis)[,2],
         r2 = summary(lm_cool_vis)$adj.r.squared,
         df = summary(lm_cool_vis)$df[2])%>%
  mutate(LM = "Cold Vis")

unique(LM_all$value)
names(LM_all)

LM_all <- rbind(df1,df2,df3,df4)%>%
  dplyr::select(LM, value, coef, min_2.5, max_97.5, r2, df)%>%
  mutate("Coefficient" = round(coef, digits = 3),
        min_2.5 = round(min_2.5, digits = 3),
        max_97.5 = round(max_97.5, digits = 3),
         R = round(r2, digits = 3))%>%
  dplyr::select(-coef, -r2)%>%
  mutate(value = ifelse(value == "(Intercept)", "Intercept",
                  ifelse(value == "depth_diff", "∆Depth (m)", 
                   ifelse(value == "alb_tminus1", "α(t-1)", 
                    ifelse(value == "newdust", "# of DE",
                     ifelse(value == "depth_m", "Depth (m)", NA))))))%>%
  filter(!is.na(value))%>%
  mutate(min_2.5 = as.numeric(min_2.5),
         max_97.5 = as.numeric(max_97.5),
         Coefficient = as.numeric(Coefficient))

LM_all$LM <- factor(LM_all$LM, levels = c("Cold Vis", "Warm Vis", "Cold NSWIR", "Warm NSWIR"))
LM_all$value <- factor(LM_all$value, levels = c("Intercept", "Depth (m)", "∆Depth (m)", "α(t-1)", "# of DE"))
  

names(LM_all)
str(LM_all)



ggplot(LM_all, aes(x=value, y=Coefficient, fill = value))+
  geom_bar(stat = "identity", color = "white", position = position_dodge())+
  geom_errorbar(aes(ymin = min_2.5, ymax = max_97.5, color = value), width=0.2, position = position_dodge())+
  facet_wrap(~LM, scales = "free_y")+
  theme_bw()+
  scale_fill_manual(values = wes_palette(n=5, name = "IsleofDogs1"))+
  scale_color_manual(values = wes_palette(n=5, name = "IsleofDogs2"))+
  theme(legend.position = c(0.62, 0.85), text = element_text(size = 17.5, family = "Times New Roman"), legend.title = element_blank())+
  labs(x=element_blank())



```

### Variable Figure

```{r}

names(final)

plot <- final%>%
  select(hour, DOSY, site, SY, depth_m, albedo, reset_alb, alb_unfilt)%>%
  filter(!is.na(alb_unfilt))%>%
  filter(hour == 12)%>%
  select(!hour)%>%
  mutate(filt = ifelse(depth_m == 0 & DOSY > 120 & DOSY < 220, NA, "OK"))%>%
  filter(!is.na(filt))%>%
  filter(!is.na(depth_m))%>%
  group_by(DOSY, site, SY)%>%
  summarize(mean_d = mean(depth_m),
            mean_alb_f = mean(albedo),
            # max_d = max(depth_m),
            # min_d = min(depth_m),
            # max_alb_f = max(albedo),
            # min_alb_f = min(albedo),
            mean_alb_s = mean(reset_alb),
            # max_alb_s = max(reset_alb),
            # min_alb_s = min(reset_alb),
            mean_alb = mean(alb_unfilt))%>%
            # max_alb = max(alb_unfilt),
            # min_alb = min(alb_unfilt))%>%
  mutate(time = ifelse(DOSY <= 91, "Early Events", 
                  ifelse(DOSY > 91 & DOSY < 227, "Accumulation", "Melt")))%>%
  mutate(time = factor(time, levels = c("Early Events", "Accumulation", "Melt")))%>%
  rename("Observed" = mean_alb, "Variable Fresh" = mean_alb_f, "CLASS" = mean_alb_s)

plot_long <- plot%>%
  gather(., key = "Model", value = "Albedo", -DOSY, -site, -SY, -mean_d, -time)

plot_function <- function(snowyear){
  
 p1 <-ggplot(plot_long%>%filter(SY == snowyear), aes(x=DOSY))+
        # geom_errorbar(aes(ymin=min_alb_s, ymax =max_alb_f), color = "red4", alpha = 0.8)+
        # geom_errorbar(aes(ymin=min_alb_f, ymax =max_alb_f), color = "cyan4", alpha = 0.8)+
        # geom_errorbar(aes(ymin=min_d/4, ymax =max_d/4), color = "steelblue3", alpha = 0.8)+
        geom_line(aes(y=Albedo, color = Model, linetype = Model))+
        geom_line(aes(y=mean_d/4), color = "steelblue4")+
        scale_color_manual(values = c("red4","black", "cyan4"))+
        scale_linetype_manual(values = c("dotted", "solid", "dashed"))+
        facet_grid(site~time, scales = "free")+
        theme_bw()+
        theme(text = element_text(size = 17.5, family = "Times New Roman"),
              axis.text.y.right = element_text(colour="steelblue3"),
              axis.title.y.right = element_text(colour="steelblue3"),
              legend.text = element_text(size = 10),
              legend.position = c(0.56, 0.55), legend.title = element_blank())+
        scale_y_continuous(name = "Broadband Albedo",
                           sec.axis = sec_axis(~.*4, name = "Depth (m)"))+
        labs(subtitle = {snowyear})

return(p1)
}

plot_function(snowyear = "SY2006")
plot_function(snowyear = "SY2007")
plot_function(snowyear = "SY2008")
plot_function(snowyear = "SY2009")
plot_function(snowyear = "SY2010")
plot_function(snowyear = "SY2011")
plot_function(snowyear = "SY2012")
plot_function(snowyear = "SY2013")
plot_function(snowyear = "SY2014")

```



### Cross Covariance

```{r}

names(vis_simp)
names(filt_simp)
names(stats_setup)
str(stats_setup)


cov(stats_setup$alb_tminus1, stats_setup$alb_tminus1)

cor(stats_setup$depth_m, stats_setup$depth_diff, method = "pearson")^2
cov(stats_setup$depth_m, stats_setup$depth_diff)

cor(stats_setup$depth_m, stats_setup$Tavg_C, method = "pearson")^2
cov(stats_setup$depth_m, stats_setup$Tavg_C)

cor(stats_setup$depth_m, stats_setup$alb_tminus1, method = "pearson")^2
cov(stats_setup$depth_m, stats_setup$alb_tminus1)

cor(stats_setup$depth_m, stats_setup$newdust, method = "pearson")^2
cov(stats_setup$depth_m, stats_setup$newdust)

cor(stats_setup$Tavg_C, stats_setup$depth_diff, method = "pearson")^2
cov(stats_setup$Tavg_C, stats_setup$depth_diff)

cor(stats_setup$Tavg_C, stats_setup$alb_tminus1, method = "pearson")^2
cov(stats_setup$Tavg_C, stats_setup$alb_tminus1)

cor(stats_setup$Tavg_C, stats_setup$newdust, method = "pearson")^2
cov(stats_setup$Tavg_C, stats_setup$newdust)

cor(stats_setup$depth_diff, stats_setup$alb_tminus1, method = "pearson")^2
cov(stats_setup$depth_diff, stats_setup$alb_tminus1)

cor(stats_setup$depth_diff, stats_setup$newdust, method = "pearson")^2
cov(stats_setup$depth_diff, stats_setup$newdust)

cor(stats_setup$alb_tminus1, stats_setup$newdust, method = "pearson")^2
cov(stats_setup$alb_tminus1, stats_setup$newdust)

```

### Hysteresis

```{r}

names(final)
summary(final)
 names(model_stats)

model_stats <-final%>%
  dplyr::select(DOSY, hour, depth_m, alb_unfilt, albedo, reset_alb, site)%>%
  filter(hour %in% c(10,11,12,13,14))%>%
  filter(!is.na(depth_m))%>%# & depth_m >0)%>%
  group_by(DOSY, site)%>%
  summarise("Observed" = mean(alb_unfilt),
            "Variable Fresh" = mean(albedo),
            "CLASS" = mean(reset_alb),
            mean_d = mean(depth_m))%>%
  gather(., key = "Model", value = "Albedo", -DOSY, -site, -mean_d)

model_stats$Model <- factor(model_stats$Model, levels = c("Observed", "Variable Fresh", "CLASS"))

summary(model_stats)

ggplot(model_stats%>%rename("Site" = site), aes(x=mean_d, y=Albedo, color = DOSY))+
  geom_point(aes(shape = Site))+
  scale_color_gradient2(low = "tan4", mid = "snow3", high = "gray25", midpoint = 182)+
  scale_shape_manual(values = c(1,4))+
  facet_wrap(~Model)+
  theme_bw()+
  theme(legend.position = c(0.87, 0.4), text = element_text(size = 17.5, family = "Times New Roman"))+
  labs(x="Mean Depth (m)", y= "Mean Broadband Albedo")+
  ylim(c(0,1))
  

model_stats_SY <-final%>%
  dplyr::select(DOSY, SY, hour, depth_m, alb_unfilt, albedo, reset_alb, site)%>%
  filter(hour %in% c(10,11,12,13,14))%>%
  filter(!is.na(depth_m))%>%
  group_by(DOSY, site, SY)%>%
  summarise("Observed" = mean(alb_unfilt),
            "Variable Fresh" = mean(albedo),
            "CLASS" = mean(reset_alb),
            mean_d = mean(depth_m))%>%
  gather(., key = "Model", value = "Albedo", -DOSY, -site, -mean_d, -SY)

model_stats_SY$Model <- factor(model_stats_SY$Model, levels = c("Observed", "Variable Fresh", "CLASS"))

ggplot(model_stats_SY%>%rename("Site" = site), aes(x=mean_d, y=Albedo, color = DOSY))+
  geom_point(aes(shape = Site))+
  scale_color_gradient2(low = "tan4", mid = "snow3", high = "gray25", midpoint = 182)+
  scale_shape_manual(values = c(1,4))+
  facet_grid(SY~Model)+
  theme_bw()+
  theme(text = element_text(size = 17.5, family = "Times New Roman"))+
  labs(x="Mean Depth (m)", y= "Mean Broadband Albedo")+
  ylim(c(0,1))
            

```

### Density Again

```{r}


fresh_dens <- new_df%>%
  group_by(site)%>%
  mutate(depth_diff = depth_m - lag(depth_m),
         depth_diff = ifelse(is.na(depth_diff), 0, depth_diff),
         alb_diff = alb_unfilt - lag(alb_unfilt),
         alb_diff = ifelse(is.na(alb_unfilt), 0, alb_diff))%>%
  ungroup()%>%
  filter(alb_unfilt < 0.98 & alb_unfilt > 0.15)%>%
  filter(depth_diff > 0)%>%
  filter(alb_diff > 0)%>%
  filter(hour %in% c(10,11,12,13,14))%>%
  mutate(HP_dens = ifelse(Tavg_C < 0, 67.92+51.25*exp(Tavg_C/2.59), NA),
         DL_dens = 119+6.48*Tavg_C,
         LaCh_dens = 50 + 1.7*(Tavg_C+15)^1.5, 
         PS_dens = 85*((-0.030*cos(0.331*Tavg_C+0.418)+0.015*cos(2*0.331*Tavg_C+0.418)-
                                    0.029*cos(3*0.331*Tavg_C+0.418)+0.123*sin(0.331*Tavg_C+0.418)+
                                      0.009*sin(2*0.331*Tavg_C+0.418)-0.026*sin(3*0.331*Tavg_C+0.418))*
                                     -1.75+1))

fresh_dens_long <-fresh_dens %>%
  dplyr::select(DOSY,Tavg_C, site, alb_unfilt, HP_dens, DL_dens, LaCh_dens, PS_dens)%>%
  rename("Hedstrom-Pomeroy" = HP_dens, "LaChapelle" = LaCh_dens, "Diamond-Lowry" = DL_dens, "Particle Shape" = PS_dens)%>%
  gather(., key = "Model", value = "Density", -DOSY, -site, -alb_unfilt, -Tavg_C)


ggplot(fresh_dens_long%>%filter(!is.na(Density) & Density > 0), aes(x=Density, y=alb_unfilt))+
  geom_point(aes(shape = site, color = Tavg_C), alpha = 0.9)+
  scale_shape_manual(values = c(1,4))+
  scale_color_gradient2(low = "blue4", mid = "snow3", high = "red4", midpoint = 0)+
  theme_bw()+
  ylim(c(0,1))+
  facet_wrap(~Model, nrow = 1, scales = "free_x")+
  labs(x="Fresh Snow Density (kg/m^3)", y = "Observed Albedo", shape = element_blank(), color = "Temp (°C)")+
  theme(text = element_text(size = 17.5, family = "Times New Roman"))



```

### SY2008 depth

```{r}
names(final)
sy08_long <- final%>%
  dplyr::select(date,hour,SY,DOSY,depth_m, alb_unfilt, reset_alb, albedo, site)%>%
  filter(SY == "SY2008")%>%
  filter(DOSY > 46 & DOSY < 86)%>%
  filter(hour ==12)%>%
  dplyr::select(!hour)%>%
  filter(site == "SBSP")%>%
  rename("Observed" = alb_unfilt, "CLASS" = reset_alb, "Variable Fresh" = albedo)%>%
  gather(., key="Model", value = "Albedo", -date,-SY,-DOSY,-depth_m,-site)

ggplot(sy08_long, aes(x=date))+
  geom_line(aes(y=Albedo, color = Model, linetype = Model))+
  scale_color_manual(values = c("red4", "black", "cyan4"))+
  scale_linetype_manual(values = c("dotted", "solid", "dashed"))+
  geom_line(aes(y=depth_m*3), color = "steelblue3", size = 1.2)+
  theme_bw()+
  scale_y_continuous(name = "Broadband Albedo", limits = c(0,1),
                           sec.axis = sec_axis(~./3, name = "Depth (m)"))+
  labs(x=element_blank())+
  theme(text = element_text(size = 17.5, family = "Times New Roman"),
              axis.text.y.right = element_text(colour="steelblue3"),
              axis.title.y.right = element_text(colour="steelblue3"),
        axis.text.x=element_text(angle=45, hjust=1),
        legend.title = element_blank(), legend.position = c(0.45,0.88))+
  scale_x_date(date_breaks = "1 week", date_labels =  "%m/%d/%Y") 



```

